### 2017-02-06 paper.tex
tex + pdf

% Created 2017-02-05 Sun 21:39
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{ffff}
\date{\today}
\title{1-Step, 3-Factor Authentication with Custom-Fit, In-Ear EEG}
\hypersetup{
 pdfauthor={ffff},
 pdftitle={1-Step, 3-Factor Authentication with Custom-Fit, In-Ear EEG},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 25.1.1 (Org mode 9.0.4)}, 
 pdflang={English}}
\begin{document}

\maketitle
\begin{abstract}
In this paper, we present a system that provides 3-factors of authentication (knowledge, posession and inherence) in a single step, using brain-based authentication via a custom-fit, in-ear EEG. Across all subjects, we achieve a best-case false acceptance, XX% false rejection rate with data from only one earpiece. In a preliminary test of an ``imposter'' spoof attack, we find a 0% false acceptance rate. _Conclusions and relevance_.
\end{abstract}

\section{Introduction}
\label{sec:org7196b99}

It is well appreciated by experts and end-users alike that strong authentication is
critical to cybersecurity and privacy, now and into the future. Unfortunately,
news 
reports of celebrity account hackings serve as regular reminders that
the currently dominant method of authentication in consumer applications, 
single-factor authentication using passwords or other user-chosen secrets, 
is faced by many challenges. Major industry players such as Google and
Facebook have been strongly encouraging their users to adopt two-factor
authentication (2FA). However, the need for users to submit two different 
authenticators in two separate steps has frustrated wide adoption, 
due its additional hassle cost to the users. For instance, the popular Apple
iPhone has already implemented the necessary technologies to support device
unlock using either a user-selected passcode or a fingerprint. Therefore the
device could easily support a two-step two-factor authentication scheme if
desired. However, it is easy to understand why users would balk at having to
enter a passcode \emph{and} provide a fingerprint each time they want to unlock their phone.

In previous work, “one-step two-factor authentication” has been proposed as a
new approach to authentication that can provide the security benefits of two-
factor authentication without incurring the hassle costs of two-step verification.
By employing consumer-grade EEG (electroencephalogram) sensing
technologies, it was demonstrated in a 2013 passthoughts study that a user can
submit both a knowledge factor (i.e., secret thought) and an inherence factor
(i.e., brainwave signal unique to the individual) in a single step by performing a
single mental task. Additionally, the robustness of this method against
impersonation attacks was demonstrated, including conditions where the attacker
may have learned the target’s secret thought and/or secret task.

In the present proposal, we will undertake, to the best of our knowledge, the first
ever study of one-step three-factor authentication. In computer security,
authenticators are classified into three types: knowledge factors (e.g., passwords
and PINs), possession factors (e.g., physical tokens, ATM cards), and inherence
factors (e.g., fingerprints and other biometrics). Because three-factor
authentication (3FA) requires the user to submit one distinct instance of each
type of authenticator, it represents the strongest level of authentication security
possible.

We propose the use of custom-fit Ear EEG technology as the platform for
investigating the feasibility, performance, and usability of one-step three-factor
authentication. In addition to the same knowledge factor and inherence factor as
in previous work, the user can submit in the same step the possession factor
in the form of the EEG-sensing ear-piece(s) that are custom-fitted to and worn in
their ear. These earpieces can serve as physical tokens in the same way as bank
ATM cards and wearable hardware tokens. Furthermore, because the earpieces
are custom-fitted to each individual, they will likely not be able to produce good
electrical impedances when worn by a different individual.

\section{Related work}
\label{sec:org3732d7c}

The use of EEG as a biometric signal for user authentication has a short history.
In 2005, Thorpe et al. motivate and outline the design of a passthoughts system,
where, rather than typing a password, users authenticate 
by thinking of a passthought. Since 2002, a number of independent groups have achieved 99-
100$\backslash$% authentication accuracy using multi-channel sensors placed on the scalp. In 2013, one group showed that 99$\backslash$% authentication accuracy can also be
achieved using a consumer-grade single-channel sensor. In particular, the
lack of signal diversity from multiple EEG channels can be overcome by allowing
the users to choose their own personalized passthoughts (e.g., sing their favorite
song in their head). There are two significant consequences of this result. First,
the passthoughts approach is no longer constrained by the high cost (> \$10,000 USD)
and low usability (gel-based electrodes; aesthetic challenges of an EEG cap) of
medical-grade multi-channel devices. Second, because users can choose and
easily change their secret mental task, this approach can support one-step two-
factor authentication via the simultaneous presentation of the inherence factor
(brainwave signatures due to the unique folding structures of the cortex) and the
knowledge factor (the secret mental task).

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figures/2EEEG.jpg}
\caption{Pair of custom-fit earpieces with 3 embedded electrodes each located at the helix and front-facing and back-facing within the ear canal.}
\end{figure}

Research in in-ear EEG is only several years old. Nonetheless, the concept has
attracted a lot of attention because of the discreetness factor of in-ear EEG over
traditional scalp-based EEG. A research team at the Imperial College London
and Aarhus University published a landmark paper in 2011 that introduced the
concept of in-ear EEG, demonstrating for the first time the feasibility of recording
brainwave signals from within the ear canal. Follow-up work from the same
group demonstrated its ability to produce signal-to-noise ratios comparable to
those from conventional EEG electrode placements, robustness to common
sources of artifacts, and use in a brain-computer interface (BCI) system based on
auditory evoked potentials and visual evoked potentials.
\uline{Citation to our pst work} 
was the first to merge these two streams of work, using in-ear EEG signals for
user authentication with a consumer-grade device. United Sciences is currently
developing a consumer hearable called The Aware that will measure EEG from the ear.
Behavioral authentication methods such as keystroke dynamics and speaker
authentication can be categorized as one-step two-factor authentication
schemes. In both cases, the knowledge factor (password or passphrase) and
inherence factor (typing rhythm or speaker’s voice) are employed. In contrast, the
Nymi band supports one-step two-factor authentication via the inherence
factor (cardiac rhythm that is supposed to be unique to each individual) and the
possession factor (the wearing of the band on the wrist). However, as far as we
know, no one has proposed or demonstrated a one-step three-factor
authentication scheme.
\section{Methods}
\label{sec:org63d105c}
\subsection{{\bfseries\sffamily TODO} Manufacturing, materials}
\label{sec:orgb483219}
\subsection{Subjects}
\label{sec:orgaf30da9}
\subsection{{\bfseries\sffamily TODO} Tasks}
\label{sec:org86eea32}

\uline{Explain stuff around tasks}

\begin{table}[h]
\centering
\begin{tabular}{ll}
\textbf{\textbf{Task}} & \textbf{\textbf{Description}}\\
\hline
Breathe & Relaxed breathing with eyes closed.\\
Breathe - Open & Relaxed breathing with eyes open.\\
Sport & Sport-related motor imagery of participant's choice.\\
Song & Imagining a song of participant's choice playing.\\
Song - Open & Imagining a song with eyes open.\\
Speech & Imagining a phrase of participant's choice being spoken.\\
Listen & Tone \& Listening to a continuous tone.\\
Listen - ASSR & Listening to noise modulated at 40 Hz.\\
Face & Imagining a person's face of participant's choice.\\
Sequence & On timed cues, imagine a face, a number, and a word.\\
\hline
\end{tabular}
\caption{Set of tasks proposed for authentication with descriptions.}
\end{table}

\begin{table}[h]
\centering
\begin{tabular}{lllll}
Task & External stimuli? & Personal secret? & Eyes? & Imagery?\\
\hline
Breathe & No & No & Closed & None\\
Breathe - open & No & No & Open & None\\
Sport & No & Yes & Closed & Motor\\
Song & No & Yes & Closed & Aural\\
Song - open & No & Yes & Open & Aural\\
Speech & No & Yes & Closed & Aural\\
Listen - Tone & Yes & No & Closed & None\\
Listen - ASSR & Yes & No & Closed & None\\
Face & No & Yes & Closed & Visual\\
Sequence & Yes & Yes & Open & Visual\\
\hline
\end{tabular}
\caption{Properties of authentication tasks. We selected tasks with a variety of different properteries, but preferred tasks that did not require external stimuli, as the need to present such stimuli at authentication time could present challenges for usability, and user security.}
\end{table}
\subsection{Protocol}
\label{sec:org2041857}
Our initial participants were recruited from a nearby university and scheduled for ear molding
and impedance checking sessions. Finally, the data collection visit was scheduled and took
approximately 90 minutes for set up and experiment execution. The OpenBCI system we used
allows for 8 channels of simultaneous recording, along with separate ground and reference channels.
Data was initially collected with the ground placed at the center of the forehead, and using the left
mastoid as reference, though we can easily re-reference to another channel by subtracting a desired
channel (such as right mastoid). Each earpiece (shown in the image below) contain three channels: 
one placed on the helix, and two inside the canal - one front-facing and the other back-facing. The remaining
two channels were placed on the right mastoid for later re-referencing, and at approximately Fp1 (on the 
forehead above the left eye) for validating the data collected in the ears against a scalp-based measure. 
Before beginning the experiment, the data from all channels was visualized and participants were asked to
blink and clench their jaws to confirm visibly that all channels were active and properly connected.

During the experiment, participants were seated in a comfortable position in a quiet room facing a laptop screen on which the
instructions and stimuli were presented using PsychoPy. Each task was completed once in sets five trials each, and then
each was completed again for another five trials. Each trial was 10 seconds in length, for a total of 10 trials and 
100 seconds of data collected per task. The instructions were read aloud to the participant by the experimenter, and
the experiment was advanced using a pointer held in the participant's lap to minimize motion artifacts in the data.  
The experimenter also recorded the participant's chosen secrets for the sport, song, face, speech, and sequence
 tasks and reminded the participant of these for the second set of trials.
\section{Analysis}
\label{sec:org6c1a839}
\subsection{Validating the data}
\label{sec:org800f2bd}

In this section, we establish that the data we collected were EEG signals with relatively low noise. 
Using the pilot data from two participants, we were able to confirm the custom-fit earpieces are able to collect EEG
data using three tests: good impedances measured for the ear electrodes, alpha-band activity attenuation when a
participant's eyes were open versus closed, and the presence of a significant ASSR signal.

The recorded impedances of the earpiece electrodes were less than 5 kOhms except one, a benchmark used widely in previous
ear EEG work. The left helix electrode of one participant was measured at 9 kOhms, and generally the 
helix impedances for both participants were higher than their ear canal counterparts. We expected this result, given that the
helix electrode relies on quality of the earpiece's fit outside the ear for good contact, and is not as securely and tightly placed as the
electrodes within the ear canal. Nonetheless, the data from all electrodes were tested in the remaining two data quality tests.

For the alpha-attenuation test, data from the "Breathe" task was compared with that of the "Breathe - Open" task. It is a well-
known feature of EEG data that activity in the alpha-band (approximately 8-12 Hz range) increases when the eyes are closed
compared with a similar state with eyes open. For both of our pilot participants this attenuation is clearly visible even in just
a single trial's data. To further validate, we also performed this calculation on the data collected from the Fp1 electrode and see
the effect clearly here as well. It is important to note that the left ear results are reported using the right mastoid as reference, and
the right ear results in turn using the left mastoid as reference. When using the same side mastoid for reference the effect is not 
visible, though it may be if we average across many trials. This is not surprising, as the further a reference electrode is from the active
channel the less "real" signal is being subtracted from the active channel. This has important design implications for eventual 
real-world deployment of this authentication method however, as it will likely require pieces worn on or around both ears to properly 
function, and not just one. The figures below show the alpha attenuation in the left and right ear channels, as well as Fp1.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{figures/001_AlphaAtt_Fp1.jpg}
\caption{Alpha-attenuation (8-12 Hz range) in Fp1 channel, referenced at left mastoid, for comparison to ear channels. Red indicates breathing data with
eyes open, blue indicates the same task with eyes closed.}
\end{figure}

\begin{figure}[h]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/001_AlphaAtt_Left.jpg}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/001_AlphaAtt_Right.jpg}
  \end{minipage}
\caption{Alpha-attenuation (8-12 Hz range) in left and right ear canal channels, referenced at opposite mastoids respectfully. Red indicates breathing data with
eyes open, blue indicates the same task with eyes closed.}
\end{figure}

Finally, for the ASSR test we calculated power spectra for data from the "Listen - ASSR" task. The audio stimulus used for this task is modulated 
at 40 Hz, which should, in turn, produce an EEG response visible in the data at 40 Hz. Strangely, in our tests we do see an ASSR spike but it is located 
around 74 Hz instead. While this has us somewhat perplexed about our stimulus, the purpose of this test was to ensure that the response seen in the ear channels 
matched the response seen from the Fp1 recordings, which is evident comparing the figures below.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{figures/001_ASSR_Fp1.jpg}
\caption{Power spectrum for data collected from the Fp1 channel during 40 Hz ASSR stimulus. An ASSR spike is clearly visible, though not at 40 Hz where it was expected.}
\end{figure}

\begin{figure}[h]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/001_ASSR_Left.jpg}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/001_ASSR_Right.jpg}
  \end{minipage}
\caption{Power spectra for data collected from the earpiece channels during 40 Hz ASSR stimulus. Again, the spike is clearly visible though not at 40 Hz, however it 
does match the activity measured at Fp1.}
\end{figure}
\subsection{{\bfseries\sffamily TODO} Classification}
\label{sec:org717cdb9}
\subsection{{\bfseries\sffamily TODO} Simulating an imposter attack}
\label{sec:orgdd6e8bd}
\section{Results}
\label{sec:org6705b1d}
\subsection{{\bfseries\sffamily TODO} Combinations of electrodes}
\label{sec:org21b14ae}

\uline{Figure: Plot of FAR/FRR by electrode combination, XGBoost and LinearSVC}.

\subsection{{\bfseries\sffamily TODO} Left-ear authentication}
\label{sec:org82cbcf4}

\uline{Our main result:}

\uline{Table: FAR/FRR Between-subjects results by participant (avg. all tasks? Best task?)}

\uline{Our attempt to substantiate that we have both inherence and knowledge factors:}

\uline{Table: original strategy, within-subjects, within-tasks strategy; where each of those headings is subdivided into mean FAR, mean FRR (across all subjects and tasks)}

\subsection{{\bfseries\sffamily TODO} Imposter attack}
\label{sec:orgac58a1b}

\subsection{{\bfseries\sffamily TODO} Usability}
\label{sec:org18d5968}

\uline{Quantitative and qualitative data, where appropriate}

\section{{\bfseries\sffamily TODO} Discussion}
\label{sec:orgcd35710}

\begin{enumerate}
\item Apparent feasibility of single earpiece

\item Balancing between FAR \& FRR, improvements over previous work

\item Notable patterns: best task breathe across participants; each feature vector represents very little time (500ms)

\item Counter to expectations: referencing same side appears to be an improvement vs. across the head; use of conductive gel resulting in ability to achieve good impedances on others’ earpieces; FP1 not performing as well as expected.
\end{enumerate}

\section{{\bfseries\sffamily TODO} Conclusion \& Future Work:}
\label{sec:org29a90c8}

\begin{itemize}
\item How will this system change with more users? How will this system change with more diverse data?
\begin{itemize}
\item EEG stability
\item Also breakdown/malfunction
\item Address with? Ambulatory settings, Exercise, alcohol, caffeine, etc.
\end{itemize}
\item How “hackable” is a passthought?
\begin{itemize}
\item Point from NSPW draft
\item Address with? Statistical analysis \& hacking existing classifiers
\end{itemize}
\item UX improvements/innovations?
\begin{itemize}
\item Dry electrodes?
\item Closed-loop system?
\end{itemize}
\end{itemize}

Closed-loop BCI system could help us understand how learning effects
on the human side might impact authentication performance, as the human and machine
co-adapt during multiple authentication attempts.
\end{document}

### 2017-02-06 paper.tex
updated abstract

@@
 In this paper, we present a system that provides 3-factors of authentication (knowledge, posession and inherence) in a single step, using brain-based authentication via a custom-fit, in-ear EEG.
-Across all subjects, we achieve a best-case false acceptance, XX% false rejection rate with data from only one earpiece.
-In a preliminary test of an ``imposter'' spoof attack, we find a 0% false acceptance rate.
-_Conclusions and relevance_.
+Across all subjects, we achieve a best-case XX\% false acceptance, XX\% false rejection rate with data from only one earpiece.
+In a preliminary test of an ``imposter'' spoof attack, we find a 0\% false acceptance rate.
+\underline{Conclusions and relevance}.
 \end{abstract}

### 2017-02-06 paper.tex
minor + gitignore
USENIX style

@@
-% Created 2017-02-05 Sun 21:39
-% Intended LaTeX compiler: pdflatex
-\documentclass[11pt]{article}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{graphicx}
-\usepackage{grffile}
-\usepackage{longtable}
-\usepackage{wrapfig}
-\usepackage{rotating}
-\usepackage[normalem]{ulem}
-\usepackage{amsmath}
-\usepackage{textcomp}
-\usepackage{amssymb}
-\usepackage{capt-of}
-\usepackage{hyperref}
-\author{ffff}
-\date{\today}
-\title{1-Step, 3-Factor Authentication with Custom-Fit, In-Ear EEG}
-\hypersetup{
- pdfauthor={ffff},
- pdftitle={1-Step, 3-Factor Authentication with Custom-Fit, In-Ear EEG},
- pdfkeywords={},
- pdfsubject={},
- pdfcreator={Emacs 25.1.1 (Org mode 9.0.4)}, 
- pdflang={English}}
+% TEMPLATE for Usenix papers, specifically to meet requirements of
+
+% https://www.usenix.org/conference/usenixsecurity17/submitting-papers
+
+% Complaints to /dev/null.
+% This version uses the latex2e styles, not the very ancient 2.09 stuff.
+\documentclass[letterpaper,twocolumn,10pt]{article}
+\usepackage{lib/usenix,epsfig,endnotes}
 \begin{document}
 
+%don't want date printed
+\date{}
+
+%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
+\title{\Large \bf 3-Step, 1-Factor Authentication With Custom-Fit, In-Ear EEG}
+
+%for single author (just remove % characters)
+\author{
+{\rm Your N.\ Here}\\
+Your Institution
+\and
+{\rm Second Name}\\
+Second Institution
+% copy the following lines to add more authors
+% \and
+% {\rm Name}\\
+%Name Institution
+} % end author
+
 \maketitle
-\begin{abstract}
+
+% Use the following at camera-ready time to suppress page numbers.
+% Comment it out when you first submit the paper for review.
+\thispagestyle{empty}
+
+\subsection*{Abstract}
 In this paper, we present a system that provides 3-factors of authentication (knowledge, posession and inherence) in a single step, using brain-based authentication via a custom-fit, in-ear EEG.
@@
 \underline{Conclusions and relevance}.
-\end{abstract}
 
@@
 auditory evoked potentials and visual evoked potentials.
-\uline{Citation to our pst work} 
+\underline{Citation to our past work} 
 was the first to merge these two streams of work, using in-ear EEG signals for
@@
 
-\uline{Explain stuff around tasks}
+\underline{Explain stuff around tasks}
 
@@
 \begin{tabular}{lllll}
-Task & External stimuli? & Personal secret? & Eyes? & Imagery?\\
+Task & External stimuli? & Knowledge factor ? & Eyes? & Imagery?\\
 \hline
@@
 
-\uline{Figure: Plot of FAR/FRR by electrode combination, XGBoost and LinearSVC}.
+\underline{Figure: Plot of FAR/FRR by electrode combination, XGBoost and LinearSVC}.
 
@@
 
-\uline{Our main result:}
+\underline{Our main result:}
 
-\uline{Table: FAR/FRR Between-subjects results by participant (avg. all tasks? Best task?)}
+\underline{Table: FAR/FRR Between-subjects results by participant (avg. all tasks? Best task?)}
 
-\uline{Our attempt to substantiate that we have both inherence and knowledge factors:}
+\underline{Our attempt to substantiate that we have both inherence and knowledge factors:}
 
-\uline{Table: original strategy, within-subjects, within-tasks strategy; where each of those headings is subdivided into mean FAR, mean FRR (across all subjects and tasks)}
+\underline{Table: original strategy, within-subjects, within-tasks strategy; where each of those headings is subdivided into mean FAR, mean FRR (across all subjects and tasks)}
 
@@
 
-\uline{Quantitative and qualitative data, where appropriate}
+\underline{Quantitative and qualitative data, where appropriate}
 

### 2017-02-06 paper.tex
Future work

@@
 
-\section{{\bfseries\sffamily TODO} Conclusion \& Future Work:}
-\label{sec:org29a90c8}
+\section{Future Work}
 
-\begin{itemize}
-\item How will this system change with more users? How will this system change with more diverse data?
-\begin{itemize}
-\item EEG stability
-\item Also breakdown/malfunction
-\item Address with? Ambulatory settings, Exercise, alcohol, caffeine, etc.
-\end{itemize}
-\item How “hackable” is a passthought?
-\begin{itemize}
-\item Point from NSPW draft
-\item Address with? Statistical analysis \& hacking existing classifiers
-\end{itemize}
-\item UX improvements/innovations?
-\begin{itemize}
-\item Dry electrodes?
-\item Closed-loop system?
-\end{itemize}
-\end{itemize}
+One primary question surrounds how our passthought system performance will change with a greater number of users, and with more diverse data.
+Our system specifically trains on negative examples of non-users; we do not yet know how this approach will scale.
+At the same time, we must investigate the stability of EEG readings for a passthought are over time.
+We must also collect EEG data from the variety of different user states: ambulatory settings, during physical exertion or exercise, under the influence of caffeine or alcohol, etc.
 
-Closed-loop BCI system could help us understand how learning effects
-on the human side might impact authentication performance, as the human and machine
-co-adapt during multiple authentication attempts.
+% We provide cursory evidence that passthoughts are difficult to spoof, though further work should expand on ours with more subjects.
+Another important question surrounds how passthoughts might be cracked.
+Generally, we do not understand how an individual's passthought is drawn from the general distribution of EEG signals that an individual produces throughout the day.
+Given a large enough corpus of EEG data, are some passthoughts as easy to guess as \textit{password1234} is for passwords?
+Future work should perform statistical analysis on passthoughts, such as clustering (perhaps with t-SNE) to better understand the space of possible passthoughts.
+This work will allow us simulate cracking attempts, and to develop empirically motivated strategies for prevention, e.g. locking users out after a certain number of attempts.
+This work could also reveal interesting tradeoffs between the usability and accuracy of certain passthoughts with their security properties.
+
+Finally, our work leaves room for some clear UX improvements.
+Future work should try using dry electrodes, commonly found in consumer EEG devices, for comfort and usability.
+Future work should also attempt a closed-loop (or online) passthought system, in which users receive immediate feedback on the result of their authentication attempt.
+A closed-loop BCI system could help us understand how learning effects
+on the human side might impact authentication performance, as the human and machine co-adapt during multiple authentication attempts.
+
+\section{TODO Conclusion}
+
 \end{document}

### 2017-02-06 paper.tex
Results/Imposter attack

@@
 Across all subjects, we achieve a best-case XX\% false acceptance, XX\% false rejection rate with data from only one earpiece.
-In a preliminary test of an ``imposter'' spoof attack, we find a 0\% false acceptance rate.
+In a preliminary test of an ``imposter'' spoofing attack, we find a 0\% false acceptance rate.
 \underline{Conclusions and relevance}.
@@
 
-\subsection{{\bfseries\sffamily TODO} Imposter attack}
-\label{sec:orgac58a1b}
+\subsection{Imposter attack}
+
+While our left-ear results establish that passthoughts achieve low FAR and FRR when tested against other subjects' passthoughts, we do not know how robust passthoughts are against a spoofing attack, in which both a subject's custom-fit electrode, and details of that subject's chosen passthought, are leaked.
+
+To explore this scenario, we chose one subject (subject 6), and referred to their report of chosen passsthoughts.
+We recorded spoofed passthoughts for two ``imposter'' subjects.
+One subject appeared in our initial pool performing their own passthoughts (subject 2), while the other subject did not appear in the initial pool, and thus was not included when training subject classifiers.
+(How well the imposters were able to spoof subject 6's passthought is an open question; see Discussion).
+
+For each task, we ran the spoofed version of the task through the classifier trained on subject 6's task as the passthought.
+None of the spoofed passthoughts were accepted, resulting in a 0\% FAR.
 
@@
 across the head; use of conductive gel resulting in ability to achieve good impedances on others’ earpieces; FP1 not performing as well as expected.
+
+\item Really saw inherence factor at work in imposter attack. What part of the song? How do you imagine the face? etc
 \end{enumerate}

### 2017-02-06 paper.tex
Discussion

@@
 \section{{\bfseries\sffamily TODO} Discussion}
-\label{sec:orgcd35710}
 
-\begin{enumerate}
-\item Apparent feasibility of single earpiece
+Our findings demonstrate the apparent feasibility of single earpiece, achieving good results with only three electrodes and a reference, all on the left ear.
+FARs and FRRs are low across all subjects and tasks, with FARs overall lower than FRRs.
+Subjects' best-performing passthoughts typically seeing no errors in our training.
+Furthermore, no spoofed attacks were successful in our cursory analysis.
 
-\item Balancing between FAR \& FRR, improvements over previous work
+The powerful interactions between inherence and knowledge emerged in our spoofing attack.
+Although our target subject documented their chosen passthought, the spoofers found ambiguity in how these passthoughts could be expressed.
+For the face task, the spoofers did not know the friend the original subject had chosen.
+For the song tasks, though the song was known, the spoofers did not know what part of the song the original subject had imagined, or how it was imagined (humming, imagining a full performance, melody, vocals, etc).
+This experience sheds light on the highly individual nature of passthoughts, and provides a positive indication that there may be some intrinsic difficulty ofr spoofing passthoughts.
 
-\item Notable patterns: best task breathe across participants; each feature vector represents very little time (500ms)
+In our analysis, some notable patterns emerged.
+First, \textit{breathe} tended to be the best-performing task among participants.
+Classifiers overall distinguished the breath task even compared to breath tasks from other subjects, implying that the task is expressed differently for each subject, i.e.
+that this task has an inherence factor sufficient for authentication, even though the task does not have a knowledge factor.
+Second, we were able to achieve good results by generating feature vectors based on only 500ms (300 voltage readings across the three electrodes).
+This short timespan is somewhat surprising, given that some tasks (like songs) presumably rely on changes or patterns over a longer period of time.
 
-\item Counter to expectations: referencing same side appears to be an improvement vs.
-across the head; use of conductive gel resulting in ability to achieve good impedances on others’ earpieces; FP1 not performing as well as expected.
-
-\item Really saw inherence factor at work in imposter attack. What part of the song? How do you imagine the face? etc
-\end{enumerate}
+Counter to our expectations, we found that referencing on the same side as the electrodes improves classification accuracy, compared to referencing on the other side of the head, as is commonly done in EEG.
+\underline{Theory as to why?} Furthermore, the use of conductive gel results in decent results (low impedances) on other subjects' custom-fit earpieces.
+This is somewhat surprising, since ear canals are believed to be more unique than fingerprints \underline{cite}.
+Finally, performance on FP1 was not as high as performance in the ear, despite FP1's popularity in past work on passthoughts \underline{cite}.
+This could be explained by the greater number of electrodes in the ear (compared to just one on FP1).
+Another explanation might be in the neural activity required to perform the tasks we chose.
+Future work might shed light on this issue.
 

### 2017-02-06 paper.tex
Metods/Classification

@@
 \end{figure}
-\subsection{{\bfseries\sffamily TODO} Classification}
-\label{sec:org717cdb9}
+
+\subsection{Classification}
+
+We analyzed the EEG signals collected during the tasks using a support vector classifier (SVC).
+Since past work has shown that classification tasks in EEG-based BCI are linear \underline{cite}, we used XGBoost, a popular tool for generating ensemble classifiers for logistic linear classification \underline{cite}.
+
+To produce feature vectors, we took slices of 100 raw values from each electrode (about 500ms of data), and performed an FFT to produce power spectra for each electrode during that slice.
+We concatenated all electrode power spectra together, and performed PCA on all concatenated vectors such that the resulting vectors described 95\% of the variance in the full power specrum data.
+For each task, for each participant, 100 seconds of data were collected in total across 10 trials of 10 seconds each, resulting in 200 samples per participant, per task, following preprocessing.
+
+We trained the classifier using a balanced sample of positive and negative examples, where positive examples were from the target subject and target task, and negative examples were randomly selected tasks from any subject besides the target subject.
+From this corpus of positive and negative samples, we withheld one third of data for testing. 
+The remaining training set was fed into a XGBoost's cross-validation method, which we set to iteratively tweak parameters over a maximum of fifty rounds of cross-validation to minimize classification error.
+After cross-validation, the updated classifier (with paramters applied) predicted labels on each sample in the test set, and we calculated FAR and FRR on its results.
+
 \subsection{{\bfseries\sffamily TODO} Simulating an imposter attack}
@@
 
-\section{{\bfseries\sffamily TODO} Discussion}
+\section{Discussion}
 

### 2017-02-06 paper.tex
table updates

@@
 \documentclass[letterpaper,twocolumn,10pt]{article}
-\usepackage{lib/usenix,epsfig,endnotes}
+\usepackage{lib/usenix,epsfig,endnotes,tabularx}
 \begin{document}
@@
 
-\begin{table}[h]
-\centering
-\begin{tabular}{ll}
-\textbf{\textbf{Task}} & \textbf{\textbf{Description}}\\
-\hline
-Breathe & Relaxed breathing with eyes closed.\\
-Breathe - Open & Relaxed breathing with eyes open.\\
-Sport & Sport-related motor imagery of participant's choice.\\
-Song & Imagining a song of participant's choice playing.\\
-Song - Open & Imagining a song with eyes open.\\
-Speech & Imagining a phrase of participant's choice being spoken.\\
-Listen & Tone \& Listening to a continuous tone.\\
-Listen - ASSR & Listening to noise modulated at 40 Hz.\\
-Face & Imagining a person's face of participant's choice.\\
-Sequence & On timed cues, imagine a face, a number, and a word.\\
-\hline
-\end{tabular}
-\caption{Set of tasks proposed for authentication with descriptions.}
-\end{table}
-
-\begin{table}[h]
-\centering
-\begin{tabular}{lllll}
-Task & External stimuli? & Knowledge factor ? & Eyes? & Imagery?\\
-\hline
-Breathe & No & No & Closed & None\\
-Breathe - open & No & No & Open & None\\
-Sport & No & Yes & Closed & Motor\\
-Song & No & Yes & Closed & Aural\\
-Song - open & No & Yes & Open & Aural\\
-Speech & No & Yes & Closed & Aural\\
-Listen - Tone & Yes & No & Closed & None\\
-Listen - ASSR & Yes & No & Closed & None\\
-Face & No & Yes & Closed & Visual\\
-Sequence & Yes & Yes & Open & Visual\\
-\hline
-\end{tabular}
-\caption{Properties of authentication tasks.
-We selected tasks with a variety of different properteries, but preferred tasks that did not require external stimuli, as the need to present such stimuli at authentication time could present challenges for usability, and user security.}
-\end{table}
 \subsection{Protocol}
@@
 
+\section{Endnotes}
+
+\begin{table}[h]
+\centering
+%% \begin{tabular}{llllll}
+\begin{tabularx}{\textwidth}{llllll}
+Task & Description & Stimuli? & Personal? & Eyes? & Imagery?\\
+\hline
+Breathe & Relaxed breathing with eyes closed & No & No & Closed & None\\
+Breathe - Open & Relaxed breathing with eyes open & No & No & Open & None\\
+Sport & Sport-related motor imagery & No & Yes & Closed & Motor\\
+Song & Imagining hearing a song & No & Yes & Closed & Aural\\
+Song - Open & Song task, with eyes open & No & Yes & Open & Aural\\
+Speech & Imagining a spoken phrase & No & Yes & Closed & Aural\\
+Listen \& Tone & Listening to a continuous tone & Yes & No & Closed & None\\
+Listen - ASSR & Listening to noise modulated at 40 Hz & Yes & No & Closed & None\\
+Face & Imagine a person's face & No & Yes & Closed & Visual\\
+Sequence & Imagine face, a number, and word on timed cues & Yes & Yes & Open & Visual\\
+\hline
+\end{tabularx}
+\caption{Properties of authentication tasks.
+We selected tasks with a variety of different properteries, but preferred tasks that did not require external stimuli, as the need to present such stimuli at authentication time could present challenges for usability, and user security.}
+\label{tab:addlabel}%
+\end{table}
+
 \end{document}

### 2017-02-06 paper.tex
Set up to integrate figures for results
Added figures

@@
 
-\subsection{{\bfseries\sffamily TODO} Simulating an imposter attack}
-\label{sec:orgdd6e8bd}
 \section{Results}
@@
 
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=.9\linewidth]{./figures/mean-far-by-electrode-config.png}
+\caption{FAR and FRR by electrode configuration. All electrodes combined achieves a perfect score. We achieve the next best scores using data from the left ear only.}
+\end{figure}
+
+% Include FRR here? (downisdes: FRR is way bigger, can't see FAR). Include LinearSVC here? (downsides: SVC FAR is way bigger, can't see FAR)
+
 \subsection{{\bfseries\sffamily TODO} Left-ear authentication}
@@
 
-\underline{Table: FAR/FRR Between-subjects results by participant (avg. all tasks? Best task?)}
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{rrrl}
+FAR & FRR & subject & task\\
+\hline
+0.0 & 0.0 & 1 & listennoise\\
+0.0 & 0.0 & 2 & breathe\\
+0.0 & 0.0 & 3 & breathe\\
+0.0 & 0.0 & 4 & breathe\\
+0.0 & 0.012 & 5 & breathe\\
+0.0 & 0.0 & 6 & breathe\\
+0.0 & 0.0 & 7 & breathe\\
+\end{tabular}
+\end{center}
+\caption{Best-case passthought FAR and FRR results by participant using data from the left ear.}
+\end{table}
 
-\underline{Our attempt to substantiate that we have both inherence and knowledge factors:}
+\underline{Our attempt to substantiate that we have both inherence and knowledge factors...}
 
-\underline{Table: original strategy, within-subjects, within-tasks strategy; where each of those headings is subdivided into mean FAR, mean FRR (across all subjects and tasks)}
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{lrrr}
+ & Original & Within-tasks & Within-subjects\\
+\hline
+FAR & 0.000074 & 0.000724 & 0.00252\\
+FRR & 0.00442 & 0.001522 & 0.0397\\
+\end{tabular}
+\end{center}
+\caption{Mean FAR and FRR for all subjects and pssthoughts across three different training strategies.}
+\end{table}
+
+\underline{compared to within-tasks training, this original strategy gives us a higher FRR, but an FAR that's an order of magnitude lower. Put takeaways more clearly in the caption.}
+
+% 1. Within-tasks performance
+% 
+% number of tasks with # far < 0.0001 AND frr < 0.01?
+%            
+% subject                                
+% 001        5
+% 002        6
+% 003        6
+% 004        9
+% 005        6
+% 006        9
+% 007        4
+% 
+% 2. Within-subjects performance
+
+% number of tasks with # far < 0.0001 AND frr < 0.01?
+% 
+% subject                                
+% 001        1
+% 002        1
+% 003        6
+% 004        3
+% 005        1
+% 006        3
+% 007        5
+%
+% 3. Original for comparison
+%
+% here is the original training (right-subject, right-task vs. wrong-subject, any-task) FAR/FRR:
+% 
+% FAR  0.000074	
+% FRR  0.004420
+%
 

### 2017-02-07 paper.tex
Draft results

@@
 
-%for single author (just remove % characters)
+%forsupose single author (just remove % characters)
 \author{
@@
 \label{sec:org6705b1d}
-\subsection{{\bfseries\sffamily TODO} Combinations of electrodes}
+\subsection{Combinations of electrodes}
 \label{sec:org21b14ae}
 
-\underline{Figure: Plot of FAR/FRR by electrode combination, XGBoost and LinearSVC}.
+For each configuration of electrodes, we calculated the mean FAR and FRR across all subjects using each task as the passthought (Figure \ref{fig:meanByElectrode}).
+Incorporating all electrodes data results in a perfect score for all tasks.
+Using data from all left-ear electrodes achieves the next lowest FAR, followed by all right ear electrodes.
+Interestingly, no single electrode from the left or right ear performs as well as the aggregate left and right ear conditions. 
+Counter to our expectations, FP1 does not perform as well as most ear electrodes.
+
+Our results indicate acceptable accuracy using electrodes on the left ear alone. 
+This corresponds to our original scenario, in which the device could be worn as an earbud.
+As such, we focus on results from the left ear alone in our following analysis.
 
@@
 \includegraphics[width=.9\linewidth]{./figures/mean-far-by-electrode-config.png}
-\caption{FAR and FRR by electrode configuration. All electrodes combined achieves a perfect score. We achieve the next best scores using data from the left ear only.}
+\caption{FAR by electrode configuration. All electrodes combined achieves a perfect score. We achieve the next best scores using data from the left ear only.}
+\label{fig:meanByElectrode}
 \end{figure}
 
-% Include FRR here? (downisdes: FRR is way bigger, can't see FAR). Include LinearSVC here? (downsides: SVC FAR is way bigger, can't see FAR)
+\subsection{Authentication results in the left-ear}
 
-\subsection{{\bfseries\sffamily TODO} Left-ear authentication}
-\label{sec:org82cbcf4}
-
-\underline{Our main result:}
+In the previous section, we trained and tested a passthought classifier with each task as the passthought, for all subjects.
+Focusing on the left ear, we filter our results for the best-performing tasks.
+We rank tasks by lowest FAR and, given a tie, the lowest FRR (Table \ref{tab:best}).
 
@@
 \caption{Best-case passthought FAR and FRR results by participant using data from the left ear.}
+\label{tab:best}
 \end{table}
 
-\underline{Our attempt to substantiate that we have both inherence and knowledge factors...}
+Breathe appeared as the best task across all participants.
+Given our training strategy, these results indicate that a given person's breathe task is distinguishable not only among other tasks, but among breathe tasks from other subjects.
+All best-performing tasks in our set achieved perfect FAR and FRRs, with the exception of subject 5, whose best-performing task (breathe) had a nonzero FRR.
+
+These results establish good performance in our original training strategy, in which we count as negative examples recordings from the wrong subject performing any task.
+For comparison, we try two additional training strategies: one in which negative examples are the correct task recorded from the wrong subject (within-tasks), and one in which negative examples are the incorrect task recorded from the correct subject (within-subjects).
 
@@
 \caption{Mean FAR and FRR for all subjects and pssthoughts across three different training strategies.}
+\label{tab:compare}
 \end{table}
 
-\underline{compared to within-tasks training, this original strategy gives us a higher FRR, but an FAR that's an order of magnitude lower. Put takeaways more clearly in the caption.}
-
-% 1. Within-tasks performance
-% 
-% number of tasks with # far < 0.0001 AND frr < 0.01?
-%            
-% subject                                
-% 001        5
-% 002        6
-% 003        6
-% 004        9
-% 005        6
-% 006        9
-% 007        4
-% 
-% 2. Within-subjects performance
-
-% number of tasks with # far < 0.0001 AND frr < 0.01?
-% 
-% subject                                
-% 001        1
-% 002        1
-% 003        6
-% 004        3
-% 005        1
-% 006        3
-% 007        5
-%
-% 3. Original for comparison
-%
-% here is the original training (right-subject, right-task vs. wrong-subject, any-task) FAR/FRR:
-% 
-% FAR  0.000074	
-% FRR  0.004420
-%
+Overall, our original training strategy achieves the lowest FAR (Table \ref{tab:compare}). Within-tasks FAR ten times higher, and within-subjects FAR is one hundred times higher.
+However, FRR is \textit{lower} in the within-tasks training strategy than in our original strategy's FRR. Within-subjects again results in the highest FRR.
 

### 2017-02-07 paper.tex
references

@@
 In this paper, we present a system that provides 3-factors of authentication (knowledge, posession and inherence) in a single step, using brain-based authentication via a custom-fit, in-ear EEG.
-Across all subjects, we achieve a best-case XX\% false acceptance, XX\% false rejection rate with data from only one earpiece.
+Across all subjects, we achieve a mean 0\% false acceptance and 0.12X\% false rejection rate with data from only one earpiece.
 In a preliminary test of an ``imposter'' spoofing attack, we find a 0\% false acceptance rate.
-\underline{Conclusions and relevance}.
+Our results indicate that in-ear EEG could provide a discrete, convenient, multifactor authentication.
 
@@
 by thinking of a passthought. Since 2002, a number of independent groups have achieved 99-
-100$\backslash$% authentication accuracy using multi-channel sensors placed on the scalp. In 2013, one group showed that 99$\backslash$% authentication accuracy can also be
+100\% authentication accuracy using multi-channel sensors placed on the scalp. In 2013, one group showed that 99\% authentication accuracy can also be
 achieved using a consumer-grade single-channel sensor. In particular, the
@@
 song in their head). There are two significant consequences of this result. First,
-the passthoughts approach is no longer constrained by the high cost (> \$10,000 USD)
+the passthoughts approach is no longer constrained by the high cost (\> \$10,000 USD)
 and low usability (gel-based electrodes; aesthetic challenges of an EEG cap) of
@@
 auditory evoked potentials and visual evoked potentials.
+
 \underline{Citation to our past work} 

### 2017-02-07 paper.tex
References

@@
 In this paper, we present a system that provides 3-factors of authentication (knowledge, posession and inherence) in a single step, using brain-based authentication via a custom-fit, in-ear EEG.
-Across all subjects, we achieve a mean 0\% false acceptance and 0.12X\% false rejection rate with data from only one earpiece.
+Across all subjects, we achieve a mean 0\% false acceptance and 0.12\% false rejection rate with data from only one earpiece.
 In a preliminary test of an ``imposter'' spoofing attack, we find a 0\% false acceptance rate.
@@
 (i.e., brainwave signal unique to the individual) in a single step by performing a
-single mental task. Additionally, the robustness of this method against
+single mental task \cite{Chuang2014}. Additionally, the robustness of this method against
 impersonation attacks was demonstrated, including conditions where the attacker
-may have learned the target’s secret thought and/or secret task.
+may have learned the target’s secret thought and/or secret task \cite{Johnson2014}.
 
@@
 \section{Related work}
-\label{sec:org3732d7c}
 
+\subsection{Passthought authentication}
 The use of EEG as a biometric signal for user authentication has a short history.
@@
 where, rather than typing a password, users authenticate 
-by thinking of a passthought. Since 2002, a number of independent groups have achieved 99-
-100\% authentication accuracy using multi-channel sensors placed on the scalp. In 2013, one group showed that 99\% authentication accuracy can also be
-achieved using a consumer-grade single-channel sensor. In particular, the
+by thinking of a passthought \cite{Thorpe2005}.
+Since 2002, a number of independent groups have achieved 99-
+100\% authentication accuracy using multi-channel sensors placed on the scalp \cite{Poulos2002,Marcel2007a,Palaniappan2008,Ashby2011}.
+In 2013, one group showed that 99\% authentication accuracy can also be
+achieved using a consumer-grade single-channel sensor \cite{Chuang2013b}. In particular, the
 lack of signal diversity from multiple EEG channels can be overcome by allowing
@@
 song in their head). There are two significant consequences of this result. First,
-the passthoughts approach is no longer constrained by the high cost (\> \$10,000 USD)
+the passthoughts approach is no longer constrained by the high cost (\textgreater \$10,000 USD)
 and low usability (gel-based electrodes; aesthetic challenges of an EEG cap) of
@@
 (brainwave signatures due to the unique folding structures of the cortex) and the
-knowledge factor (the secret mental task).
+knowledge factor (the secret mental task) \cite{Chuang2014}.
 
@@
 
+\subsection{In-Ear EEG}
 Research in in-ear EEG is only several years old. Nonetheless, the concept has
@@
 concept of in-ear EEG, demonstrating for the first time the feasibility of recording
-brainwave signals from within the ear canal. Follow-up work from the same
+brainwave signals from within the ear canal
+\cite{Looney2011}.
+Follow-up work from the same
 group demonstrated its ability to produce signal-to-noise ratios comparable to
@@
 sources of artifacts, and use in a brain-computer interface (BCI) system based on
-auditory evoked potentials and visual evoked potentials.
+auditory evoked potentials and visual evoked potentials
+\cite{Looney2012a,Kidmose2013a,Kidmose2013b}.
+United Sciences is currently developing a consumer ``hearable'' (in-ear wearable) called The Aware, which will measure EEG from the ear, among other biometrics \cite{UnitedSciences}.
 
-\underline{Citation to our past work} 
-was the first to merge these two streams of work, using in-ear EEG signals for
-user authentication with a consumer-grade device. United Sciences is currently
-developing a consumer hearable called The Aware that will measure EEG from the ear.
+\cite{curranpassthoughts} was the first to merge in-ear EEG with passthought authentication.
+
+\subsection{Multi-Factor Authentication in a Single Step}
 Behavioral authentication methods such as keystroke dynamics and speaker
@@
 schemes. In both cases, the knowledge factor (password or passphrase) and
-inherence factor (typing rhythm or speaker’s voice) are employed. In contrast, the
-Nymi band supports one-step two-factor authentication via the inherence
+inherence factor (typing rhythm or speaker’s voice) are employed \cite{Monrose1997}.
+In contrast, the Nymi band supports one-step two-factor authentication via the inherence
 factor (cardiac rhythm that is supposed to be unique to each individual) and the
-possession factor (the wearing of the band on the wrist). However, as far as we
-know, no one has proposed or demonstrated a one-step three-factor
-authentication scheme.
+possession factor (the wearing of the band on the wrist) \cite{Nymi}.
+However, as far as we know, no one has proposed or demonstrated a one-step three-factor
+authentication scheme, in which possession of a unique device also serves to authenticate the user.
+
 \section{Methods}
@@
 \subsection{{\bfseries\sffamily TODO} Tasks}
-\label{sec:org86eea32}
 
 \underline{Explain stuff around tasks}
+
+\begin{table*}[t]
+\centering
+%% \begin{tabular}{llllll}
+\begin{tabularx}{\textwidth}{llllll}
+Task & Description & Stimuli? & Personal? & Eyes? & Imagery?\\
+\hline
+Breathe & Relaxed breathing with eyes closed & No & No & Closed & None\\
+Breathe - Open & Relaxed breathing with eyes open & No & No & Open & None\\
+Sport & Sport-related motor imagery & No & Yes & Closed & Motor\\
+Song & Imagining hearing a song & No & Yes & Closed & Aural\\
+Song - Open & Song task, with eyes open & No & Yes & Open & Aural\\
+Speech & Imagining a spoken phrase & No & Yes & Closed & Aural\\
+Listen \& Tone & Listening to a continuous tone & Yes & No & Closed & None\\
+Listen - ASSR & Listening to noise modulated at 40 Hz & Yes & No & Closed & None\\
+Face & Imagine a person's face & No & Yes & Closed & Visual\\
+Sequence & Imagine face, a number, and word on timed cues & Yes & Yes & Open & Visual\\
+\hline
+\end{tabularx}
+\caption{Properties of authentication tasks.
+We selected tasks with a variety of different properteries, but preferred tasks that did not require external stimuli, as the need to present such stimuli at authentication time could present challenges for usability, and user security.}
+\label{tab:addlabel}%
+\end{table*}
 
@@
 We analyzed the EEG signals collected during the tasks using a support vector classifier (SVC).
-Since past work has shown that classification tasks in EEG-based BCI are linear \underline{cite}, we used XGBoost, a popular tool for generating ensemble classifiers for logistic linear classification \underline{cite}.
+Since past work has shown that classification tasks in EEG-based BCI are linear \underline{Garrett2003a}, we used XGBoost, a tool for logistic linear classification \underline{Chen2016}.
 
@@
 This is somewhat surprising, since ear canals are believed to be more unique than fingerprints \underline{cite}.
-Finally, performance on FP1 was not as high as performance in the ear, despite FP1's popularity in past work on passthoughts \underline{cite}.
+Finally, performance on FP1 was not as high as performance in the ear, despite FP1's popularity in past work on passthoughts \cite{Chuang2013b}.
 This could be explained by the greater number of electrodes in the ear (compared to just one on FP1).
@@
 
-\section{Endnotes}
-
-\begin{table}[h]
-\centering
-%% \begin{tabular}{llllll}
-\begin{tabularx}{\textwidth}{llllll}
-Task & Description & Stimuli? & Personal? & Eyes? & Imagery?\\
-\hline
-Breathe & Relaxed breathing with eyes closed & No & No & Closed & None\\
-Breathe - Open & Relaxed breathing with eyes open & No & No & Open & None\\
-Sport & Sport-related motor imagery & No & Yes & Closed & Motor\\
-Song & Imagining hearing a song & No & Yes & Closed & Aural\\
-Song - Open & Song task, with eyes open & No & Yes & Open & Aural\\
-Speech & Imagining a spoken phrase & No & Yes & Closed & Aural\\
-Listen \& Tone & Listening to a continuous tone & Yes & No & Closed & None\\
-Listen - ASSR & Listening to noise modulated at 40 Hz & Yes & No & Closed & None\\
-Face & Imagine a person's face & No & Yes & Closed & Visual\\
-Sequence & Imagine face, a number, and word on timed cues & Yes & Yes & Open & Visual\\
-\hline
-\end{tabularx}
-\caption{Properties of authentication tasks.
-We selected tasks with a variety of different properteries, but preferred tasks that did not require external stimuli, as the need to present such stimuli at authentication time could present challenges for usability, and user security.}
-\label{tab:addlabel}%
-\end{table}
+{\footnotesize \bibliographystyle{acm}
+\bibliography{references}}
 

### 2017-02-08 paper.tex
Proofs

@@
 reports of celebrity account hackings serve as regular reminders that
+single-factor authentication using passwords or other user-chosen secrets, 
 the currently dominant method of authentication in consumer applications, 
-single-factor authentication using passwords or other user-chosen secrets, 
-is faced by many challenges. Major industry players such as Google and
-Facebook have been strongly encouraging their users to adopt two-factor
+face many challenges. Major industry players such as Google and
+Facebook have strongly encouraged their users to adopt two-factor
 authentication (2FA). However, the need for users to submit two different 
@@
 iPhone has already implemented the necessary technologies to support device
-unlock using either a user-selected passcode or a fingerprint. Therefore the
+unlock using either a user-selected passcode or a fingerprint. The
 device could easily support a two-step two-factor authentication scheme if
@@
 
-In the present proposal, we will undertake, to the best of our knowledge, the first
+In this paper, we undertake, to the best of our knowledge, the first
 ever study of one-step three-factor authentication. In computer security,
@@
 
-We propose the use of custom-fit Ear EEG technology as the platform for
+We find that we can achieve good classification accuracy with a single earpiece containing only three electrodes. \underline{More result details.....}
+
+\section{Related work}
+
+We investigate custom-fit ear-EEG technology as the platform for
 investigating the feasibility, performance, and usability of one-step three-factor
-authentication. In addition to the same knowledge factor and inherence factor as
-in previous work, the user can submit in the same step the possession factor
+authentication. In addition to the dual knowledge and inherence factors in
+in previous work, this work includes a posession factor
 in the form of the EEG-sensing ear-piece(s) that are custom-fitted to and worn in
 their ear. These earpieces can serve as physical tokens in the same way as bank
-ATM cards and wearable hardware tokens. Furthermore, because the earpieces
+ATM cards and wearable hardware tokens. Because the earpieces
 are custom-fitted to each individual, they will likely not be able to produce good
@@
 
-\section{Related work}
+\underline{Brief outline of the rest of this lit review....}
 
@@
 We analyzed the EEG signals collected during the tasks using a support vector classifier (SVC).
-Since past work has shown that classification tasks in EEG-based BCI are linear \underline{Garrett2003a}, we used XGBoost, a tool for logistic linear classification \underline{Chen2016}.
+Since past work has shown that classification tasks in EEG-based BCI are linear \cite{Garrett2003a}, we used XGBoost, a tool for logistic linear classification \cite{Chen2016}.
 

### 2017-02-09 paper.tex
Updating study overview and some procedures

@@
 \subsection*{Abstract}
-In this paper, we present a system that provides 3-factors of authentication (knowledge, posession and inherence) in a single step, using brain-based authentication via a custom-fit, in-ear EEG.
-Across all subjects, we achieve a mean 0\% false acceptance and 0.12\% false rejection rate with data from only one earpiece.
-In a preliminary test of an ``imposter'' spoofing attack, we find a 0\% false acceptance rate.
-Our results indicate that in-ear EEG could provide a discrete, convenient, multifactor authentication.
+In this paper, we present a system that provides all three factors of authentication (knowledge, possession, and inherence) in a single step, using brain-based authentication via a custom-fit, in-ear EEG.
+Across all participants, we achieve mean 0\% false acceptance and 0.12\% false rejection rates with data from only one earpiece with three electrodes.
+In a preliminary test of an "imposter'' spoofing attack, we find a 0\% false acceptance rate.
+Our results indicate that in-ear EEG could provide a discreet, convenient, multi-factor authentication.
+(TO ADD: neural source of signal confirmation, usability summary)
 
@@
 critical to cybersecurity and privacy, now and into the future. Unfortunately,
-news 
-reports of celebrity account hackings serve as regular reminders that
+news reports of celebrity account hackings serve as regular reminders that
 single-factor authentication using passwords or other user-chosen secrets, 
@@
 
-In previous work, “one-step two-factor authentication” has been proposed as a
+In previous work, "one-step two-factor authentication" has been proposed as a
 new approach to authentication that can provide the security benefits of two-
@@
 impersonation attacks was demonstrated, including conditions where the attacker
-may have learned the target’s secret thought and/or secret task \cite{Johnson2014}.
+may have learned the target'۪s secret thought and/or secret task \cite{Johnson2014}.
 
-In this paper, we undertake, to the best of our knowledge, the first
+In this study we undertake, to the best of our knowledge, the first
 ever study of one-step three-factor authentication. In computer security,
@@
 \cite{Looney2012a,Kidmose2013a,Kidmose2013b}.
-United Sciences is currently developing a consumer ``hearable'' (in-ear wearable) called The Aware, which will measure EEG from the ear, among other biometrics \cite{UnitedSciences}.
+United Sciences is currently developing a consumer "hearable'' (in-ear wearable) called The Aware, which will measure EEG from the ear, among other biometrics \cite{UnitedSciences}.
 
@@
 schemes. In both cases, the knowledge factor (password or passphrase) and
-inherence factor (typing rhythm or speaker’s voice) are employed \cite{Monrose1997}.
+inherence factor (typing rhythm or speaker's voice) are employed \cite{Monrose1997}.
 In contrast, the Nymi band supports one-step two-factor authentication via the inherence
@@
 \label{sec:orgb483219}
-\subsection{Subjects}
+\subsection{Study Overview}
+
+7 male participants, 5 students and 2 non-students, completed our study protocol approved by the UC Berkeley Committee for Protection of Human Subjects (CPHS).
+The participant pool was limited due to the necessity of creating a pair of custom-fitted earpieces for each.
+There were three study visits per participant, the first to obtain 3D molds of participants' ears to use in creating the earpieces, the second to do a fit and impedance check once earpieces were manufactured, and a third to collect data using the earpieces while participants performed a set of mental tasks to be used in authentication analysis.
+Informed consent was obtained prior to study procedures.
+On the third study visit participants completed a short demographics questionnaire, a set up period with the openBCI and earpieces including a second impedance check, performed 9 mental tasks presented on a laptop, and finally a post-experiment questionnaire.
+Approximately two weeks after the third study visit, a subset of participants reported via e-mail whether or not they remembered the passthoughts they chose and performed.
+
 \label{sec:orgaf30da9}
-\subsection{{\bfseries\sffamily TODO} Tasks}
+\subsection{Tasks}
 
-\underline{Explain stuff around tasks}
+We used an expanded set of mental tasks with properties based on findings in related work regarding the relative strengths of different mental tasks in authentication accuracy and usability as reported by participants.
+Furthermore, given the in-ear placement of the electrodes and therefore the proximity to the temporal lobes containing the auditory cortex, we tested several novel authentication tasks based specifically on auditory imagery or stimuli.
+The nine authentication tasks and their attributes are listed in Table I.
+We purposefully selected tasks that captured a diversity of possibilities across the dimensions of external stimuli, involving a personalized secret, eyes open or closed (due to known significant effects on EEG), and different types of imagery.
 
@@
 \begin{tabularx}{\textwidth}{llllll}
-Task & Description & Stimuli? & Personal? & Eyes? & Imagery?\\
+Task & Description & Stimuli? & Secret? & Eyes & Imagery\\
 \hline
@@
 Speech & Imagining a spoken phrase & No & Yes & Closed & Aural\\
-Listen \& Tone & Listening to a continuous tone & Yes & No & Closed & None\\
 Listen - ASSR & Listening to noise modulated at 40 Hz & Yes & No & Closed & None\\
@@
 \end{tabularx}
-\caption{Properties of authentication tasks.
-We selected tasks with a variety of different properteries, but preferred tasks that did not require external stimuli, as the need to present such stimuli at authentication time could present challenges for usability, and user security.}
+\caption{Table I.
+Properties of authentication tasks.
+We selected tasks with a variety of different properties, but preferred tasks that did not require external stimuli, as the need to present such stimuli at authentication time could present challenges for usability, and user security.}
 \label{tab:addlabel}%
@@
 
-\subsection{Protocol}
+\subsection{Data Collection Protocol}
 \label{sec:org2041857}
-Our initial participants were recruited from a nearby university and scheduled for ear molding
-and impedance checking sessions. Finally, the data collection visit was scheduled and took
-approximately 90 minutes for set up and experiment execution. The OpenBCI system we used
+The data collection visit took approximately 90 minutes for set up and experiment execution. The OpenBCI system we used
 allows for 8 channels of simultaneous recording, along with separate ground and reference channels.
 Data was initially collected with the ground placed at the center of the forehead, and using the left
-mastoid as reference, though we can easily re-reference to another channel by subtracting a desired
-channel (such as right mastoid). Each earpiece (shown in the image below) contain three channels: 
-one placed on the helix, and two inside the canal - one front-facing and the other back-facing. The remaining
+mastoid as reference, though we later re-referenced to the right mastoid channel.
+Each earpiece (shown in the image below) contains three channels: one placed on the helix, and two inside the canal - one front-facing and the other back-facing.
+The remaining
 two channels were placed on the right mastoid for later re-referencing, and at approximately Fp1 (on the 
 forehead above the left eye) for validating the data collected in the ears against a scalp-based measure. 
-Before beginning the experiment, the data from all channels was visualized and participants were asked to
-blink and clench their jaws to confirm visibly that all channels were active and properly connected.
+Before beginning the experiment, the data from each channel was visually inspected and participants were asked to
+blink and clench their jaws to confirm that all channels were active and properly connected. Audio stimuli was delivered through small tubes in the earpieces opening into the ear canal.
 
@@
  tasks and reminded the participant of these for the second set of trials.
+
+ After the completion of the experiment, a subset of participants completed a usability questionnaire asking about the ease of performing, level of engagement, perceived repeatability, and likeliness of using each task.
+The questionnaire also asked participants to rank the tasks overall from most to least favorite, as well as several open response questions regarding potential use cases of ear EEG and this method of authentication, level of comfort wearing the earpieces, and any other comments they chose to provide.
 \section{Analysis}
 \label{sec:org6c1a839}
-\subsection{Validating the data}
+\subsection{Validating the data {\bfseries\sffamily TODO (Update beyond pilot participants}}
 \label{sec:org800f2bd}
@@
 
-\section{TODO Conclusion}
+\section{{\bfseries\sffamily TODO} Conclusion}
 

### 2017-02-09 paper.tex
Additions to discussion

@@
 Interestingly, no single electrode from the left or right ear performs as well as the aggregate left and right ear conditions. 
-Counter to our expectations, FP1 does not perform as well as most ear electrodes.
+Counter to our expectations, Fp1 does not perform as well as most ear electrodes.
 
@@
 
-Counter to our expectations, we found that referencing on the same side as the electrodes improves classification accuracy, compared to referencing on the other side of the head, as is commonly done in EEG.
-\underline{Theory as to why?} Furthermore, the use of conductive gel results in decent results (low impedances) on other subjects' custom-fit earpieces.
-This is somewhat surprising, since ear canals are believed to be more unique than fingerprints \underline{cite}.
-Finally, performance on FP1 was not as high as performance in the ear, despite FP1's popularity in past work on passthoughts \cite{Chuang2013b}.
-This could be explained by the greater number of electrodes in the ear (compared to just one on FP1).
-Another explanation might be in the neural activity required to perform the tasks we chose.
-Future work might shed light on this issue.
+Furthermore, the use of conductive gel results in low impedances on other subjects' custom-fit earpieces, despite the uniquness of ear canal shapes between individuals \cite{Akkermans2005}.
+Nevertheless, classifiers appear to resists spoofing attacks, indicating that task-related signals are unique to individuals.
+In the future, the custom-fit earbuds could include a hardware keypair to sign authentication attempts, providing a more secure method for establishing the posession factor in our three-factor, one-step scheme.
+
+Counter to our expectations, we found that referencing on the same side as the electrodes improves classification accuracy.
+This result implies that our tasks do not involve inter-hemispheric dynamics (if our tasks require symmetric neural activity, referencing to the other hemisphere would incorporate additional noise, explaining our finding).
+Since a single earpiece is more convenient from a usability and manufacturing standpoint, tasks with symmetric activity should be preferred in future work.
+
+Finally, performance on Fp1 was not as high as performance in the ear, despite Fp1's popularity in past work on passthoughts \cite{Chuang2013b}.
+This could be explained by the greater number of electrodes in the ear (compared to just one on Fp1).
+Additionally, Fp1 is best poised to pick up on frontal lobe activity (e..g, concentration), but our tasks did not generally involve frontal lobe activity; in fact, a good number of them involved audio, which we would expect to be better observed near the auditory cortex at the ears.
+Future work should continue to investigate what sorts of mental tasks lend themselves to in-ear recording.
 

### 2017-02-09 paper.tex
Added swapan's materials graf

@@
 \section{Methods}
-\label{sec:org63d105c}
-\subsection{{\bfseries\sffamily TODO} Manufacturing, materials}
-\label{sec:orgb483219}
+
+\subsection{Manufacturing and materials}
+
+Custom ear impressions were made by injecting silicon into the ear canal.
+A cotton ball with a string attached is placed into the ear canal first.
+When the silicon dries after a few minutes, the string is pulled to remove the impression from the ear canal.
+This impression is then scanned with a 3d scanner and the resulting scan modified based on some heuristics to achieve a comfortable fit and to ensure the intended electrode sites will make good contact with the skin.
+Channels are created in the 3d model to allow wire leads and associated EEG electrodes as well as a plastic tube to deliver audio.
+This 3d model is then sent to a 3d printer.
+Following this wires leads and associated AGCL electrodes are installed.
+
 \subsection{Study Overview}

### 2017-02-10 paper.tex
new title
Removed ASSR stuff

@@
 %make title bold and 14 pt font (Latex default is non-bold, 16 pt)
-\title{\Large \bf 3-Step, 1-Factor Authentication With Custom-Fit, In-Ear EEG}
+\title{\Large \bf One-Step, Three-Factor Authentication With Custom-Fit, In-Ear EEG}
 
@@
 Data was initially collected with the ground placed at the center of the forehead, and using the left
-mastoid as reference, though we later re-referenced to the right mastoid channel.
+mastoid as reference, though we later re-referenced to the right mastoid channel, so that our analysis reflects data from a single earpiece.
 Each earpiece (shown in the image below) contains three channels: one placed on the helix, and two inside the canal - one front-facing and the other back-facing.
@@
 The questionnaire also asked participants to rank the tasks overall from most to least favorite, as well as several open response questions regarding potential use cases of ear EEG and this method of authentication, level of comfort wearing the earpieces, and any other comments they chose to provide.
+
 \section{Analysis}
@@
 
-In this section, we establish that the data we collected were EEG signals with relatively low noise. 
-Using the pilot data from two participants, we were able to confirm the custom-fit earpieces are able to collect EEG
-data using three tests: good impedances measured for the ear electrodes, alpha-band activity attenuation when a
-participant's eyes were open versus closed, and the presence of a significant ASSR signal.
+In this section, we establish that the data we collected were of a neural origin, and had relatively little noise. 
+Using data from two participants, we were able to confirm the custom-fit earpieces are able to collect EEG
+data using three tests: good impedances measured for the ear electrodes, and alpha-band activity attenuation when a
+participant's eyes were open versus closed.
 
@@
 eyes open, blue indicates the same task with eyes closed.}
-\end{figure}
-
-Finally, for the ASSR test we calculated power spectra for data from the "Listen - ASSR" task. The audio stimulus used for this task is modulated 
-at 40 Hz, which should, in turn, produce an EEG response visible in the data at 40 Hz. Strangely, in our tests we do see an ASSR spike but it is located 
-around 74 Hz instead. While this has us somewhat perplexed about our stimulus, the purpose of this test was to ensure that the response seen in the ear channels 
-matched the response seen from the Fp1 recordings, which is evident comparing the figures below.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.5\textwidth]{figures/001_ASSR_Fp1.jpg}
-\caption{Power spectrum for data collected from the Fp1 channel during 40 Hz ASSR stimulus. An ASSR spike is clearly visible, though not at 40 Hz where it was expected.}
-\end{figure}
-
-\begin{figure}[h]
-  \centering
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{figures/001_ASSR_Left.jpg}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{figures/001_ASSR_Right.jpg}
-  \end{minipage}
-\caption{Power spectra for data collected from the earpiece channels during 40 Hz ASSR stimulus. Again, the spike is clearly visible though not at 40 Hz, however it 
-does match the activity measured at Fp1.}
 \end{figure}
@@
 
-\subsection{Imposter attack}
+\section{Imposter attack}
 
@@
 
-To explore this scenario, we chose one subject (subject 6), and referred to their report of chosen passsthoughts.
-We recorded spoofed passthoughts for two ``imposter'' subjects.
+To explore this scenario, we chose one subject (subject 6), and referred to their report of chosen passsthoughts. One subject, drawn from the initial pool, \underline{...methods..}.
+\underline{....results.....}
+
+However, since this subject's data appeared in the initial pool, the classifier may have been trained on his or her recordings as negative examples.
+To explore the efficacy of an outsider spoofing recordings, we repeated the same protocol with a subject who did not appear in our initial set of subjects.
+\underline{...results....}
+
+% We recorded spoofed passthoughts for two ``imposter'' subjects.
 One subject appeared in our initial pool performing their own passthoughts (subject 2), while the other subject did not appear in the initial pool, and thus was not included when training subject classifiers.
 (How well the imposters were able to spoof subject 6's passthought is an open question; see Discussion).
+% For each task, we ran the spoofed version of the task through the classifier trained on subject 6's task as the passthought. None of the spoofed passthoughts were accepted, resulting in a 0\% FAR.
 
-For each task, we ran the spoofed version of the task through the classifier trained on subject 6's task as the passthought.
-None of the spoofed passthoughts were accepted, resulting in a 0\% FAR.
-
-\subsection{{\bfseries\sffamily TODO} Usability}
-\label{sec:org18d5968}
+\section{{\bfseries\sffamily TODO} Usability}
 
@@
 In the future, the custom-fit earbuds could include a hardware keypair to sign authentication attempts, providing a more secure method for establishing the posession factor in our three-factor, one-step scheme.
-
-Counter to our expectations, we found that referencing on the same side as the electrodes improves classification accuracy.
-This result implies that our tasks do not involve inter-hemispheric dynamics (if our tasks require symmetric neural activity, referencing to the other hemisphere would incorporate additional noise, explaining our finding).
-Since a single earpiece is more convenient from a usability and manufacturing standpoint, tasks with symmetric activity should be preferred in future work.
 

### 2017-02-10 paper.tex
Expanded imposter section

@@
 Furthermore, given the in-ear placement of the electrodes and therefore the proximity to the temporal lobes containing the auditory cortex, we tested several novel authentication tasks based specifically on auditory imagery or stimuli.
-The nine authentication tasks and their attributes are listed in Table I.
+The nine authentication tasks and their attributes are listed in Table \ref{tab:tasks}.
 We purposefully selected tasks that captured a diversity of possibilities across the dimensions of external stimuli, involving a personalized secret, eyes open or closed (due to known significant effects on EEG), and different types of imagery.
@@
 Speech & Imagining a spoken phrase & No & Yes & Closed & Aural\\
-Listen - ASSR & Listening to noise modulated at 40 Hz & Yes & No & Closed & None\\
+Listen - Tone & Listening to noise modulated at 40 Hz & Yes & No & Closed & None\\
 Face & Imagine a person's face & No & Yes & Closed & Visual\\
@@
 \end{tabularx}
-\caption{Table I.
-Properties of authentication tasks.
+\caption{Properties of authentication tasks.
 We selected tasks with a variety of different properties, but preferred tasks that did not require external stimuli, as the need to present such stimuli at authentication time could present challenges for usability, and user security.}
-\label{tab:addlabel}%
+\label{tab:tasks}%
 \end{table*}
@@
 \hline
-0.0 & 0.0 & 1 & listennoise\\
-0.0 & 0.0 & 2 & breathe\\
-0.0 & 0.0 & 3 & breathe\\
-0.0 & 0.0 & 4 & breathe\\
-0.0 & 0.012 & 5 & breathe\\
-0.0 & 0.0 & 6 & breathe\\
-0.0 & 0.0 & 7 & breathe\\
+0.0 & 0.0 & 1 & Listen - noise\\
+0.0 & 0.0 & 2 & Breathe\\
+0.0 & 0.0 & 3 & Breathe\\
+0.0 & 0.0 & 4 & Breathe\\
+0.0 & 0.012 & 5 & Breathe\\
+0.0 & 0.0 & 6 & Breathe\\
+0.0 & 0.0 & 7 & Breathe\\
 \end{tabular}
@@
 
-To explore this scenario, we chose one subject (subject 6), and referred to their report of chosen passsthoughts. One subject, drawn from the initial pool, \underline{...methods..}.
-\underline{....results.....}
+To explore this scenario, we chose one subject (subject 6), and referred to their report of chosen passsthoughts.
+One subject, drawn from the initial subject pool, performed each of subject 6's passthoughts (simulating an ``inside imposter'').
+Following the same classification and preprocessing steps, we generated 200 samples per task for our imposter, using data from all left ear electrodes.
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{lll}
+Task & FAR (Insider) & FAR (Outsider)\\
+\hline
+Breathe & 0.0 & 0.0\\
+Breathe - Open & 0.0 & 0.0\\
+Sport \& & 0.0 & 0.0\\
+Song \& I & 0.0 & 0.0\\
+Song - Open & 0.0 & 0.0\\
+Speech \& & 0.0 & 0.0\\
+Listen - Tone & 0.0 & 0.0\\
+Face \& I & 0.0 & 0.0\\
+Sequence & 0.0 & 0.0\\
+\end{tabular}
+\end{center}
+\caption{False acceptance rate for spoofed versions of Subject 6's passthoughts, performed by an inside imposter (from the original subject pool) and an outsid eimposter (not from the original subject pool).}
+\label{tab:imposter}
+\end{table}
+
+Since every subject has one classifier per task (for which that task is the passthought), we are able to make 200 spoofed attempts with the correct passthought on each of subject 6's classifiers (Table \ref{tab:imposter}).
+We find no successful spoof attempts for tasks with a chosen secret (e.g., song, face).
+However, we also do not find any successful spoof attacks for tasks with no chosen secret (e.g., breathe).
+In all 1,800 spoof attempts (200 attempts for each of the 9 classifiers), we do not find a single successful attack on any of subject 6's classifiers.
 
 However, since this subject's data appeared in the initial pool, the classifier may have been trained on his or her recordings as negative examples.
-To explore the efficacy of an outsider spoofing recordings, we repeated the same protocol with a subject who did not appear in our initial set of subjects.
-\underline{...results....}
+To explore the efficacy of an outsider spoofing recordings, we repeated the same protocol with a subject who did not appear in our initial set of subjects (an ``outside imposter,'' Table \ref{tab:imposter}).
+Again, we do not find any successful authentication attempts.
 

### 2017-02-11 paper.tex
Updating parts of intro, tasks, collection protocol, and data validation.

@@
 type of authenticator, it represents the strongest level of authentication security
-possible.
+possible. The system we propose and test here uses the choice of a mental task
+or "passthought" to perform as knowledge, the uniqueness of an individual's brain
+activity as measured by EEG as inherence, and the physical token of custom-fit 
+earpieces which could easily contain a hardware key-pair as a possession factor.
+The ability to utilize all three of these security factors in a single step by performing 
+a mental task of a few seconds is a promising in pursuit of extremely strong security 
+while maintaining a low amount of effort and obtrusiveness to the user.
 
@@
 authentication. In addition to the dual knowledge and inherence factors in
-in previous work, this work includes a posession factor
+in previous work, this work includes a possession factor
 in the form of the EEG-sensing ear-piece(s) that are custom-fitted to and worn in
 their ear. These earpieces can serve as physical tokens in the same way as bank
-ATM cards and wearable hardware tokens. Because the earpieces
-are custom-fitted to each individual, they will likely not be able to produce good
-electrical impedances when worn by a different individual.
+ATM cards and wearable hardware tokens by implementing a hardware key-pair.
+Furthermore, because the earpieces are custom-fitted to each individual, we predicted 
+they would likely not be able to produce good electrical impedances when worn by a different individual.
 
@@
 
-\cite{curranpassthoughts} was the first to merge in-ear EEG with passthought authentication.
+\cite{curranpassthoughts} was the first to merge in-ear EEG with passthought authentication,
+ using a single modified consumer grade EEG device among participants and achieving approximately 80 percent authentication accuracy.
 
@@
 
-Custom ear impressions were made by injecting silicon into the ear canal.
+Custom ear impressions were made by cleaning and injecting silicon into the ear canal.
 A cotton ball with a string attached is placed into the ear canal first.
 When the silicon dries after a few minutes, the string is pulled to remove the impression from the ear canal.
-This impression is then scanned with a 3d scanner and the resulting scan modified based on some heuristics to achieve a comfortable fit and to ensure the intended electrode sites will make good contact with the skin.
+This impression is then scanned with a 3D scanner and the resulting scan modified based on some heuristics to achieve a comfortable fit and to ensure the intended electrode sites will make good contact with the skin.
 Channels are created in the 3d model to allow wire leads and associated EEG electrodes as well as a plastic tube to deliver audio.
@@
 
+\underline{Is there specifics on how the exactly positions of the electrodes on these pieces were chosen? If not, can simply mention 2 in the ear canal and 1 on the outer ear (helix) }
+
 \subsection{Study Overview}
@@
 7 male participants, 5 students and 2 non-students, completed our study protocol approved by the UC Berkeley Committee for Protection of Human Subjects (CPHS).
-The participant pool was limited due to the necessity of creating a pair of custom-fitted earpieces for each.
-There were three study visits per participant, the first to obtain 3D molds of participants' ears to use in creating the earpieces, the second to do a fit and impedance check once earpieces were manufactured, and a third to collect data using the earpieces while participants performed a set of mental tasks to be used in authentication analysis.
+Three study visits took place per participant, in the first the 3D molds of participants' ears to use in creating the earpieces were obtained, the second to do a fit and electrical impedance check once earpieces were manufactured, and a third to collect data using the earpieces while participants performed a set of mental tasks to be used in authentication analysis.
 Informed consent was obtained prior to study procedures.
-On the third study visit participants completed a short demographics questionnaire, a set up period with the openBCI and earpieces including a second impedance check, performed 9 mental tasks presented on a laptop, and finally a post-experiment questionnaire.
+The third study visit consisted of participants completing a short demographics questionnaire, a set up period with the openBCI system and earpieces including a second impedance check, the performance of 9 mental tasks presented on a laptop, and finally a post-experiment questionnaire.
 Approximately two weeks after the third study visit, a subset of participants reported via e-mail whether or not they remembered the passthoughts they chose and performed.
@@
 
-We used an expanded set of mental tasks with properties based on findings in related work regarding the relative strengths of different mental tasks in authentication accuracy and usability as reported by participants.
+We used a set of mental tasks based on findings in related work regarding the relative strengths of different mental tasks in authentication accuracy and usability as reported by participants.
 Furthermore, given the in-ear placement of the electrodes and therefore the proximity to the temporal lobes containing the auditory cortex, we tested several novel authentication tasks based specifically on auditory imagery or stimuli.
-The nine authentication tasks and their attributes are listed in Table \ref{tab:tasks}.
-We purposefully selected tasks that captured a diversity of possibilities across the dimensions of external stimuli, involving a personalized secret, eyes open or closed (due to known significant effects on EEG), and different types of imagery.
+The 9 authentication tasks and their attributes are listed in Table \ref{tab:tasks}.
+Our strategy was to select tasks that captured a diversity of possibilities across the dimensions of external stimuli, involving a personal secret, eyes open or closed (due to known significant effects on EEG), and different types of mental imagery.
 
@@
 Speech & Imagining a spoken phrase & No & Yes & Closed & Aural\\
-Listen - Tone & Listening to noise modulated at 40 Hz & Yes & No & Closed & None\\
+Listen - Noise & Listening to noise modulated at 40 Hz & Yes & No & Closed & None\\
 Face & Imagine a person's face & No & Yes & Closed & Visual\\
@@
 \caption{Properties of authentication tasks.
-We selected tasks with a variety of different properties, but preferred tasks that did not require external stimuli, as the need to present such stimuli at authentication time could present challenges for usability, and user security.}
+We selected tasks with a variety of different properties, but preferred tasks that did not require external stimuli, as the need to present such stimuli at authentication time could present challenges for usability and user security.}
 \label{tab:tasks}%
@@
 \label{sec:org2041857}
-The data collection visit took approximately 90 minutes for set up and experiment execution. The OpenBCI system we used
-allows for 8 channels of simultaneous recording, along with separate ground and reference channels.
-Data was initially collected with the ground placed at the center of the forehead, and using the left
-mastoid as reference, though we later re-referenced to the right mastoid channel, so that our analysis reflects data from a single earpiece.
-Each earpiece (shown in the image below) contains three channels: one placed on the helix, and two inside the canal - one front-facing and the other back-facing.
-The remaining
-two channels were placed on the right mastoid for later re-referencing, and at approximately Fp1 (on the 
-forehead above the left eye) for validating the data collected in the ears against a scalp-based measure. 
-Before beginning the experiment, the data from each channel was visually inspected and participants were asked to
-blink and clench their jaws to confirm that all channels were active and properly connected. Audio stimuli was delivered through small tubes in the earpieces opening into the ear canal.
+The data collection visit took approximately 90 minutes for set up and experiment execution.
+All collection sites were cleaned with ethanol prior to electrode placement, and a small amount of conductive gel was used on each electrode.
+For EEG recording we used OpenBCI \cite{OpenBCI}, an open-source biosensing system to maintain an overall low cost our set up.
+OpenBCI has a price tag of about \$600, and thus is an affordable alternative to medical-grade EEG systems that can cost tens of thousands of dollars.
+Recent work has demonstrated the robustness of OpenBCI compared to an industry standard medical-grade EEG system, particularly for non-medical use cases such as ours \cite{Frey2016}.
+The OpenBCI system we used allows for 8 channels of simultaneous recording, along with separate ground and reference channels.
+Data was initially collected with the ground placed at the center of the forehead (a common approach to not bias one side of the head over the other), and using the left mastoid as reference, though we later re-referenced to the right mastoid channel so that our analysis reflects data from a single earpiece.
+Each earpiece (shown in the image below) contains three channels: one placed on the helix, and two inside the canal - one on the anterior canal wall (front-facing) and the other on the posterior wall (back-facing).
+The remaining two channels, AGCL ring electrodes, were placed on the right mastoid for later re-referencing, and at approximately Fp1 (the forehead above the left eye) for validating the data collected in the ears against a scalp-based placement.
+Before beginning the experiment, the data from each channel was visually inspected using the OpenBCI GUI and participants were asked to blink and clench their jaws to confirm that all channels were active and properly connected.
+Audio stimuli were delivered through small tubes in the earpieces opening into the ear canal.
 
@@
 In this section, we establish that the data we collected were of a neural origin, and had relatively little noise.
-Using data from two participants, we were able to confirm the custom-fit earpieces are able to collect EEG
-data using three tests: good impedances measured for the ear electrodes, and alpha-band activity attenuation when a
-participant's eyes were open versus closed.
+We were able to confirm the custom-fit earpieces are able to collect EEG data using two tests: good impedances measured for the ear electrodes, and alpha-band activity attenuation when a participant's eyes were open versus closed.
+
+The first quality check was examining the electrical impedances achieved for the ear pieces as a low impedance (<10 kOhm) 
+is best for obtaining quality EEG signals.
+Table \ref{tab:impedances} below summarizes the impedances across the seven participants' six ear channels.
+With the exception of a few channels in select participants, impedances achieved were overall very good.
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{lrrrrrr}
+& \multicolumn{6}{c}{Impedances [kOhm]} \\
+\cline{2-7}
+& \multicolumn{3}{|c|}{Left ear} & \multicolumn{3}{c|}{Right ear} \\
+Subject & Helix & Front & Back & Helix & Front & Back \\
+\hline
+1 & 4 & 4 & 4 & \textless1 & 4 & 3\\
+2 & 9 & 5 & 4 & 3 & 4 & 4\\
+3 & 4 & 5 & 4 & 9 & 6 & 9\\
+4 & 4 & 5 & 4 & 3 & 16 & 9\\
+5 & 9 & 20 & 7 & 3 & 7 & 9\\
+6 & 5 & 8 & 2 & 1 & 1 & 9\\
+7 & 2 & 9 & 8 & 7 & 5 & 6\\
+\end{tabular}
+\end{center}
+\caption{Electrical impedances measured for earpiece electrodes.}
+\label{tab:impedances}
+\end{table}
 
@@
 known feature of EEG data that activity in the alpha-band (approximately 8-12 Hz range) increases when the eyes are closed
-compared with a similar state with eyes open. For both of our pilot participants this attenuation is clearly visible even in just
+compared with a similar state with eyes open. For our participants, this attenuation is clearly visible even in just
 a single trial's data. To further validate, we also performed this calculation on the data collected from the Fp1 electrode and see
@@
 real-world deployment of this authentication method however, as it will likely require pieces worn on or around both ears to properly 
-function, and not just one. The figures below show the alpha attenuation in the left and right ear channels, as well as Fp1.
+function, and not just one. The figures below show the alpha attenuation in the left and right ear channels, as well as Fp1 of one participant for example.
 

### 2017-02-11 paper.tex
small proofs

@@
 
-We find that we can achieve good classification accuracy with a single earpiece containing only three electrodes. \underline{More result details.....}
+We find that we can achieve good classification accuracy with a single earpiece containing only three electrodes.
+\underline{More result details.....}
 
@@
 they would likely not be able to produce good electrical impedances when worn by a different individual.
-
-\underline{Brief outline of the rest of this lit review....}
 
@@
 This impression is then scanned with a 3D scanner and the resulting scan modified based on some heuristics to achieve a comfortable fit and to ensure the intended electrode sites will make good contact with the skin.
-Channels are created in the 3d model to allow wire leads and associated EEG electrodes as well as a plastic tube to deliver audio.
-This 3d model is then sent to a 3d printer.
+Channels are created in the 3D model to allow wire leads and associated EEG electrodes as well as a plastic tube to deliver audio.
+This 3D model is then sent to a 3D printer.
 Following this wires leads and associated AGCL electrodes are installed.

### 2017-02-12 paper.tex
Updating earpiece figure

@@
 \centering
-\includegraphics[width=.9\linewidth]{./figures/2EEEG.jpg}
-\caption{Pair of custom-fit earpieces with 3 embedded electrodes each located at the helix and front-facing and back-facing within the ear canal.}
+\includegraphics[width=.9\linewidth]{./figures/CFEEEG_piecefig_Right.jpg}
+\caption{Example of right ear custom-fit earpieces with 3 embedded electrodes located at the helix, and front-facing in the ear canal, and back-facing in the ear canal.}
 \end{figure}
@@
 
-\underline{Is there specifics on how the exactly positions of the electrodes on these pieces were chosen? If not, can simply mention 2 in the ear canal and 1 on the outer ear (helix) }
+***Is there specifics on how the exactly positions
+of the electrodes on these pieces were chosen? If not,
+can simply mention 2 in the ear canal and 1 on the outer ear (helix)***
 

### 2017-02-13 paper.tex
Updating Usability and Imposter sections

@@
 \author{
-{\rm Your N.\ Here}\\
+{\rm First Name}\\
 Your Institution
@@
 Second Institution
+\and
+{\rm Third Name}\\
+Third Institution
+\and
+{\rm Fourth Name}\\
+Fourth Institution
 % copy the following lines to add more authors
@@
 \begin{tabular}{lrrrrrr}
-& \multicolumn{6}{c}{Impedances [kOhm]} \\
+& \multicolumn{6}{c}{Impedances [k\(\Omega\)]} \\
 \cline{2-7}
 & \multicolumn{3}{|c|}{Left ear} & \multicolumn{3}{c|}{Right ear} \\
-Subject & Helix & Front & Back & Helix & Front & Back \\
+Participant & Helix & Front & Back & Helix & Front & Back \\
 \hline
@@
 
-We trained the classifier using a balanced sample of positive and negative examples, where positive examples were from the target subject and target task, and negative examples were randomly selected tasks from any subject besides the target subject.
+We trained the classifier using a balanced sample of positive and negative examples, where positive examples were from the target participant and target task, and negative examples were randomly selected tasks from any participant besides the target participant.
 From this corpus of positive and negative samples, we withheld one third of data for testing. 
@@
 
-For each configuration of electrodes, we calculated the mean FAR and FRR across all subjects using each task as the passthought (Figure \ref{fig:meanByElectrode}).
+For each configuration of electrodes, we calculated the mean FAR and FRR across all participants using each task as the passthought (Figure \ref{fig:meanByElectrode}).
 Incorporating all electrodes data results in a perfect score for all tasks.
@@
 
-In the previous section, we trained and tested a passthought classifier with each task as the passthought, for all subjects.
+In the previous section, we trained and tested a passthought classifier with each task as the passthought, for all participants.
 Focusing on the left ear, we filter our results for the best-performing tasks.
@@
 \begin{tabular}{rrrl}
-FAR & FRR & subject & task\\
+FAR & FRR & Participant & Task\\
 \hline
@@
 Breathe appeared as the best task across all participants.
-Given our training strategy, these results indicate that a given person's breathe task is distinguishable not only among other tasks, but among breathe tasks from other subjects.
-All best-performing tasks in our set achieved perfect FAR and FRRs, with the exception of subject 5, whose best-performing task (breathe) had a nonzero FRR.
+Given our training strategy, these results indicate that a given person's breathe task is distinguishable not only among other tasks, but among breathe tasks from other participants.
+All best-performing tasks in our set achieved perfect FAR and FRRs, with the exception of P5, whose best-performing task (breathe) had a nonzero FRR.
 
-These results establish good performance in our original training strategy, in which we count as negative examples recordings from the wrong subject performing any task.
-For comparison, we try two additional training strategies: one in which negative examples are the correct task recorded from the wrong subject (within-tasks), and one in which negative examples are the incorrect task recorded from the correct subject (within-subjects).
+These results establish good performance in our original training strategy, in which we count as negative examples recordings from the wrong participant performing any task.
+For comparison, we try two additional training strategies: one in which negative examples are the correct task recorded from the wrong participant (within-tasks), and one in which negative examples are the incorrect task recorded from the correct participant (within-participants).
 
@@
 \begin{tabular}{lrrr}
- & Original & Within-tasks & Within-subjects\\
+ & Original & Within-tasks & Within-participants\\
 \hline
@@
 \end{center}
-\caption{Mean FAR and FRR for all subjects and pssthoughts across three different training strategies.}
+\caption{Mean FAR and FRR for all participants and passthoughts across three different training strategies.}
 \label{tab:compare}
@@
 
-Overall, our original training strategy achieves the lowest FAR (Table \ref{tab:compare}). Within-tasks FAR ten times higher, and within-subjects FAR is one hundred times higher.
-However, FRR is \textit{lower} in the within-tasks training strategy than in our original strategy's FRR. Within-subjects again results in the highest FRR.
+Overall, our original training strategy achieves the lowest FAR (Table \ref{tab:compare}). Within-tasks FAR ten times higher, and within-participants FAR is one hundred times higher.
+However, FRR is \textit{lower} in the within-tasks training strategy than in our original strategy's FRR. Within-participants again results in the highest FRR.
+
+\subsection{Usability}
+
+A subset of four participants completed our usability questionnaire.
+This questionnaire asked them to rank each of the mental tasks on 7-point likert-type scales on ease of use, level of engagement, perceived repeatability, and likeliness to use in a real-world authentication setting.
+The breathe and listen (\(\mu\)=6.75) tasks were ranked easiest to use, while the sequence (\(\mu\)=2.25) and face (\(\mu\)=2.75) tasks were ranked the most difficult.
+Sequence was rated highly in engagement however (\(\mu\)=5), as was the song task (\(\mu\)=5), while breathe-open and listen-noise were ranked least engaging (\(\mu\)=2.25).
+Breathe (\(\mu\)=7) and listen-noise (\(\mu\)=6.75) were ranked highest in repeatability, with sequence (\(\mu\)=2.5) along with face and sport (\(\mu\)=3) ranked least repeatable.
+Finally in terms of likeliness of use for authentication, song-open (\(\mu\)=5) and sequence (\(\mu\)=4.25) performed highest though modestly, while breathe (\(\mu\)=2.75) and listen-noise (\(\mu\)=3) were rated least likely to use.
+In addition to these rating scales we asked participants to rank the tasks from most (1) to least (9) favorite overall.
+The song-open task ranked highest among favorites (\(\mu\)=4.25) followed by a tie between breathe-open, song, and speech (\(\mu\)=4.75).
+In line with some of the results above, sequence (\(\mu\)=7.75) and face (\(\mu\)=6.75) were rated as least favorites.
+
+In addition to the scales and rankings, we included in our questionnaire a few open response questions to ascertain attitudes about the use cases for in-ear EEG and passthoughts, and the comfort of wearing an in-ear EEG device in everyday life.
+Participants first read the prompt, "Imagine a commercially available wireless earbud product is now available based on this technology that you've just experienced.
+It requires minimal effort for you to put on and wear.", and were asked about use cases for in-ear EEG and passthoughts.
+Responses about in-ear EEG expectedly included authentication for unlocking a phone or computer and building access, but also aspects of self-improvement such as P4's response "Help people increase focus and productivity".
+P5 and P6 also indicated a use for measuring engagement with media like movies and music, and relatedly P4 wrote "music playback optimized for current mental state and feelings".
+In terms of comfort wearing such a device, participants generally responded they would be comfortable, though P5 and P6 stipulated only when they would otherwise be wearing something like earphones in their ears already.
+In response to an "any other comments" prompt, notably three participants pointed out the mental imagery of a face was difficult for them and some concerns about their ability to repeat tasks in the same exact way each time.
+
+A final component of usability we measured was the ability of the participants to recall their specific chosen passthoughts for the song, sport, speech, face, and sequence tasks.
+Participants were contacted approximately two weeks after their data collection study visit and were prompted with these categories and asked to respond with what they remembered their choices being.
+As evidenced by their responses, all participants were able to recall all of their chosen secrets, with the exception of one participant who incorrectly remembered their chosen word for the sequence task.
 
@@
 
-While our left-ear results establish that passthoughts achieve low FAR and FRR when tested against other subjects' passthoughts, we do not know how robust passthoughts are against a spoofing attack, in which both a subject's custom-fit electrode, and details of that subject's chosen passthought, are leaked.
+While our left-ear results establish that passthoughts achieve low FAR and FRR when tested against other participants' passthoughts, we do not know how robust passthoughts are against a spoofing attack, in which both a participant's custom-fit electrode, and details of that participant's chosen passthought, are leaked.
 
-To explore this scenario, we chose one subject (subject 6), and referred to their report of chosen passsthoughts.
-One subject, drawn from the initial subject pool, performed each of subject 6's passthoughts (simulating an ``inside imposter'').
-Following the same classification and preprocessing steps, we generated 200 samples per task for our imposter, using data from all left ear electrodes.
+The first aspect of this scenario we tested was the ability of an imposter to wear an earpiece acquired from someone else and achieve viable impedance values for EEG collection.
+P1 tried on each of the other participants' earpieces, which firstly were able to fit at least somewhat in P1's ears.
+The impedances of P1 wearing other participants' earpieces were then recorded and are listed in Table \ref{tab:imposter_impedances} below.
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{lrrrrrr}
+& \multicolumn{6}{c}{Impedances [k\(\Omega\)]} \\
+\cline{2-7}
+& \multicolumn{3}{|c|}{Left ear} & \multicolumn{3}{c|}{Right ear} \\
+Participant & Helix & Front & Back & Helix & Front & Back \\
+\hline
+2 & 34.1 & 10.2 & 12.8 & 27.8 & 16.0 & 16.3\\
+3 & 21.1 & 20.9 & 19.0 & 13.5 & 11.3 & 19.5\\
+4 & 14.1 & 11.9 & 9.7 & 11.0 & 11.1 & 13.3\\
+5 & 17.2 & 21.9 & 10.3 & 32.6 & 12.5 & 11.6\\
+6 & 18.7 & 10.0 & 8.4 & 14.8 & 11.5 & 8.9\\
+7 & 91.5 & \textgreater1000 & 21.5 & 33.5 & 26.4 & 31.0\\
+\end{tabular}
+\end{center}
+\caption{Electrical impedances measured while P1 wore each other participant's custom-fitted earpieces.}
+\label{tab:imposter_impedances}
+\end{table}
+
+To explore the scenario of an imposter attempting to gain access, we chose the worst case participant, P6, whose earpieces P1 had the lowest impedances wearing.
+We collected data using the same data collection protocol, but had P1 refer to P6's report of chosen passsthoughts.
+P1 performed each of P6's passthoughts (simulating an ``inside imposter'').
+Following the same classification and preprocessing steps, we generated 200 samples per task for our imposters, using data from all left ear electrodes.
 
@@
 \end{center}
-\caption{False acceptance rate for spoofed versions of Subject 6's passthoughts, performed by an inside imposter (from the original subject pool) and an outsid eimposter (not from the original subject pool).}
+\caption{False acceptance rate for spoofed versions of P6's passthoughts, performed by an inside imposter (P1 from the original participant pool) and an outside imposter (not from the original participant pool).}
 \label{tab:imposter}
@@
 
-Since every subject has one classifier per task (for which that task is the passthought), we are able to make 200 spoofed attempts with the correct passthought on each of subject 6's classifiers (Table \ref{tab:imposter}).
+Since every participant has one classifier per task (for which that task is the passthought), we are able to make 200 spoofed attempts with the correct passthought on each of P6's classifiers (Table \ref{tab:imposter}).
 We find no successful spoof attempts for tasks with a chosen secret (e.g., song, face).
 However, we also do not find any successful spoof attacks for tasks with no chosen secret (e.g., breathe).
-In all 1,800 spoof attempts (200 attempts for each of the 9 classifiers), we do not find a single successful attack on any of subject 6's classifiers.
+In all 1,800 spoof attempts (200 attempts for each of the 9 classifiers), we do not find a single successful attack on any of P6's classifiers.
 
-However, since this subject's data appeared in the initial pool, the classifier may have been trained on his or her recordings as negative examples.
-To explore the efficacy of an outsider spoofing recordings, we repeated the same protocol with a subject who did not appear in our initial set of subjects (an ``outside imposter,'' Table \ref{tab:imposter}).
+However, since this participant's data appeared in the initial pool, the classifier may have been trained on his or her recordings as negative examples.
+To explore the efficacy of an outsider spoofing recordings, we repeated the same protocol with an individual who did not appear in our initial set of participants (an ``outside imposter,'' Table \ref{tab:imposter}).
 Again, we do not find any successful authentication attempts.
@@
 
-\section{{\bfseries\sffamily TODO} Usability}
-
-\underline{Quantitative and qualitative data, where appropriate}
-
 \section{Discussion}
@@
 Our findings demonstrate the apparent feasibility of single earpiece, achieving good results with only three electrodes and a reference, all on the left ear.
-FARs and FRRs are low across all subjects and tasks, with FARs overall lower than FRRs.
-Subjects' best-performing passthoughts typically seeing no errors in our training.
+FARs and FRRs are low across all participants and tasks, with FARs overall lower than FRRs.
+Participants' best-performing passthoughts typically seeing no errors in our training.
 Furthermore, no spoofed attacks were successful in our cursory analysis.
@@
 The powerful interactions between inherence and knowledge emerged in our spoofing attack.
-Although our target subject documented their chosen passthought, the spoofers found ambiguity in how these passthoughts could be expressed.
-For the face task, the spoofers did not know the friend the original subject had chosen.
-For the song tasks, though the song was known, the spoofers did not know what part of the song the original subject had imagined, or how it was imagined (humming, imagining a full performance, melody, vocals, etc).
+Although our target participant documented their chosen passthought, the spoofers found ambiguity in how these passthoughts could be expressed.
+For the face task, the spoofers did not know the friend the original participant had chosen.
+For the song tasks, though the song was known, the spoofers did not know what part of the song the original participant had imagined, or how it was imagined (humming, imagining a full performance, melody, vocals, etc).
 This experience sheds light on the highly individual nature of passthoughts, and provides a positive indication that there may be some intrinsic difficulty ofr spoofing passthoughts.
@@
 First, \textit{breathe} tended to be the best-performing task among participants.
-Classifiers overall distinguished the breath task even compared to breath tasks from other subjects, implying that the task is expressed differently for each subject, i.e.
+Classifiers overall distinguished the breath task even compared to breath tasks from other participants, implying that the task is expressed differently for each participant, i.e.
 that this task has an inherence factor sufficient for authentication, even though the task does not have a knowledge factor.
@@
 
-Furthermore, the use of conductive gel results in low impedances on other subjects' custom-fit earpieces, despite the uniquness of ear canal shapes between individuals \cite{Akkermans2005}.
+Furthermore, the use of conductive gel results in low impedances on other participants' custom-fit earpieces, despite the uniquness of ear canal shapes between individuals \cite{Akkermans2005}.
 Nevertheless, classifiers appear to resists spoofing attacks, indicating that task-related signals are unique to individuals.

### 2017-02-14 paper.tex
Updating validation section, fixing CPHS, describing fp1/AFz, fixing fig 1 caption, changing listen-noise to listen

@@
 \includegraphics[width=.9\linewidth]{./figures/CFEEEG_piecefig_Right.jpg}
-\caption{Example of right ear custom-fit earpieces with 3 embedded electrodes located at the helix, and front-facing in the ear canal, and back-facing in the ear canal.}
+\caption{Labeled photo of one of our manufactured right ear custom-fit earpieces with 3 embedded electrodes located at the helix, and front-facing in the ear canal, and back-facing in the ear canal.}
 \end{figure}
@@
 
-7 male participants, 5 students and 2 non-students, completed our study protocol approved by the UC Berkeley Committee for Protection of Human Subjects (CPHS).
+7 male participants (P1-P7), 5 students and 2 non-students, completed our study protocol that was approved by our local Institutional Review Board.
 Three study visits took place per participant, in the first the 3D molds of participants' ears to use in creating the earpieces were obtained, the second to do a fit and electrical impedance check once earpieces were manufactured, and a third to collect data using the earpieces while participants performed a set of mental tasks to be used in authentication analysis.
@@
 Speech & Imagining a spoken phrase & No & Yes & Closed & Aural\\
-Listen - Noise & Listening to noise modulated at 40 Hz & Yes & No & Closed & None\\
+Listen & Listening to noise modulated at 40 Hz & Yes & No & Closed & None\\
 Face & Imagine a person's face & No & Yes & Closed & Visual\\
@@
 The OpenBCI system we used allows for 8 channels of simultaneous recording, along with separate ground and reference channels.
-Data was initially collected with the ground placed at the center of the forehead (a common approach to not bias one side of the head over the other), and using the left mastoid as reference, though we later re-referenced to the right mastoid channel so that our analysis reflects data from a single earpiece.
-Each earpiece (shown in the image below) contains three channels: one placed on the helix, and two inside the canal - one on the anterior canal wall (front-facing) and the other on the posterior wall (back-facing).
-The remaining two channels, AGCL ring electrodes, were placed on the right mastoid for later re-referencing, and at approximately Fp1 (the forehead above the left eye) for validating the data collected in the ears against a scalp-based placement.
+Data was collected with the ground placed at the center of the forehead, approximately AFz according to the 10-20 International Standard for Electrode Placement (ISEP), and using the left mastoid as reference.
+Notably, when examining data from the right earpiece, we re-referenced to the right mastoid channel so that our results reflect data from a single earpiece.
+Each earpiece (shown in Figure 1) contains three channels: one placed on the helix, and two inside the canal - one on the anterior canal wall (front-facing) and the other on the posterior wall (back-facing).
+The remaining two channels, AGCL ring electrodes, were placed on the right mastoid for later re-referencing, and at approximately Fp1 (left frontal lobe region, above the left eye in accordance with the ISEP) for validating the data collected in the ears against a common scalp-based placement.
 Before beginning the experiment, the data from each channel was visually inspected using the OpenBCI GUI and participants were asked to blink and clench their jaws to confirm that all channels were active and properly connected.
@@
 \label{sec:org6c1a839}
-\subsection{Validating the data {\bfseries\sffamily TODO (Update beyond pilot participants}}
+\subsection{Data Validation}
 \label{sec:org800f2bd}
@@
 Table \ref{tab:impedances} below summarizes the impedances across the seven participants' six ear channels.
-With the exception of a few channels in select participants, impedances achieved were overall very good.
+With the exception of a few channels in select participants, impedances achieved were overall good.
 
@@
 & \multicolumn{3}{|c|}{Left ear} & \multicolumn{3}{c|}{Right ear} \\
-Participant & Helix & Front & Back & Helix & Front & Back \\
+P & Helix & Front & Back & Helix & Front & Back \\
 \hline
@@
 
-The recorded impedances of the earpiece electrodes were less than 5 kOhms except one, a benchmark used widely in previous
-ear EEG work. The left helix electrode of one participant was measured at 9 kOhms, and generally the 
-helix impedances for both participants were higher than their ear canal counterparts. We expected this result, given that the
-helix electrode relies on quality of the earpiece's fit outside the ear for good contact, and is not as securely and tightly placed as the
-electrodes within the ear canal. Nonetheless, the data from all electrodes were tested in the remaining two data quality tests.
+Most of the recorded impedances of the earpiece electrodes were less than 5 k\(\Omega\), a benchmark used widely in previous
+ear EEG work, and all except two were less than 10 k\(\Omega\). Nonetheless, the data from all electrodes were tested in the remaining two data quality tests.
 
@@
 a single trial's data. To further validate, we also performed this calculation on the data collected from the Fp1 electrode and see
-the effect clearly here as well. It is important to note that the left ear results are reported using the right mastoid as reference, and
-the right ear results in turn using the left mastoid as reference. When using the same side mastoid for reference the effect is not 
-visible, though it may be if we average across many trials. This is not surprising, as the further a reference electrode is from the active
-channel the less "real" signal is being subtracted from the active channel. This has important design implications for eventual 
-real-world deployment of this authentication method however, as it will likely require pieces worn on or around both ears to properly 
-function, and not just one. The figures below show the alpha attenuation in the left and right ear channels, as well as Fp1 of one participant for example.
+the effect clearly here as well.
+The figure below shows the alpha attenuation in the left ear channels, as well as Fp1 of one participant as an example.
+We see the same effect in the right ear channels referenced to the right mastoid.
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{figures/001_AlphaAtt_Fp1.jpg}
-\caption{Alpha-attenuation (8-12 Hz range) in Fp1 channel, referenced at left mastoid, for comparison to ear channels. Red indicates breathing data with
-eyes open, blue indicates the same task with eyes closed.}
-\end{figure}
-
-\begin{figure}[h]
-  \centering
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{figures/001_AlphaAtt_Left.jpg}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[b]{0.45\textwidth}
-    \includegraphics[width=\textwidth]{figures/001_AlphaAtt_Right.jpg}
-  \end{minipage}
-\caption{Alpha-attenuation (8-12 Hz range) in left and right ear canal channels, referenced at opposite mastoids respectfully. Red indicates breathing data with
-eyes open, blue indicates the same task with eyes closed.}
+\includegraphics[width=0.5\textwidth]{figures/002_AlphaAtt_all.jpg}
+\caption{Alpha-attenuation (8-12 Hz range) in left ear channels compared against the Fp1 channel, referenced at left mastoid.
+Red indicates breathing data with eyes open, blue indicates the same task with eyes closed.}
 \end{figure}
@@
 To produce feature vectors, we took slices of 100 raw values from each electrode (about 500ms of data), and performed an FFT to produce power spectra for each electrode during that slice.
-We concatenated all electrode power spectra together, and performed PCA on all concatenated vectors such that the resulting vectors described 95\% of the variance in the full power specrum data.
+We concatenated all electrode power spectra together, and performed PCA on all concatenated vectors such that the resulting vectors described 95\% of the variance in the full power spectrum data.
 For each task, for each participant, 100 seconds of data were collected in total across 10 trials of 10 seconds each, resulting in 200 samples per participant, per task, following preprocessing.
@@
 The remaining training set was fed into a XGBoost's cross-validation method, which we set to iteratively tweak parameters over a maximum of fifty rounds of cross-validation to minimize classification error.
-After cross-validation, the updated classifier (with paramters applied) predicted labels on each sample in the test set, and we calculated FAR and FRR on its results.
+After cross-validation, the updated classifier (with parameters applied) predicted labels on each sample in the test set, and we calculated FAR and FRR on its results.
 
@@
 \begin{tabular}{rrrl}
-FAR & FRR & Participant & Task\\
+FAR & FRR & P & Task\\
 \hline
-0.0 & 0.0 & 1 & Listen - noise\\
+0.0 & 0.0 & 1 & Listen\\
 0.0 & 0.0 & 2 & Breathe\\
@@
 The breathe and listen (\(\mu\)=6.75) tasks were ranked easiest to use, while the sequence (\(\mu\)=2.25) and face (\(\mu\)=2.75) tasks were ranked the most difficult.
-Sequence was rated highly in engagement however (\(\mu\)=5), as was the song task (\(\mu\)=5), while breathe-open and listen-noise were ranked least engaging (\(\mu\)=2.25).
-Breathe (\(\mu\)=7) and listen-noise (\(\mu\)=6.75) were ranked highest in repeatability, with sequence (\(\mu\)=2.5) along with face and sport (\(\mu\)=3) ranked least repeatable.
-Finally in terms of likeliness of use for authentication, song-open (\(\mu\)=5) and sequence (\(\mu\)=4.25) performed highest though modestly, while breathe (\(\mu\)=2.75) and listen-noise (\(\mu\)=3) were rated least likely to use.
+Sequence was rated highly in engagement however (\(\mu\)=5), as was the song task (\(\mu\)=5), while breathe-open and listen were ranked least engaging (\(\mu\)=2.25).
+Breathe (\(\mu\)=7) and listen (\(\mu\)=6.75) were ranked highest in repeatability, with sequence (\(\mu\)=2.5) along with face and sport (\(\mu\)=3) ranked least repeatable.
+Finally in terms of likeliness of use for authentication, song-open (\(\mu\)=5) and sequence (\(\mu\)=4.25) performed highest though modestly, while breathe (\(\mu\)=2.75) and listen (\(\mu\)=3) were rated least likely to use.
 In addition to these rating scales we asked participants to rank the tasks from most (1) to least (9) favorite overall.
@@
 Speech \& & 0.0 & 0.0\\
-Listen - Tone & 0.0 & 0.0\\
+Listen & 0.0 & 0.0\\
 Face \& I & 0.0 & 0.0\\

### 2017-02-14 paper.tex
Fixing helix to concha in paper and figures

@@
 \includegraphics[width=.9\linewidth]{./figures/CFEEEG_piecefig_Right.jpg}
-\caption{Labeled photo of one of our manufactured right ear custom-fit earpieces with 3 embedded electrodes located at the helix, and front-facing in the ear canal, and back-facing in the ear canal.}
+\caption{Labeled photo of one of our manufactured right ear custom-fit earpieces with 3 embedded electrodes located in the concha, and front-facing in the ear canal, and back-facing in the ear canal.}
 \end{figure}
@@
 
-***Is there specifics on how the exactly positions
-of the electrodes on these pieces were chosen? If not,
-can simply mention 2 in the ear canal and 1 on the outer ear (helix)***
+The electrode positions were simplified from the positions described in \cite{mikkelsen2014eeg}.
+We reduced the canal electrodes in order to help prevent bridging and positioned them approximately 180 degrees apart in the canal (posterior/back and anterior/front locations in the canal).
+We also reduced the number of electrodes in the concha to one.
 
@@
 Notably, when examining data from the right earpiece, we re-referenced to the right mastoid channel so that our results reflect data from a single earpiece.
-Each earpiece (shown in Figure 1) contains three channels: one placed on the helix, and two inside the canal - one on the anterior canal wall (front-facing) and the other on the posterior wall (back-facing).
+Each earpiece (shown in Figure 1) contains three channels: one placed in the concha, and two inside the canal - one on the anterior canal wall (front-facing) and the other on the posterior wall (back-facing).
 The remaining two channels, AGCL ring electrodes, were placed on the right mastoid for later re-referencing, and at approximately Fp1 (left frontal lobe region, above the left eye in accordance with the ISEP) for validating the data collected in the ears against a common scalp-based placement.
@@
 & \multicolumn{3}{|c|}{Left ear} & \multicolumn{3}{c|}{Right ear} \\
-P & Helix & Front & Back & Helix & Front & Back \\
+P & Concha & Front & Back & Concha & Front & Back \\
 \hline

### 2017-02-14 paper.tex
New figures, some proofs

@@
 Breathe - Open & Relaxed breathing with eyes open & No & No & Open & None\\
-Sport & Sport-related motor imagery & No & Yes & Closed & Motor\\
-Song & Imagining hearing a song & No & Yes & Closed & Aural\\
+Sport & Imagine acting out a sport-related task & No & Yes & Closed & Motor\\
+Song & Imagine hearing a song & No & Yes & Closed & Aural\\
 Song - Open & Song task, with eyes open & No & Yes & Open & Aural\\
-Speech & Imagining a spoken phrase & No & Yes & Closed & Aural\\
-Listen & Listening to noise modulated at 40 Hz & Yes & No & Closed & None\\
+Speech & Imagine a spoken phrase & No & Yes & Closed & Aural\\
+Listen & Listen to noise modulated at 40 Hz & Yes & No & Closed & None\\
 Face & Imagine a person's face & No & Yes & Closed & Visual\\
@@
 
+All best-performing tasks in our best-case set achieved perfect FAR and FRRs, with the exception of P5, whose best-performing task (breathe) had a nonzero FRR.
 Breathe appeared as the best task across all participants.
 Given our training strategy, these results indicate that a given person's breathe task is distinguishable not only among other tasks, but among breathe tasks from other participants.
-All best-performing tasks in our set achieved perfect FAR and FRRs, with the exception of P5, whose best-performing task (breathe) had a nonzero FRR.
+This task performed about as well as its open-eyes counterpart (Figure \ref{fig:meanByTask}), as did /Song (eyes open)/ and /sport/ (though, interestingly, song with eyes closed performed less well).
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=.9\linewidth]{./figures/mean-far-by-task.png}
+\caption{FAR in the left ear by task, across all subjects.}
+\label{fig:meanByTask}
+\end{figure}
 
@@
 \hline
-FAR & 0.000074 & 0.000724 & 0.00252\\
-FRR & 0.00442 & 0.001522 & 0.0397\\
+FAR & 0.000074 & 0.000724 & 0.002523\\
+FRR & 0.004424 & 0.001522 & 0.039702\\
 \end{tabular}

### 2017-02-14 paper.tex
New figures, some proofs

@@
 
-\subsection{Multi-Factor Authentication in a Single Step}
+\subsection{One-Step, Multi-Factor Authentication}
 Behavioral authentication methods such as keystroke dynamics and speaker
@@
 Since past work has shown that classification tasks in EEG-based BCI are linear \cite{Garrett2003a}, we used XGBoost, a tool for logistic linear classification \cite{Chen2016}.
+Compared to other linear classiifers, XGBoost uses gradient boosting; in which an algorithm generates an ensemble (in this case, a decision tree) of weak linear classifiers that minimizes a given loss function.
+Gradient boosting gives better results in linear classification problems, without our needing to manually tune classifier hyperparameters.
 

### 2017-02-14 paper.tex
Added USENIX related work

@@
 
-We find that we can achieve good classification accuracy with a single earpiece containing only three electrodes.
-\underline{More result details.....}
-
 \section{Related work}
@@
 they would likely not be able to produce good electrical impedances when worn by a different individual.
+
+\subsection{Usable authentication}
+
+Authentication protocols are often susceptible to a so-called \textit{rubber-hose attack}, in which users are coerced into giving up their chosen secret (e.g.
+password), biometric, or unique token, voluntarily or not \cite{Bojinov2012, Martinovic2012}.
+This attack is particularly effective against protocols that rely only on inherence factors, as inherent traits such as fingerprints are difficult to change without costly reprocussions \cite{Spielberg2002}.
+One defense against such an attack is textit{tacit authentication}, in which the user does not know exacly how s/he performs the authenticating action.
+
+Past work has exploited tacit skills: skills we know exactly how to do, but cannot explain how we do it, e.g.
+riding a bike or walking \cite{Bojinov2012}.
+In practice, these skills require time to learn, and their visible performance could open opportunities for recording and replay attacks.
+
+In this work, we explore a different solution to rubber-hose attacks: a thought, which is secret (and thus changeable), but has a particular expression unique to an individual, the performance of which cannot be described  (and thus cannot be coerced).
+Furthermore, the performance of the thought is invisible, makng the actual authentication impervious to shoulder-surfing.
 
@@
 
-Custom ear impressions were made by cleaning and injecting silicon into the ear canal.
+To produce custom ear impressions, we cleaned subjects' ears and injected silicon into the ear canal.
 A cotton ball with a string attached is placed into the ear canal first.
@@
 All collection sites were cleaned with ethanol prior to electrode placement, and a small amount of conductive gel was used on each electrode.
-For EEG recording we used OpenBCI \cite{OpenBCI}, an open-source biosensing system to maintain an overall low cost our set up.
+For EEG recording we used OpenBCI \cite{Frey2016}, an open-source biosensing system to maintain an overall low cost our set up.
 OpenBCI has a price tag of about \$600, and thus is an affordable alternative to medical-grade EEG systems that can cost tens of thousands of dollars.
@@
 
-During the experiment, participants were seated in a comfortable position in a quiet room facing a laptop screen on which the
-instructions and stimuli were presented using PsychoPy. Each task was completed once in sets five trials each, and then
-each was completed again for another five trials. Each trial was 10 seconds in length, for a total of 10 trials and 
-100 seconds of data collected per task. The instructions were read aloud to the participant by the experimenter, and
-the experiment was advanced using a pointer held in the participant's lap to minimize motion artifacts in the data.  
-The experimenter also recorded the participant's chosen secrets for the sport, song, face, speech, and sequence
- tasks and reminded the participant of these for the second set of trials.
+During the experiment, participants were seated in a comfortable position in a quiet room facing a laptop screen on which the instructions and stimuli were presented using PsychoPy.
+Each task was completed once in sets five trials each, and then each was completed again for another five trials.
+Each trial was 10 seconds in length, for a total of 10 trials and 100 seconds of data collected per task.
+The instructions were read aloud to the participant by the experimenter, and the experiment was advanced using a pointer held in the participant's lap to minimize motion artifacts in the data.
+The experimenter also recorded the participant's chosen secrets for the sport, song, face, speech, and sequence tasks and reminded the participant of these for the second set of trials.
 
- After the completion of the experiment, a subset of participants completed a usability questionnaire asking about the ease of performing, level of engagement, perceived repeatability, and likeliness of using each task.
+ After completing the experiment, a subset of participants completed a usability questionnaire asking about the ease of performing, level of engagement, perceived repeatability, and likeliness of using each task.
 The questionnaire also asked participants to rank the tasks overall from most to least favorite, as well as several open response questions regarding potential use cases of ear EEG and this method of authentication, level of comfort wearing the earpieces, and any other comments they chose to provide.
@@
 \end{center}
-\caption{Best-case passthought FAR and FRR results by participant using data from the left ear.}
+\caption{Best-performing passthought, with FAR and FRR, for each participant, using data from the left ear.}
 \label{tab:best}
@@
 Breathe - Open & 0.0 & 0.0\\
-Sport \& & 0.0 & 0.0\\
-Song \& I & 0.0 & 0.0\\
+Sport & 0.0 & 0.0\\
+Song I & 0.0 & 0.0\\
 Song - Open & 0.0 & 0.0\\
-Speech \& & 0.0 & 0.0\\
+Speech & 0.0 & 0.0\\
 Listen & 0.0 & 0.0\\
-Face \& I & 0.0 & 0.0\\
+Face I & 0.0 & 0.0\\
 Sequence & 0.0 & 0.0\\
@@
 Again, we do not find any successful authentication attempts.
-
-% We recorded spoofed passthoughts for two ``imposter'' subjects.
-One subject appeared in our initial pool performing their own passthoughts (subject 2), while the other subject did not appear in the initial pool, and thus was not included when training subject classifiers.
-(How well the imposters were able to spoof subject 6's passthought is an open question; see Discussion).
-% For each task, we ran the spoofed version of the task through the classifier trained on subject 6's task as the passthought. None of the spoofed passthoughts were accepted, resulting in a 0\% FAR.
 

### 2017-02-14 paper.tex
typo

@@
 Informed consent was obtained prior to study procedures.
-The third study visit consisted of participants completing a short demographics questionnaire, a set up period with the openBCI system and earpieces including a second impedance check, the performance of 9 mental tasks presented on a laptop, and finally a post-experiment questionnaire.
+The third study visit consisted of participants completing a short demographics questionnaire, a set up period with the OpenBCI system and earpieces including a second impedance check, the performance of 9 mental tasks presented on a laptop, and finally a post-experiment questionnaire.
 Approximately two weeks after the third study visit, a subset of participants reported via e-mail whether or not they remembered the passthoughts they chose and performed.

### 2017-02-14 paper.tex
final conclusion graf, proofs

@@
 Facebook have strongly encouraged their users to adopt two-factor
-authentication (2FA). However, the need for users to submit two different 
-authenticators in two separate steps has frustrated wide adoption, 
-due its additional hassle cost to the users. For instance, the popular Apple
-iPhone has already implemented the necessary technologies to support device
-unlock using either a user-selected passcode or a fingerprint. The
+authentication (2FA). However, submitting two different 
+authenticators in two separate steps has frustrated wide adoption
+due to its additional hassle cost to users. The Apple iPhone, for instance,
+already supports device unlock using either a user-selected passcode or a fingerprint. The
 device could easily support a two-step two-factor authentication scheme if
@@
 new approach to authentication that can provide the security benefits of two-
-factor authentication without incurring the hassle costs of two-step verification.
-By employing consumer-grade EEG (electroencephalogram) sensing
-technologies, it was demonstrated in a 2013 passthoughts study that a user can
+factor authentication without incurring the hassle of two-step verification.
+By employing consumer-grade EEG (electroencephalogram),
+it was demonstrated in a 2013 passthoughts study that a user can
 submit both a knowledge factor (i.e., secret thought) and an inherence factor
@@
 while maintaining a low amount of effort and obtrusiveness to the user.
+
+We find that we can achieve low FARs and FRRs with a single, three-electrode earpiece.
+Interestingly, we found that we performed better in the ear than on the scalp.
+Additionally, we find that an passthoughts could not be spoofed by imposters, even when the imposters had the subject's earpiece and knew the secret passthoughts.
+We discuss the benefits of passthoughts to usable authentication, and raise questions about how and why passthoughts work as well as they do.
 
@@
 Another important question surrounds how passthoughts might be cracked.
-Generally, we do not understand how an individual's passthought is drawn from the general distribution of EEG signals that an individual produces throughout the day.
+Generally, we do not understand how an individual's passthought is drawn from the distribution of EEG signals that an individual produces throughout the day. 
 Given a large enough corpus of EEG data, are some passthoughts as easy to guess as \textit{password1234} is for passwords?

### 2017-02-14 paper.tex
conclusion, abstract updates

@@
 In a preliminary test of an "imposter'' spoofing attack, we find a 0\% false acceptance rate.
-Our results indicate that in-ear EEG could provide a discreet, convenient, multi-factor authentication.
-(TO ADD: neural source of signal confirmation, usability summary)
+Our results indicate that in-ear EEG could provide a discreet, convenient, and usable protocol for multi-factor authentication in a single step, in which a user thinks their chosen passthought.
 
@@
 
-\section{{\bfseries\sffamily TODO} Conclusion}
+\section{Conclusion}
+
+We believe custom-fit, in-ear EEG earbuds could provide three factors of authentication in a authentication single step: thinking one's password.
+In this paper, we demonstrate quite high authentication accuracy using a single sensing earbud.
+By expanding our corpus of EEG readings (in population size, time, and diversity of settings), we hope to better understand the underlying distribution of EEG signals, so that we may better understand the security properties of passthoughts.
 

### 2017-02-14 paper.tex
better abstract / first page

@@
 In a preliminary test of an "imposter'' spoofing attack, we find a 0\% false acceptance rate.
-Our results indicate that in-ear EEG could provide a discreet, convenient, and usable protocol for multi-factor authentication in a single step, in which a user thinks their chosen passthought.
+Our results indicate that in-ear EEG could provide a discreet, convenient, and useable protocol for one-step, multi-factor authentication.
 

### 2017-02-14 paper.tex
affiliations
Several proofs

@@
 \author{
-{\rm First Name}\\
-Your Institution
+{\rm First Name, Second Name, Third Name}\\
+First Institution
 \and
@@
 Second Institution
-\and
-{\rm Third Name}\\
-Third Institution
-\and
-{\rm Fourth Name}\\
-Fourth Institution
 % copy the following lines to add more authors
@@
 Across all participants, we achieve mean 0\% false acceptance and 0.12\% false rejection rates with data from only one earpiece with three electrodes.
-In a preliminary test of an "imposter'' spoofing attack, we find a 0\% false acceptance rate.
-Our results indicate that in-ear EEG could provide a discreet, convenient, and useable protocol for one-step, multi-factor authentication.
+We find a 0\% false acceptance rate in a preliminary simulation of an impersonation attack.
+Our results indicate that in-ear EEG could provide a discreet, convenient, and useable means for one-step, multi-factor authentication.
 
@@
 news reports of celebrity account hackings serve as regular reminders that
+the currently dominant method of authentication in consumer applications, 
 single-factor authentication using passwords or other user-chosen secrets, 
-the currently dominant method of authentication in consumer applications, 
-face many challenges. Major industry players such as Google and
+faces many challenges. Major industry players such as Google and
 Facebook have strongly encouraged their users to adopt two-factor
@@
 authenticators in two separate steps has frustrated wide adoption
-due to its additional hassle cost to users. The Apple iPhone, for instance,
+due to its additional hassle to users. The Apple iPhone, for instance,
 already supports device unlock using either a user-selected passcode or a fingerprint. The
@@
 new approach to authentication that can provide the security benefits of two-
-factor authentication without incurring the hassle of two-step verification.
+factor authentication without incurring the hassle cost of two-step verification.
 By employing consumer-grade EEG (electroencephalogram),
@@
 In this study we undertake, to the best of our knowledge, the first
-ever study of one-step three-factor authentication. In computer security,
+ever study of one-step, three-factor authentication. In computer security,
 authenticators are classified into three types: knowledge factors (e.g., passwords
 and PINs), possession factors (e.g., physical tokens, ATM cards), and inherence
-factors (e.g., fingerprints and other biometrics). Because three-factor
-authentication (3FA) requires the user to submit one distinct instance of each
+factors (e.g., fingerprints and other biometrics).
+
+We find that we can achieve low FARs and FRRs with a single, three-electrode earpiece.
+Interestingly, we found that performance improves in the ear compared to on the scalp.
+Additionally, we find that an passthoughts could not be spoofed by imposters, even when the imposters had the subject's earpiece and knew the secret passthoughts.
+We discuss the benefits of passthoughts to usable authentication, and raise questions about how and why passthoughts work as well as they do.
+
+\section{Related work}
+
+Because three-factor authentication (3FA) requires the user to
+submit one distinct instance of each
 type of authenticator, it represents the strongest level of authentication security
@@
 
-We find that we can achieve low FARs and FRRs with a single, three-electrode earpiece.
-Interestingly, we found that we performed better in the ear than on the scalp.
-Additionally, we find that an passthoughts could not be spoofed by imposters, even when the imposters had the subject's earpiece and knew the secret passthoughts.
-We discuss the benefits of passthoughts to usable authentication, and raise questions about how and why passthoughts work as well as they do.
-
-\section{Related work}
-
-We investigate custom-fit ear-EEG technology as the platform for
+Following this work, we investigate custom-fit ear-EEG technology as the platform for
 investigating the feasibility, performance, and usability of one-step three-factor
@@
 
-Past work has exploited tacit skills: skills we know exactly how to do, but cannot explain how we do it, e.g.
+Past work has exploited tacit skills (skills we know how to do, but cannot readily explain our method for doing, e.g.
 riding a bike or walking \cite{Bojinov2012}.
@@
 In this work, we explore a different solution to rubber-hose attacks: a thought, which is secret (and thus changeable), but has a particular expression unique to an individual, the performance of which cannot be described  (and thus cannot be coerced).
-Furthermore, the performance of the thought is invisible, makng the actual authentication impervious to shoulder-surfing.
+Furthermore, the performance of the chosen thought is invisible to outside observers, makng the actual authentication impervious to shoulder-surfing.
+
+\subsection{One-Step, Multi-Factor Authentication}
+Behavioral authentication methods such as keystroke dynamics and speaker
+authentication can be categorized as one-step two-factor authentication
+schemes. In both cases, the knowledge factor (password or passphrase) and
+inherence factor (typing rhythm or speaker's voice) are employed \cite{Monrose1997}.
+In contrast, the Nymi band supports one-step two-factor authentication via the inherence
+factor (cardiac rhythm that is supposed to be unique to each individual) and the
+possession factor (the wearing of the band on the wrist) \cite{Nymi}.
+However, as far as we know, no one has proposed or demonstrated a one-step three-factor
+authentication scheme, in which possession of a unique device also serves to authenticate the user.
+In this paper, we introduce custom-built EEG devices, incorporating an added posession factor to the already two-step authentication provided by passthoughs.
 
@@
 The use of EEG as a biometric signal for user authentication has a short history.
-In 2005, Thorpe et al. motivate and outline the design of a passthoughts system,
-where, rather than typing a password, users authenticate 
-by thinking of a passthought \cite{Thorpe2005}.
+In 2005, Thorpe et al. motivate and outline the design of a passthoughts system \cite{Thorpe2005}.
 Since 2002, a number of independent groups have achieved 99-
@@
 \subsection{In-Ear EEG}
+
+Even consumer-grade headsets can be uncomfortable to wear, and are awkwardly visible to observers.
+Earbuds present a more discreet, comfortable location for an EEG sensor, as many people already wear earbuds in day-to-day life.
+
 Research in in-ear EEG is only several years old. Nonetheless, the concept has
@@
 \cite{curranpassthoughts} was the first to merge in-ear EEG with passthought authentication,
- using a single modified consumer grade EEG device among participants and achieving approximately 80 percent authentication accuracy.
-
-\subsection{One-Step, Multi-Factor Authentication}
-Behavioral authentication methods such as keystroke dynamics and speaker
-authentication can be categorized as one-step two-factor authentication
-schemes. In both cases, the knowledge factor (password or passphrase) and
-inherence factor (typing rhythm or speaker's voice) are employed \cite{Monrose1997}.
-In contrast, the Nymi band supports one-step two-factor authentication via the inherence
-factor (cardiac rhythm that is supposed to be unique to each individual) and the
-possession factor (the wearing of the band on the wrist) \cite{Nymi}.
-However, as far as we know, no one has proposed or demonstrated a one-step three-factor
-authentication scheme, in which possession of a unique device also serves to authenticate the user.
+ using a modified consumer grade EEG device with a single electrode, achieving approximately 80 percent authentication accuracy.
 
@@
 
-The electrode positions were simplified from the positions described in \cite{mikkelsen2014eeg}.
+The electrode positions were simplified from the positions described in \cite{Mikkelsen2015}.
 We reduced the canal electrodes in order to help prevent bridging and positioned them approximately 180 degrees apart in the canal (posterior/back and anterior/front locations in the canal).
@@
 \begin{tabularx}{\textwidth}{llllll}
-Task & Description & Stimuli? & Secret? & Eyes & Imagery\\
+
+\textbf{Task} & \textbf{Description} & \textbf{Stimuli}? & \textbf{Secret} ? & \textbf{Eyes} & \textbf{Imagery}\\
 \hline
@@
 For EEG recording we used OpenBCI \cite{Frey2016}, an open-source biosensing system to maintain an overall low cost our set up.
-OpenBCI has a price tag of about \$600, and thus is an affordable alternative to medical-grade EEG systems that can cost tens of thousands of dollars.
+OpenBCI costs about \$600USD, and thus is an affordable alternative to medical-grade EEG systems that can cost tens of thousands of dollars.
 Recent work has demonstrated the robustness of OpenBCI compared to an industry standard medical-grade EEG system, particularly for non-medical use cases such as ours \cite{Frey2016}.
@@
 \begin{tabular}{lrrrrrr}
-& \multicolumn{6}{c}{Impedances [k\(\Omega\)]} \\
+& \multicolumn{6}{c}{\textbf{Impedances} [k\(\Omega\)]} \\
 \cline{2-7}
-& \multicolumn{3}{|c|}{Left ear} & \multicolumn{3}{c|}{Right ear} \\
-P & Concha & Front & Back & Concha & Front & Back \\
+& \multicolumn{3}{|c|}{\textbf{Left ear}} & \multicolumn{3}{c|}{\textbf{Right ear}} \\
+\textbf{P} & \textbf{Concha} & \textbf{Front} & \textbf{Back} & \textbf{Concha} & \textbf{Front} & \textbf{Back} \\
 \hline
@@
 From this corpus of positive and negative samples, we withheld one third of data for testing. 
-The remaining training set was fed into a XGBoost's cross-validation method, which we set to iteratively tweak parameters over a maximum of fifty rounds of cross-validation to minimize classification error.
+The remaining training set was fed into a XGBoost's cross-validation method, which we set to iteratively tweak parameters over a maximum of fifty rounds of cross-validation to minimize loss.
 After cross-validation, the updated classifier (with parameters applied) predicted labels on each sample in the test set, and we calculated FAR and FRR on its results.
@@
 Our results indicate acceptable accuracy using electrodes on the left ear alone. 
-This corresponds to our original scenario, in which the device could be worn as an earbud.
+This corresponds to our original scenario, in which the device could be worn as an earbud (ideally, only one earbud would need sensors).
 As such, we focus on results from the left ear alone in our following analysis.
@@
 \begin{tabular}{rrrl}
-FAR & FRR & P & Task\\
+\textbf{P} & \textbf{FAR} & \textbf{FRR} & \textbf{Task}\\
 \hline
-0.0 & 0.0 & 1 & Listen\\
-0.0 & 0.0 & 2 & Breathe\\
-0.0 & 0.0 & 3 & Breathe\\
-0.0 & 0.0 & 4 & Breathe\\
-0.0 & 0.012 & 5 & Breathe\\
-0.0 & 0.0 & 6 & Breathe\\
-0.0 & 0.0 & 7 & Breathe\\
+1 & 0.0 & 0.0 & Listen\\
+2 & 0.0 & 0.0 & Breathe\\
+3 & 0.0 & 0.0 & Breathe\\
+4 & 0.0 & 0.0 & Breathe\\
+& 5 0.0 & 0.012 & Breathe\\
+6 & 0.0 & 0.0 & Breathe\\
+7 & 0.0 & 0.0 & Breathe\\
 \end{tabular}
@@
 \begin{center}
-\begin{tabular}{lrrr}
- & Original & Within-tasks & Within-participants\\
+\begin{tabular}{lrr}
+ & \textbf{FAR} & \textbf{FRR}\\
 \hline
-FAR & 0.000074 & 0.000724 & 0.002523\\
-FRR & 0.004424 & 0.001522 & 0.039702\\
+Original & 0.000074 & 0.004424\\
+Within-tasks & 0.000724 & 0.001522\\
+Within-participants & 0.002523 & 0.039702\\
 \end{tabular}
@@
 This work will allow us simulate cracking attempts, and to develop empirically motivated strategies for prevention, e.g. locking users out after a certain number of attempts.
-This work could also reveal interesting tradeoffs between the usability and accuracy of certain passthoughts with their security properties.
+This work could also reveal interesting tradeoffs between the usability or accuracy of passthoughts and their security.
 
@@
 A closed-loop BCI system could help us understand how learning effects
-on the human side might impact authentication performance, as the human and machine co-adapt during multiple authentication attempts.
+on the human side might impact authentication performance, as the human and machine co-adapt through authentication attempts.
 

### 2017-02-14 paper.tex
Missed a table for bolding
Adding section in discussion about sample size

--- 2017-02-14 paper.tex
@@
 
-\section{Related work}
+\section{Related Work}
 
@@
 
-\subsection{Usable authentication}
+\subsection{Usable Authentication}
 
@@
 
-\subsection{Passthought authentication}
+\subsection{Passthoughts Authentication}
 The use of EEG as a biometric signal for user authentication has a short history.
@@
 
-\subsection{Manufacturing and materials}
+\subsection{Earpiece Design and Manufacturing}
 
@@
 
-The first quality check was examining the electrical impedances achieved for the ear pieces as a low impedance (<10 kOhm) 
+The first quality check was examining the electrical impedances achieved for the ear pieces as a low impedance (\textless10 kOhm) 
 is best for obtaining quality EEG signals.
@@
 
-\subsection{Authentication results in the left-ear}
+\subsection{Authentication Results}
 
 In the previous section, we trained and tested a passthought classifier with each task as the passthought, for all participants.
+Our analyses revealed the choice between left and right ear to have little effect on the results, this enables us to postulate around a more usable device using channels only around the left ear.
 Focusing on the left ear, we filter our results for the best-performing tasks.
@@
 Finally in terms of likeliness of use for authentication, song-open (\(\mu\)=5) and sequence (\(\mu\)=4.25) performed highest though modestly, while breathe (\(\mu\)=2.75) and listen (\(\mu\)=3) were rated least likely to use.
+
 In addition to these rating scales we asked participants to rank the tasks from most (1) to least (9) favorite overall.
@@
 
-Our findings demonstrate the apparent feasibility of single earpiece, achieving good results with only three electrodes and a reference, all on the left ear.
-FARs and FRRs are low across all participants and tasks, with FARs overall lower than FRRs.
-Participants' best-performing passthoughts typically seeing no errors in our training.
+Our findings demonstrate the apparent feasibility of single earpiece, achieving good results with only three electrodes and a reference, all on or around the left ear.
+FARs and FRRs are low across all participants and tasks, with FARs overall lower than FRRs, a desirable pattern in terms of authenticating access to potentially sensitive information.
+Participants' best-performing passthoughts typically see no errors in our training.
 Furthermore, no spoofed attacks were successful in our cursory analysis.
+
+This study was conducted with a small, relatively homogeneous sample of participants.
+We recognize this weakness and agree that more participants from diverse sample would greatly improve our understanding and interpretation of the capabilities of this technology.
+This does not lessen the importance of the work reported here however, as this sample size is comparable to that of previous scalp-based EEG passthoughts work\cite{Ashby2011, Marcel2007a, Palaniappan2008, palaniappan2006electroencephalogram, Poulos2002, Chuang2013b}, the only other in-ear EEG passthoughts study we are aware of \cite{curranpassthoughts} (note a generic fit system was used here), and other custom-fit in-ear EEG research \cite{kidmose2013study}.
+The fitting and manufacturing of custom-fit earpieces was the main limitation to increasing our sample size, and may very well pose a limitation to adoption of such a technology.
+Recently, however there have been developments in at-home kits for creating one's own custom-fitted earpieces \cite{voix2015settable} that could help overcome this barrier.
 
@@
 For the song tasks, though the song was known, the spoofers did not know what part of the song the original participant had imagined, or how it was imagined (humming, imagining a full performance, melody, vocals, etc).
-This experience sheds light on the highly individual nature of passthoughts, and provides a positive indication that there may be some intrinsic difficulty ofr spoofing passthoughts.
+This experience sheds light on the highly individual nature of passthoughts, and provides a positive indication that there may be some intrinsic difficulty of spoofing passthoughts.
 
@@
 First, \textit{breathe} tended to be the best-performing task among participants.
-Classifiers overall distinguished the breath task even compared to breath tasks from other participants, implying that the task is expressed differently for each participant, i.e.
-that this task has an inherence factor sufficient for authentication, even though the task does not have a knowledge factor.
+Classifiers overall distinguished the breathe task even compared to breathe tasks from other participants, implying that the task is expressed differently for each participant, i.e.
+that this task has an inherence factor sufficient for authentication, even though the task does not have a secondary knowledge factor beyond knowing which task to perform.
 Second, we were able to achieve good results by generating feature vectors based on only 500ms (300 voltage readings across the three electrodes).
@@
 
-Furthermore, the use of conductive gel results in low impedances on other participants' custom-fit earpieces, despite the uniquness of ear canal shapes between individuals \cite{Akkermans2005}.
+Furthermore, the use of conductive gel results in low impedances on other participants' custom-fit earpieces, despite the uniqueness of ear canal shapes between individuals \cite{Akkermans2005}.
 Nevertheless, classifiers appear to resists spoofing attacks, indicating that task-related signals are unique to individuals.
-In the future, the custom-fit earbuds could include a hardware keypair to sign authentication attempts, providing a more secure method for establishing the posession factor in our three-factor, one-step scheme.
+In the future, the custom-fit earbuds could easily include a hardware keypair to sign authentication attempts, providing a secure method for establishing the possession factor in our three-factor, one-step scheme.
 
-Finally, performance on Fp1 was not as high as performance in the ear, despite Fp1's popularity in past work on passthoughts \cite{Chuang2013b}.
+Finally, performance on Fp1 was not as high as performance in the ear, despite Fp1's popularity in past work on passthoughts \cite{Chuang2013b} and the general assumed benefits of measuring EEG from scalp-based locations.
 This could be explained by the greater number of electrodes in the ear (compared to just one on Fp1).

### 2017-02-15 paper.tex
Trying again with small fixes and sample size discussion

--- 2017-02-14 paper.tex
@@
 \cline{2-7}
-& \multicolumn{3}{|c|}{Left ear} & \multicolumn{3}{c|}{Right ear} \\
-P & Concha & Front & Back & Concha & Front & Back \\
+& \multicolumn{3}{|c|}{\textbf{Left ear}} & \multicolumn{3}{c|}{\textbf{Right ear}} \\
+\textbf{P} & \textbf{Concha} & \textbf{Front} & \textbf{Back} & \textbf{Concha} & \textbf{Front} & \textbf{Back} \\
 \hline
@@
 
-Our findings demonstrate the apparent feasibility of single earpiece, achieving good results with only three electrodes and a reference, all on the left ear.
-FARs and FRRs are low across all participants and tasks, with FARs overall lower than FRRs.
-Participants' best-performing passthoughts typically seeing no errors in our training.
+Our findings demonstrate the apparent feasibility of single earpiece, achieving good results with only three electrodes and a reference, all on or around the left ear.
+FARs and FRRs are low across all participants and tasks, with FARs overall lower than FRRs, a desirable pattern in terms of authenticating access to potentially sensitive information.
+Participants' best-performing passthoughts typically see no errors in our training.
 Furthermore, no spoofed attacks were successful in our cursory analysis.
+
+This study was conducted with a small, relatively homogeneous sample of participants.
+We recognize this weakness and agree that more participants from diverse sample would greatly improve our understanding and interpretation of the capabilities of this technology.
+This does not lessen the importance of the work reported here however, as this sample size is comparable to that of previous scalp-based EEG passthoughts work\cite{Ashby2011, Marcel2007a, Palaniappan2008, palaniappan2006electroencephalogram, Poulos2002, Chuang2013b}, the only other in-ear EEG passthoughts study we are aware of \cite{curranpassthoughts} (notably a generic fit system was used here), and other custom-fit in-ear EEG research \cite{kidmose2013study}.
+The fitting and manufacturing of custom-fit earpieces was the main limitation to increasing our sample size, and may very well pose a limitation in adoption of such a technology.
+Recently, however there have been developments in at-home kits for creating one's own custom-fitted earpieces \cite{voix2015settable} that could help overcome this barrier.
 
@@
 First, \textit{breathe} tended to be the best-performing task among participants.
-Classifiers overall distinguished the breath task even compared to breath tasks from other participants, implying that the task is expressed differently for each participant, i.e.
+Classifiers overall distinguished the breathe task even compared to breathe tasks from other participants, implying that the task is expressed differently for each participant, i.e.
 that this task has an inherence factor sufficient for authentication, even though the task does not have a knowledge factor.
@@
 
-Furthermore, the use of conductive gel results in low impedances on other participants' custom-fit earpieces, despite the uniquness of ear canal shapes between individuals \cite{Akkermans2005}.
+Furthermore, the use of conductive gel results in low impedances on other participants' custom-fit earpieces, despite the uniqueness of ear canal shapes between individuals \cite{Akkermans2005}.
 Nevertheless, classifiers appear to resists spoofing attacks, indicating that task-related signals are unique to individuals.
-In the future, the custom-fit earbuds could include a hardware keypair to sign authentication attempts, providing a more secure method for establishing the posession factor in our three-factor, one-step scheme.
+In the future, the custom-fit earbuds could easily include a hardware keypair to sign authentication attempts, providing a more secure method for establishing the possession factor in our three-factor, one-step scheme.
 

### 2017-02-15 paper.tex
Updated charts

--- 2017-02-14 paper.tex
@@
 \centering
-\includegraphics[width=.9\linewidth]{./figures/mean-far-by-electrode-config.png}
+\includegraphics[width=.9\linewidth]{./figures/mean-far-and-frr-by-electrode-config.png}
 \caption{FAR by electrode configuration. All electrodes combined achieves a perfect score. We achieve the next best scores using data from the left ear only.}
@@
 Given our training strategy, these results indicate that a given person's breathe task is distinguishable not only among other tasks, but among breathe tasks from other participants.
-This task performed about as well as its open-eyes counterpart (Figure \ref{fig:meanByTask}), as did /Song (eyes open)/ and /sport/ (though, interestingly, song with eyes closed performed less well).
+This task performed about as well as its open-eyes counterpart (Figure \ref{fig:meanByTask}), as did song (eyes open) and sport (though, interestingly, song with eyes closed performed less well).
 
@@
 \centering
-\includegraphics[width=.9\linewidth]{./figures/mean-far-by-task.png}
-\caption{FAR in the left ear by task, across all subjects.}
+\includegraphics[width=.9\linewidth]{./figures/mean-far-and-frr-by-task.png}
+\caption{FAR by task, across all subjects, using data from the left ear only.}
 \label{fig:meanByTask}

### 2017-02-15 paper.tex
Fixed table 3 error

@@
 4 & 0.0 & 0.0 & Breathe\\
-& 5 0.0 & 0.012 & Breathe\\
+5 & 0.0 & 0.012 & Breathe\\
 6 & 0.0 & 0.0 & Breathe\\

### 2017-02-15 paper.tex
Minor notes

@@
 Breathe appeared as the best task across all participants.
-Given our training strategy, these results indicate that a given person's breathe task is distinguishable not only among other tasks, but among breathe tasks from other participants.
+Given our training strategy, these results indicate that a given person's breathe task is distinguishable not only among other tasks, but among breathe tasks from other participants (that is, we are not simply picking a unique passthought task for each subject).
 This task performed about as well as its open-eyes counterpart (Figure \ref{fig:meanByTask}), as did song (eyes open) and sport (though, interestingly, song with eyes closed performed less well).
@@
 Finally, our work leaves room for some clear UX improvements.
-Future work should try using dry electrodes, commonly found in consumer EEG devices, for comfort and usability.
+Future work should try using dry electrodes, commonly found in consumer EEG devices, for comfort and usability. The electrodes could be grounded to the ear, instead of the forehead.
+Additionally, future work could easily place a speaker inside our current custom-fit earbuds to produce working ``hearables'' that can be used as ordinary headphones.
+
 Future work should also attempt a closed-loop (or online) passthought system, in which users receive immediate feedback on the result of their authentication attempt.

### 2017-02-15 paper.tex
Fixed impedence table overflow

@@
 & \multicolumn{3}{|c|}{\textbf{Left ear}} & \multicolumn{3}{c|}{\textbf{Right ear}} \\
-\textbf{P} & \textbf{Concha} & \textbf{Front} & \textbf{Back} & \textbf{Concha} & \textbf{Front} & \textbf{Back} \\
+\textbf{P} & \textbf{C} & \textbf{F} & \textbf{B} & \textbf{C} & \textbf{F} & \textbf{B} \\
 \hline
@@
 \end{center}
-\caption{Electrical impedances measured for earpiece electrodes.}
+\caption{Electrical impedances measured for earpiece electrodes, for concha (C), front (F) and back (B).}
 \label{tab:impedances}
@@
 \end{center}
-\caption{Electrical impedances measured while P1 wore each other participant's custom-fitted earpieces.}
+\caption{Electrical impedances measured while P1 wore each other participant's custom-fitted earpieces, for concha (C), front (F) and back (B).}
 \label{tab:imposter_impedances}

### 2017-02-15 paper.tex
Table 3 all same sigdigs

@@
 \hline
-1 & 0.0 & 0.0 & Listen\\
-2 & 0.0 & 0.0 & Breathe\\
-3 & 0.0 & 0.0 & Breathe\\
-4 & 0.0 & 0.0 & Breathe\\
-5 & 0.0 & 0.012 & Breathe\\
-6 & 0.0 & 0.0 & Breathe\\
-7 & 0.0 & 0.0 & Breathe\\
+1 & 0.000 & 0.000 & Listen\\
+2 & 0.000 & 0.000 & Breathe\\
+3 & 0.000 & 0.000 & Breathe\\
+4 & 0.000 & 0.000 & Breathe\\
+5 & 0.000 & 0.012 & Breathe\\
+6 & 0.000 & 0.000 & Breathe\\
+7 & 0.000 & 0.000 & Breathe\\
 \end{tabular}

### 2017-02-15 paper.tex
Minor fixes

--- 2017-02-15 paper.tex
@@
 \subsection*{Abstract}
-In this paper, we present a system that provides all three factors of authentication (knowledge, possession, and inherence) in a single step, using brain-based authentication via a custom-fit, in-ear EEG.
+In this paper, we present a system that provides all three factors of authentication (knowledge, possession, and inherence) in a single step, using brain-based authentication via a custom-fit, in-ear electroencephalography (EEG).
+We demonstrate collecting EEG data from seven participants using manufactured custom-fit earpieces with embedded electrodes.
 Across all participants, we achieve mean 0\% false acceptance and 0.12\% false rejection rates with data from only one earpiece with three electrodes.
 We find a 0\% false acceptance rate in a preliminary simulation of an impersonation attack.
-Our results indicate that in-ear EEG could provide a discreet, convenient, and useable means for one-step, multi-factor authentication.
+Our results indicate that in-ear EEG could provide a discreet, convenient, and useable means for one-step, three-factor authentication.
 
@@
 and PINs), possession factors (e.g., physical tokens, ATM cards), and inherence
-factors (e.g., fingerprints and other biometrics).
+factors (e.g., fingerprints and other biometrics). By taking advantage of a physical token 
+in the form of personalized earpieces, the uniqueness of an individual's brainwaves, and
+a choice of mental task to use as one's passthoughts, we seek to achieve all three factors 
+of authentication in a single step by the user.
 
-We find that we can achieve low FARs and FRRs with a single, three-electrode earpiece.
-Interestingly, we found that performance improves in the ear compared to on the scalp.
-Additionally, we find that an passthoughts could not be spoofed by imposters, even when the imposters had the subject's earpiece and knew the secret passthoughts.
-We discuss the benefits of passthoughts to usable authentication, and raise questions about how and why passthoughts work as well as they do.
+We find that we can achieve low false acceptance rates (FAR) and false rejection rates (FRR) with a single, 
+three-electrode earpiece. Interestingly, we found that performance improves in the ear compared to a single electrode on the scalp.
+Additionally, we find that a passthoughts could not be spoofed by imposters, even when the imposters had the user's earpiece and knew their chosen passthoughts.
+We discuss the benefits of passthoughts for usable authentication, and raise questions about how and why passthoughts work as well as they do.
 
@@
 Because three-factor authentication (3FA) requires the user to
-submit one distinct instance of each
-type of authenticator, it represents the strongest level of authentication security
+submit one distinct instance of each type of authenticator, it represents the strongest level of authentication security
 possible. The system we propose and test here uses the choice of a mental task
@@
 activity as measured by EEG as inherence, and the physical token of custom-fit 
-earpieces which could easily contain a hardware key-pair as a possession factor.
+earpieces, which could easily contain a hardware key-pair, as a possession factor.
 The ability to utilize all three of these security factors in a single step by performing 
@@
 
-Following this work, we investigate custom-fit ear-EEG technology as the platform for
+Following this, we investigate custom-fit in-ear EEG technology as the platform for
 investigating the feasibility, performance, and usability of one-step three-factor
@@
 password), biometric, or unique token, voluntarily or not \cite{Bojinov2012, Martinovic2012}.
-This attack is particularly effective against protocols that rely only on inherence factors, as inherent traits such as fingerprints are difficult to change without costly reprocussions \cite{Spielberg2002}.
-One defense against such an attack is textit{tacit authentication}, in which the user does not know exacly how s/he performs the authenticating action.
+This attack is particularly effective against protocols that rely only on inherence factors, as inherent traits such as fingerprints are difficult to change without costly repercussions \cite{Spielberg2002}.
+One defense against such an attack is textit{tacit authentication}, in which the user does not know exactly how s/he performs the authenticating action.
 
@@
 In this work, we explore a different solution to rubber-hose attacks: a thought, which is secret (and thus changeable), but has a particular expression unique to an individual, the performance of which cannot be described  (and thus cannot be coerced).
-Furthermore, the performance of the chosen thought is invisible to outside observers, makng the actual authentication impervious to shoulder-surfing.
+Furthermore, the performance of the chosen thought is invisible to outside observers, making the actual authentication impervious to shoulder-surfing.
 
@@
 authentication scheme, in which possession of a unique device also serves to authenticate the user.
-In this paper, we introduce custom-built EEG devices, incorporating an added posession factor to the already two-step authentication provided by passthoughs.
+In this paper, we introduce custom-built EEG devices, incorporating an added possession factor to the already two-step authentication provided by passthoughts.
 
@@
 The use of EEG as a biometric signal for user authentication has a short history.
-In 2005, Thorpe et al. motivate and outline the design of a passthoughts system \cite{Thorpe2005}.
+In 2005, Thorpe et al. motivated and outlined the design of a passthoughts system \cite{Thorpe2005}.
 Since 2002, a number of independent groups have achieved 99-
@@
 knowledge factor (the secret mental task) \cite{Chuang2014}.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=.9\linewidth]{./figures/CFEEEG_piecefig_Right.jpg}
-\caption{Labeled photo of one of our manufactured right ear custom-fit earpieces with 3 embedded electrodes located in the concha, and front-facing in the ear canal, and back-facing in the ear canal.}
-\end{figure}
 
@@
 
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=.9\linewidth]{./figures/CFEEEG_piecefig_Right.jpg}
+\caption{Labeled photo of one of our manufactured right ear custom-fit earpieces with 3 embedded electrodes located in the concha, and front-facing in the ear canal, and back-facing in the ear canal.}
+\end{figure}
+
 To produce custom ear impressions, we cleaned subjects' ears and injected silicon into the ear canal.
@@
 We also reduced the number of electrodes in the concha to one.
+An example of one of the manufactured earpieces is shown in Figure 1.
 
@@
 
-\textbf{Task} & \textbf{Description} & \textbf{Stimuli}? & \textbf{Secret} ? & \textbf{Eyes} & \textbf{Imagery}\\
+\textbf{Task} & \textbf{Description} & \textbf{Stimuli}? & \textbf{Secret}? & \textbf{Eyes} & \textbf{Imagery}\\
 \hline
@@
 For EEG recording we used OpenBCI \cite{Frey2016}, an open-source biosensing system to maintain an overall low cost our set up.
-OpenBCI costs about \$600USD, and thus is an affordable alternative to medical-grade EEG systems that can cost tens of thousands of dollars.
+OpenBCI costs about 600 USD, and thus is an affordable alternative to medical-grade EEG systems that can cost tens of thousands of dollars.
 Recent work has demonstrated the robustness of OpenBCI compared to an industry standard medical-grade EEG system, particularly for non-medical use cases such as ours \cite{Frey2016}.
@@
 
-During the experiment, participants were seated in a comfortable position in a quiet room facing a laptop screen on which the instructions and stimuli were presented using PsychoPy.
+During the experiment, participants were seated in a comfortable position in a quiet room facing a laptop screen on which the instructions and stimuli were presented using PsychoPy \cite{peirce2007psychopy}.
 Each task was completed once in sets five trials each, and then each was completed again for another five trials.
@@
 
-For the alpha-attenuation test, data from the "Breathe" task was compared with that of the "Breathe - Open" task. It is a well-
+For the alpha-attenuation test, data from the \textit{breathe} task was compared with that of the \textit{breathe - open} task. It is a well-
 known feature of EEG data that activity in the alpha-band (approximately 8-12 Hz range) increases when the eyes are closed
@@
 Since past work has shown that classification tasks in EEG-based BCI are linear \cite{Garrett2003a}, we used XGBoost, a tool for logistic linear classification \cite{Chen2016}.
-Compared to other linear classiifers, XGBoost uses gradient boosting; in which an algorithm generates an ensemble (in this case, a decision tree) of weak linear classifiers that minimizes a given loss function.
+Compared to other linear classifiers, XGBoost uses gradient boosting; in which an algorithm generates an ensemble (in this case, a decision tree) of weak linear classifiers that minimizes a given loss function.
 Gradient boosting gives better results in linear classification problems, without our needing to manually tune classifier hyperparameters.
@@
 Interestingly, no single electrode from the left or right ear performs as well as the aggregate left and right ear conditions. 
-Counter to our expectations, Fp1 does not perform as well as most ear electrodes.
+Counter to our expectations, Fp1 does not perform as well as most ear electrodes, though overall these reported rates are far less 
+than 1\%.
 
@@
 \centering
-\includegraphics[width=.9\linewidth]{./figures/mean-far-and-frr-by-electrode-config.png}
+\includegraphics[width=.9\linewidth]{./figures/mean-far-by-electrode-config.png}
 \caption{FAR by electrode configuration. All electrodes combined achieves a perfect score. We achieve the next best scores using data from the left ear only.}
@@
 
-All best-performing tasks in our best-case set achieved perfect FAR and FRRs, with the exception of P5, whose best-performing task (breathe) had a nonzero FRR.
-Breathe appeared as the best task across all participants.
-Given our training strategy, these results indicate that a given person's breathe task is distinguishable not only among other tasks, but among breathe tasks from other participants (that is, we are not simply picking a unique passthought task for each subject).
-This task performed about as well as its open-eyes counterpart (Figure \ref{fig:meanByTask}), as did song (eyes open) and sport (though, interestingly, song with eyes closed performed less well).
+All best-performing tasks in our best-case set achieved perfect FAR and FRRs, with the exception of P5, whose best-performing task (\textit{breathe}) had a nonzero FRR.
+\textit{Breathe} appeared as the best task across all participants.
+Given our training strategy, these results indicate that a given person's \textit{breathe} task is distinguishable not only among other tasks, but among \textit{breathe} tasks from other participants.
+This task performed about as well as its open-eyes counterpart (Figure \ref{fig:meanByTask}), as did \textit{song - open} and \textit{sport} (though, interestingly, \textit{song} with eyes closed performed less well).
 
@@
 \centering
-\includegraphics[width=.9\linewidth]{./figures/mean-far-and-frr-by-task.png}
-\caption{FAR by task, across all subjects, using data from the left ear only.}
+\includegraphics[width=.9\linewidth]{./figures/mean-far-by-task.png}
+\caption{FAR in the left ear by task, across all subjects.}
 \label{fig:meanByTask}
@@
 This questionnaire asked them to rank each of the mental tasks on 7-point likert-type scales on ease of use, level of engagement, perceived repeatability, and likeliness to use in a real-world authentication setting.
-The breathe and listen (\(\mu\)=6.75) tasks were ranked easiest to use, while the sequence (\(\mu\)=2.25) and face (\(\mu\)=2.75) tasks were ranked the most difficult.
-Sequence was rated highly in engagement however (\(\mu\)=5), as was the song task (\(\mu\)=5), while breathe-open and listen were ranked least engaging (\(\mu\)=2.25).
-Breathe (\(\mu\)=7) and listen (\(\mu\)=6.75) were ranked highest in repeatability, with sequence (\(\mu\)=2.5) along with face and sport (\(\mu\)=3) ranked least repeatable.
-Finally in terms of likeliness of use for authentication, song-open (\(\mu\)=5) and sequence (\(\mu\)=4.25) performed highest though modestly, while breathe (\(\mu\)=2.75) and listen (\(\mu\)=3) were rated least likely to use.
+The \textit{breathe} and \textit{listen} (\(\mu\)=6.75) tasks were ranked easiest to use, while the \textit{sequence} (\(\mu\)=2.25) and \textit{face} (\(\mu\)=2.75) tasks were ranked the most difficult.
+\textit{Sequence} was rated highly in engagement however (\(\mu\)=5), as was \textit{song}  (\(\mu\)=5), while \textit{breathe-open} and \textit{listen} were ranked least engaging (\(\mu\)=2.25).
+\textit{Breathe} (\(\mu\)=7) and \textit{listen} (\(\mu\)=6.75) were ranked highest in repeatability, with \textit{sequence} (\(\mu\)=2.5) along with \textit{face} and \textit{sport} (\(\mu\)=3) ranked least repeatable.
+Finally in terms of likeliness of use for authentication, \textit{song-open} (\(\mu\)=5) and \textit{sequence} (\(\mu\)=4.25) were rated highest, though modestly, while \textit{breathe} (\(\mu\)=2.75) and \textit{listen} (\(\mu\)=3) were rated least likely to use.
 
 In addition to these rating scales we asked participants to rank the tasks from most (1) to least (9) favorite overall.
-The song-open task ranked highest among favorites (\(\mu\)=4.25) followed by a tie between breathe-open, song, and speech (\(\mu\)=4.75).
-In line with some of the results above, sequence (\(\mu\)=7.75) and face (\(\mu\)=6.75) were rated as least favorites.
+The \textit{song - open} task ranked highest among favorites (\(\mu\)=4.25) followed by a tie between \textit{breathe - open}, \textit{song}, and \textit{speech} (\(\mu\)=4.75).
+In line with some of the results above, \textit{sequence} (\(\mu\)=7.75) and \textit{face} (\(\mu\)=6.75) were rated as least favorites.
 
@@
 
-A final component of usability we measured was the ability of the participants to recall their specific chosen passthoughts for the song, sport, speech, face, and sequence tasks.
+A final component of usability we measured was the ability of the participants to recall their specific chosen passthoughts for the \textit{song}, \textit{sport}, \textit{speech}, \textit{face}, and \textit{sequence} tasks.
 Participants were contacted approximately two weeks after their data collection study visit and were prompted with these categories and asked to respond with what they remembered their choices being.
-As evidenced by their responses, all participants were able to recall all of their chosen secrets, with the exception of one participant who incorrectly remembered their chosen word for the sequence task.
+As evidenced by their responses, all participants were able to recall all of their chosen secrets, with the exception of one participant who incorrectly remembered their chosen word for the \textit{sequence} task.
 
-\section{Imposter attack}
+\section{Imposter Attack}
 
@@
 
-To explore the scenario of an imposter attempting to gain access, we chose the worst case participant, P6, whose earpieces P1 had the lowest impedances wearing.
+To explore the scenario of an imposter attempting to gain access, we chose the worst case participant, P6, whose earpieces P1 had the lowest impedances while wearing.
 We collected data using the same data collection protocol, but had P1 refer to P6's report of chosen passsthoughts.
-P1 performed each of P6's passthoughts (simulating an ``inside imposter'').
+P1 performed each of P6's passthoughts (simulating an "inside imposter'').
 Following the same classification and preprocessing steps, we generated 200 samples per task for our imposters, using data from all left ear electrodes.
@@
 Sport & 0.0 & 0.0\\
-Song I & 0.0 & 0.0\\
+Song & 0.0 & 0.0\\
 Song - Open & 0.0 & 0.0\\
@@
 Listen & 0.0 & 0.0\\
-Face I & 0.0 & 0.0\\
+Face & 0.0 & 0.0\\
 Sequence & 0.0 & 0.0\\
@@
 This study was conducted with a small, relatively homogeneous sample of participants.
-We recognize this weakness and agree that more participants from diverse sample would greatly improve our understanding and interpretation of the capabilities of this technology.
-This does not lessen the importance of the work reported here however, as this sample size is comparable to that of previous scalp-based EEG passthoughts work\cite{Ashby2011, Marcel2007a, Palaniappan2008, palaniappan2006electroencephalogram, Poulos2002, Chuang2013b}, the only other in-ear EEG passthoughts study we are aware of \cite{curranpassthoughts} (notably a generic fit system was used here), and other custom-fit in-ear EEG research \cite{kidmose2013study}.
+We feel that more participants from a more diverse pool would greatly improve our understanding and interpretation of the capabilities of this technology.
+This does not lessen the importance of this work however, as this sample size is comparable to that of previous scalp-based EEG passthoughts work\cite{Ashby2011, Marcel2007a, Palaniappan2008, palaniappan2006electroencephalogram, Poulos2002, Chuang2013b}, the only other in-ear EEG passthoughts study we are aware of \cite{curranpassthoughts} (notably a generic fit system was used here), and other custom-fit in-ear EEG research \cite{kidmose2013study}.
 The fitting and manufacturing of custom-fit earpieces was the main limitation to increasing our sample size, and may very well pose a limitation in adoption of such a technology.
-Recently, however there have been developments in at-home kits for creating one's own custom-fitted earpieces \cite{voix2015settable} that could help overcome this barrier.
+Recently, however there have been developments in at-home kits for creating one's own custom-fitted earpieces \cite{voix2015settable} that could help overcome this barrier in the future.
 
@@
 Although our target participant documented their chosen passthought, the spoofers found ambiguity in how these passthoughts could be expressed.
-For the face task, the spoofers did not know the friend the original participant had chosen.
-For the song tasks, though the song was known, the spoofers did not know what part of the song the original participant had imagined, or how it was imagined (humming, imagining a full performance, melody, vocals, etc).
-This experience sheds light on the highly individual nature of passthoughts, and provides a positive indication that there may be some intrinsic difficulty ofr spoofing passthoughts.
+For the \textit{face} task, the spoofers did not know the precise friend the original participant had chosen.
+For the \textit{song} and \textit{song - open} tasks, though the song was known, the spoofers did not know what part of the song the original participant had imagined, or how it was imagined (humming, imagining a full performance, melody, vocals, etc).
+This experience sheds light on the highly individual nature of passthoughts, and provides a positive indication that there may be some intrinsic difficulty in spoofing attempts of passthoughts.
 
@@
 First, \textit{breathe} tended to be the best-performing task among participants.
-Classifiers overall distinguished the breathe task even compared to breathe tasks from other participants, implying that the task is expressed differently for each participant, i.e.
-that this task has an inherence factor sufficient for authentication, even though the task does not have a knowledge factor.
+Classifiers overall distinguished the \textit{breathe} task even compared to \textit{breathe} tasks from other participants, implying that the task is expressed differently for each participant, i.e.
+that this task has an inherence factor sufficient for authentication, even though the task does not have an explicit secondary knowledge factor as in \textit{song}, for example.
 Second, we were able to achieve good results by generating feature vectors based on only 500ms (300 voltage readings across the three electrodes).
@@
 Finally, our work leaves room for some clear UX improvements.
-Future work should try using dry electrodes, commonly found in consumer EEG devices, for comfort and usability. The electrodes could be grounded to the ear, instead of the forehead.
-Additionally, future work could easily place a speaker inside our current custom-fit earbuds to produce working ``hearables'' that can be used as ordinary headphones.
-
+Future work should try using dry electrodes, commonly found in consumer EEG devices, for comfort and usability.
 Future work should also attempt a closed-loop (or online) passthought system, in which users receive immediate feedback on the result of their authentication attempt.
@@
 
-We believe custom-fit, in-ear EEG earbuds could provide three factors of authentication in a authentication single step: thinking one's password.
-In this paper, we demonstrate quite high authentication accuracy using a single sensing earbud.
+As demonstrated by these preliminary results, custom-fit, in-ear EEG earpieces provide three factors of authentication in a authentication single step: thinking one's password, using the discreet form factor of an earpiece.
+In this paper, we demonstrate quite high authentication accuracy using a single sensing earpiece.
 By expanding our corpus of EEG readings (in population size, time, and diversity of settings), we hope to better understand the underlying distribution of EEG signals, so that we may better understand the security properties of passthoughts.

### 2017-02-15 paper.tex
NEw graphs

@@
 \subsection*{Abstract}
-In this paper, we present a system that provides all three factors of authentication (knowledge, possession, and inherence) in a single step, using brain-based authentication via a custom-fit, in-ear electroencephalography (EEG).
+In this paper, we present a system that provides all three factors of authentication (knowledge, possession, and inherence) in a single step, using brain-based authentication via custom-fit, in-ear electroencephalography (EEG).
 We demonstrate collecting EEG data from seven participants using manufactured custom-fit earpieces with embedded electrodes.
-Across all participants, we achieve mean 0\% false acceptance and 0.12\% false rejection rates with data from only one earpiece with three electrodes.
+Across all participants, we achieve mean 0\% false acceptance and 0.017\% false rejection rates with data from only one earpiece with three electrodes.
 We find a 0\% false acceptance rate in a preliminary simulation of an impersonation attack.
-Our results indicate that in-ear EEG could provide a discreet, convenient, and useable means for one-step, three-factor authentication.
+Our results indicate that in-ear EEG could provide a discreet, convenient, and useable method for one-step, three-factor authentication.
 
@@
 This attack is particularly effective against protocols that rely only on inherence factors, as inherent traits such as fingerprints are difficult to change without costly repercussions \cite{Spielberg2002}.
-One defense against such an attack is textit{tacit authentication}, in which the user does not know exactly how s/he performs the authenticating action.
+One defense against such an attack is \textit{tacit authentication}, in which the user does not know exactly how s/he performs the authenticating action.
 
@@
 
-\begin{figure}[htbp]
+\begin{figure*}[t]
 \centering
@@
 \label{fig:meanByElectrode}
-\end{figure}
+\end{figure*}
 
@@
 All best-performing tasks in our best-case set achieved perfect FAR and FRRs, with the exception of P5, whose best-performing task (\textit{breathe}) had a nonzero FRR.
-\textit{Breathe} appeared as the best task across all participants.
+\textit{Breathe} appeared as the best task across all participants, except P1.
 Given our training strategy, these results indicate that a given person's \textit{breathe} task is distinguishable not only among other tasks, but among \textit{breathe} tasks from other participants.
@@
 \label{fig:meanByTask}
-\end{figure}
+\end{figure*}
 

### 2017-02-15 paper.tex
Proofs to intro

@@
 
-In previous work, "one-step two-factor authentication" has been proposed as a
-new approach to authentication that can provide the security benefits of two-
-factor authentication without incurring the hassle cost of two-step verification.
-By employing consumer-grade EEG (electroencephalogram),
-it was demonstrated in a 2013 passthoughts study that a user can
-submit both a knowledge factor (i.e., secret thought) and an inherence factor
-(i.e., brainwave signal unique to the individual) in a single step by performing a
-single mental task \cite{Chuang2014}. Additionally, the robustness of this method against
-impersonation attacks was demonstrated, including conditions where the attacker
-may have learned the target'۪s secret thought and/or secret task \cite{Johnson2014}.
-
+In previous work, "one-step two-factor authentication" has been proposed as a new approach to authentication that can provide the security benefits of two- factor authentication without incurring the hassle cost of two-step verification.
 In this study we undertake, to the best of our knowledge, the first
@@
 
-Because three-factor authentication (3FA) requires the user to
-submit one distinct instance of each type of authenticator, it represents the strongest level of authentication security
-possible. The system we propose and test here uses the choice of a mental task
-or "passthought" to perform as knowledge, the uniqueness of an individual's brain
-activity as measured by EEG as inherence, and the physical token of custom-fit 
-earpieces, which could easily contain a hardware key-pair, as a possession factor.
-The ability to utilize all three of these security factors in a single step by performing 
-a mental task of a few seconds is a promising in pursuit of extremely strong security 
-while maintaining a low amount of effort and obtrusiveness to the user.
+By employing consumer-grade EEG (electroencephalogram), it was demonstrated in a 2013 passthoughts study that a user can submit both a knowledge factor (i.e., secret thought) and an inherence factor (i.e., brainwave signal unique to the individual) in a single step by performing a single mental task \cite{Chuang2014}.
+Additionally, the robustness of this method against impersonation attacks was demonstrated, including conditions where the attacker may have learned the target'۪s secret thought and/or secret task \cite{Johnson2014}.
 
-Following this, we investigate custom-fit in-ear EEG technology as the platform for
-investigating the feasibility, performance, and usability of one-step three-factor
-authentication. In addition to the dual knowledge and inherence factors in
-in previous work, this work includes a possession factor
-in the form of the EEG-sensing ear-piece(s) that are custom-fitted to and worn in
-their ear. These earpieces can serve as physical tokens in the same way as bank
-ATM cards and wearable hardware tokens by implementing a hardware key-pair.
-Furthermore, because the earpieces are custom-fitted to each individual, we predicted 
-they would likely not be able to produce good electrical impedances when worn by a different individual.
+Following this, we investigate custom-fit in-ear EEG technology as the platform for investigating the feasibility, performance, and usability of one-step three-factor authentication.
+ The system we propose and test here uses the choice of a mental task or "passthought" to perform as knowledge (factor one), the uniqueness of an individual's brain activity as measured by EEG as inherence (factor two), and the physical token of custom-fit earpieces, which could easily contain a hardware key-pair, as a possession factor (factor 3).
+ %% In addition to the dual knowledge and inherence factors established in previous work, this study incorporates a possession factor in the form of the EEG-sensing ear-piece(s) that are custom-fitted to and worn in their ear.
+These earpieces can serve as physical tokens in the same way as bank ATM cards and wearable hardware tokens by implementing a hardware key-pair.
+ %% Furthermore, because the earpieces are custom-fitted to each individual, we predicted they would likely not be able to produce good electrical impedances when worn by a different individual.
+%% Because three-factor authentication (3FA) requires the user to submit one distinct instance of each type of authenticator, it represents the strongest level of authentication security possible.
+The ability to utilize all three of these security factors in a single step by performing a mental task of a few seconds is a promising in pursuit of extremely strong security while maintaining a low amount of effort and obtrusiveness to the user.
 
@@
 
-Authentication protocols are often susceptible to a so-called \textit{rubber-hose attack}, in which users are coerced into giving up their chosen secret (e.g.
+In addition, authentication protocols are often susceptible to a so-called \textit{rubber-hose attack}, in which users are coerced into giving up their chosen secret (e.g.
 password), biometric, or unique token, voluntarily or not \cite{Bojinov2012, Martinovic2012}.
@@
 
-For each configuration of electrodes, we calculated the mean FAR and FRR across all participants using each task as the passthought (Figure \ref{fig:meanByElectrode}).
-Incorporating all electrodes data results in a perfect score for all tasks.
-Using data from all left-ear electrodes achieves the next lowest FAR, followed by all right ear electrodes.
-Interestingly, no single electrode from the left or right ear performs as well as the aggregate left and right ear conditions. 
-Counter to our expectations, Fp1 does not perform as well as most ear electrodes, though overall these reported rates are far less 
-than 1\%.
-
-Our results indicate acceptable accuracy using electrodes on the left ear alone. 
-This corresponds to our original scenario, in which the device could be worn as an earbud (ideally, only one earbud would need sensors).
-As such, we focus on results from the left ear alone in our following analysis.
-
 \begin{figure*}[t]
@@
 \end{figure*}
+
+For each configuration of electrodes, we calculated the mean FAR and FRR across all participants using each task as the passthought (Figure \ref{fig:meanByElectrode}).
+Incorporating all electrodes data results in a perfect score for all tasks.
+Using data from all left-ear electrodes achieves the next lowest FAR, followed by all right ear electrodes.
+Interestingly, no single electrode from the left or right ear performs as well as the aggregate left and right ear conditions.
+
+Counter to our expectations, Fp1 does not perform as well as most ear electrodes, though overall these reported rates are far less 
+than 1\%. 
+Further, while FRR seemed to correlate roughly with FAR for most electrodes, the right concha and right canal front electrodes achieved extremeley high FRRs, while their FARs were among the lowest.
+
+Our results indicate acceptable accuracy using electrodes on the left ear alone. 
+This corresponds to our original scenario, in which the device could be worn as an earbud (ideally, only one earbud would need sensors).
+As such, we focus on results from the left ear alone in our following analysis.
 

### 2017-02-15 paper.tex
proofs

@@
 riding a bike or walking \cite{Bojinov2012}.
-In practice, these skills require time to learn, and their visible performance could open opportunities for recording and replay attacks.
+In practice, these skills require time to learn, and the fact that they are performed visibly could open up opportunities for recording and replay attacks.
 
@@
 
-Even consumer-grade headsets can be uncomfortable to wear, and are awkwardly visible to observers.
+Even consumer-grade headsets can be uncomfortable to wear, and are awkwardly visible to outside observers.
 Earbuds present a more discreet, comfortable location for an EEG sensor, as many people already wear earbuds in day-to-day life.

### 2017-02-16 paper.tex
fixed fig3, addded note

@@
 \includegraphics[width=.9\linewidth]{./figures/CFEEEG_piecefig_Right.jpg}
-\caption{Labeled photo of one of our manufactured right ear custom-fit earpieces with 3 embedded electrodes located in the concha, and front-facing in the ear canal, and back-facing in the ear canal.}
+\caption{Labeled photo of one of our manufactured custom-fit earpieces with 3 embedded electrodes located in the concha, and front-facing in the ear canal, and back-facing in the ear canal.}
 \end{figure}
@@
 This 3D model is then sent to a 3D printer.
-Following this wires leads and associated AGCL electrodes are installed.
+Following this wires leads and associated AgCl electrodes are installed.
 
@@
 \subsection{Data Collection Protocol}
-\label{sec:org2041857}
+
 The data collection visit took approximately 90 minutes for set up and experiment execution.
@@
 Each earpiece (shown in Figure 1) contains three channels: one placed in the concha, and two inside the canal - one on the anterior canal wall (front-facing) and the other on the posterior wall (back-facing).
-The remaining two channels, AGCL ring electrodes, were placed on the right mastoid for later re-referencing, and at approximately Fp1 (left frontal lobe region, above the left eye in accordance with the ISEP) for validating the data collected in the ears against a common scalp-based placement.
+The remaining two channels, AgCl ring electrodes, were placed on the right mastoid for later re-referencing, and at approximately Fp1 (left frontal lobe region, above the left eye in accordance with the ISEP) for validating the data collected in the ears against a common scalp-based placement.
 Before beginning the experiment, the data from each channel was visually inspected using the OpenBCI GUI and participants were asked to blink and clench their jaws to confirm that all channels were active and properly connected.
@@
 
-The first quality check was examining the electrical impedances achieved for the ear pieces as a low impedance (<10 kOhm) 
+The first quality check was examining the electrical impedances achieved for the ear pieces as a low impedance ($<$10 kOhm) 
 is best for obtaining quality EEG signals.
@@
 a single trial's data. To further validate, we also performed this calculation on the data collected from the Fp1 electrode and see
-the effect clearly here as well.
-The figure below shows the alpha attenuation in the left ear channels, as well as Fp1 of one participant as an example.
+the effect clearly here as well. The figure below shows the alpha attenuation in the left ear channels, as well as Fp1 of one participant as an example.
 We see the same effect in the right ear channels referenced to the right mastoid.
@@
 Incorporating all electrodes data results in a perfect score for all tasks.
-Using data from all left-ear electrodes achieves the next lowest FAR, followed by all right ear electrodes.
-Interestingly, no single electrode from the left or right ear performs as well as the aggregate left and right ear conditions.
+Using data from all left-ear electrodes achieves the next lowest FAR.
+Interestingly, no single electrode performs as well as the aggregate left or both-ear plus Fp1 (all) conditions.
 
@@
 than 1\%. 
-Further, while FRR seemed to correlate roughly with FAR for most electrodes, the right concha and right canal front electrodes achieved extremeley high FRRs, while their FARs were among the lowest.
+For each position, FAR was about ten times lower than FRR, which is preferable for authentication, as false authentications are potentially more costly than false rejections.
+% Further, while FRR seemed to correlate roughly with FAR for most electrodes, the right concha and right canal front electrodes achieved extremeley high FRRs, while their FARs were among the lowest. 
+% Since our results were similar in the right and left ear aggregate conditions, we proceed with only one ear (the left) in the following analyses.
 
@@
 In the previous section, we trained and tested a passthought classifier with each task as the passthought, for all participants.
-Our analyses revealed the choice between left and right ear to have little effect on the results, this enables us to postulate around a more usable device using channels only around the left ear.
+Our analyses revealed the left produced decent results.
 Focusing on the left ear, we filter our results for the best-performing tasks.
 We rank tasks by lowest FAR and, given a tie, the lowest FRR (Table \ref{tab:best}).
+Overall, we find  a mean FAR of zero and mean FRR of 0.017\%.
 

### 2017-02-16 paper.tex
missed a space

@@
 We feel that more participants from a more diverse pool would greatly improve our understanding and interpretation of the capabilities of this technology.
-This does not lessen the importance of this work however, as this sample size is comparable to that of previous scalp-based EEG passthoughts work\cite{Ashby2011, Marcel2007a, Palaniappan2008, palaniappan2006electroencephalogram, Poulos2002, Chuang2013b}, the only other in-ear EEG passthoughts study we are aware of \cite{curranpassthoughts} (notably a generic fit system was used here), and other custom-fit in-ear EEG research \cite{kidmose2013study}.
+This does not lessen the importance of this work however, as this sample size is comparable to that of previous scalp-based EEG passthoughts work \cite{Ashby2011, Marcel2007a, Palaniappan2008, palaniappan2006electroencephalogram, Poulos2002, Chuang2013b}, the only other in-ear EEG passthoughts study we are aware of \cite{curranpassthoughts} (notably a generic fit system was used here), and other custom-fit in-ear EEG research \cite{kidmose2013study}.
 The fitting and manufacturing of custom-fit earpieces was the main limitation to increasing our sample size, and may very well pose a limitation in adoption of such a technology.

### 2017-02-16 paper.tex
tightened first page

@@
 \subsection*{Abstract}
-In this paper, we present a system that provides all three factors of authentication (knowledge, possession, and inherence) in a single step, using brain-based authentication via custom-fit, in-ear electroencephalography (EEG).
+We present a system that provides all three factors of authentication (knowledge, possession, and inherence) in a single step, using brain-based authentication via custom-fit, in-ear electroencephalography (EEG).
 We demonstrate collecting EEG data from seven participants using manufactured custom-fit earpieces with embedded electrodes.
@@
 Additionally, we find that a passthoughts could not be spoofed by imposters, even when the imposters had the user's earpiece and knew their chosen passthoughts.
-We discuss the benefits of passthoughts for usable authentication, and raise questions about how and why passthoughts work as well as they do.
+We discuss future work to investigate the robustness of passthoughts in day-to-day life, and raise questions about how and why passthoughts work as well as they do.
 
@@
 By employing consumer-grade EEG (electroencephalogram), it was demonstrated in a 2013 passthoughts study that a user can submit both a knowledge factor (i.e., secret thought) and an inherence factor (i.e., brainwave signal unique to the individual) in a single step by performing a single mental task \cite{Chuang2014}.
-Additionally, the robustness of this method against impersonation attacks was demonstrated, including conditions where the attacker may have learned the target'۪s secret thought and/or secret task \cite{Johnson2014}.
+Additionally, the robustness of this method against impersonation attacks was demonstrated, including conditions where the attacker may have learned the target'۪s secret thought \cite{Johnson2014}.
 
-Following this, we investigate custom-fit in-ear EEG technology as the platform for investigating the feasibility, performance, and usability of one-step three-factor authentication.
- The system we propose and test here uses the choice of a mental task or "passthought" to perform as knowledge (factor one), the uniqueness of an individual's brain activity as measured by EEG as inherence (factor two), and the physical token of custom-fit earpieces, which could easily contain a hardware key-pair, as a possession factor (factor 3).
+Following this work, we investigate custom-fit, in-ear EEG earpieces as a platform for one-step, three-factor authentication.
+We use the choice of a mental task or "passthought" to perform as knowledge (factor one), the uniqueness of an individual's brain activity as measured by EEG as inherence (factor two), and the physical token of custom-fit earpieces, which could easily contain a hardware key-pair, as a possession factor (factor 3).
  %% In addition to the dual knowledge and inherence factors established in previous work, this study incorporates a possession factor in the form of the EEG-sensing ear-piece(s) that are custom-fitted to and worn in their ear.

### 2017-02-16 paper.tex
typo

@@
 Following this work, we investigate custom-fit, in-ear EEG earpieces as a platform for one-step, three-factor authentication.
-We use the choice of a mental task or "passthought" to perform as knowledge (factor one), the uniqueness of an individual's brain activity as measured by EEG as inherence (factor two), and the physical token of custom-fit earpieces, which could easily contain a hardware key-pair, as a possession factor (factor 3).
+We use the choice of a mental task or "passthought" to perform as knowledge (factor one), the uniqueness of an individual's brain activity as measured by EEG as inherence (factor two), and the physical token of custom-fit earpieces, which could easily contain a hardware key-pair, as a possession factor (factor three).
  %% In addition to the dual knowledge and inherence factors established in previous work, this study incorporates a possession factor in the form of the EEG-sensing ear-piece(s) that are custom-fitted to and worn in their ear.

### 2017-02-16 paper.tex
Another once-over, some reordering of related work and discussion

--- 2017-02-16 paper.tex
@@
 \subsection*{Abstract}
-In this paper, we present a system that provides all three factors of authentication (knowledge, possession, and inherence) in a single step, using brain-based authentication via custom-fit, in-ear electroencephalography (EEG).
-We demonstrate collecting EEG data from seven participants using manufactured custom-fit earpieces with embedded electrodes.
+In this paper, we present a system that provides all three factors of authentication (knowledge, possession, and inherence) in a single step by using brain-based authentication via custom-fit, in-ear electroencephalography (EEG).
+We demonstrate its potential by collecting electroencephalography (EEG) data from seven participants using manufactured custom-fit earpieces with embedded electrodes.
 Across all participants, we achieve mean 0\% false acceptance and 0.017\% false rejection rates with data from only one earpiece with three electrodes.
-We find a 0\% false acceptance rate in a preliminary simulation of an impersonation attack.
-Our results indicate that in-ear EEG could provide a discreet, convenient, and useable method for one-step, three-factor authentication.
+Furthermore, we find a 0\% false acceptance rate in a preliminary simulation of an impersonation attack.
+We also report some positive usability perspectives from our participants and discuss constructive directions for future work.
+Our results indicate that in-ear EEG could provide a discreet, convenient, and usable method for secure one-step, three-factor authentication.
 
@@
 already supports device unlock using either a user-selected passcode or a fingerprint. The
-device could easily support a two-step two-factor authentication scheme if
+device could very well support a two-step two-factor authentication scheme if
 desired. However, it is easy to understand why users would balk at having to
@@
 
-In previous work, "one-step two-factor authentication" has been proposed as a new approach to authentication that can provide the security benefits of two- factor authentication without incurring the hassle cost of two-step verification.
+In previous work, "one-step two-factor authentication" has been proposed as a new approach to authentication that can provide the security benefits of two-factor authentication without incurring the hassle cost of two-step verification.
 In this study we undertake, to the best of our knowledge, the first
@@
 We find that we can achieve low false acceptance rates (FAR) and false rejection rates (FRR) with a single, 
-three-electrode earpiece. Interestingly, we found that performance improves in the ear compared to a single electrode on the scalp.
-Additionally, we find that a passthoughts could not be spoofed by imposters, even when the imposters had the user's earpiece and knew their chosen passthoughts.
-We discuss the benefits of passthoughts for usable authentication, and raise questions about how and why passthoughts work as well as they do.
+three-electrode earpiece.
+Interestingly, we found that performance in our protocol improves in the ear compared to a single electrode placed more traditionally on the scalp.
+Additionally, we find that passthoughts are not able to be spoofed by imposters, either from within the data set or outside of it, even when the imposters had a user's earpiece that fit their ear and knew their chosen passthoughts.
+We discuss the benefits of passthoughts for usable authentication, and raise questions for future pursuit about how and why passthoughts work as well as they do.
 
 \section{Related Work}
-
-By employing consumer-grade EEG (electroencephalogram), it was demonstrated in a 2013 passthoughts study that a user can submit both a knowledge factor (i.e., secret thought) and an inherence factor (i.e., brainwave signal unique to the individual) in a single step by performing a single mental task \cite{Chuang2014}.
-Additionally, the robustness of this method against impersonation attacks was demonstrated, including conditions where the attacker may have learned the target'۪s secret thought and/or secret task \cite{Johnson2014}.
-
-Following this, we investigate custom-fit in-ear EEG technology as the platform for investigating the feasibility, performance, and usability of one-step three-factor authentication.
- The system we propose and test here uses the choice of a mental task or "passthought" to perform as knowledge (factor one), the uniqueness of an individual's brain activity as measured by EEG as inherence (factor two), and the physical token of custom-fit earpieces, which could easily contain a hardware key-pair, as a possession factor (factor 3).
- %% In addition to the dual knowledge and inherence factors established in previous work, this study incorporates a possession factor in the form of the EEG-sensing ear-piece(s) that are custom-fitted to and worn in their ear.
-These earpieces can serve as physical tokens in the same way as bank ATM cards and wearable hardware tokens by implementing a hardware key-pair.
- %% Furthermore, because the earpieces are custom-fitted to each individual, we predicted they would likely not be able to produce good electrical impedances when worn by a different individual.
-%% Because three-factor authentication (3FA) requires the user to submit one distinct instance of each type of authenticator, it represents the strongest level of authentication security possible.
-The ability to utilize all three of these security factors in a single step by performing a mental task of a few seconds is a promising in pursuit of extremely strong security while maintaining a low amount of effort and obtrusiveness to the user.
-
-\subsection{Usable Authentication}
-
-In addition, authentication protocols are often susceptible to a so-called \textit{rubber-hose attack}, in which users are coerced into giving up their chosen secret (e.g.
-password), biometric, or unique token, voluntarily or not \cite{Bojinov2012, Martinovic2012}.
-This attack is particularly effective against protocols that rely only on inherence factors, as inherent traits such as fingerprints are difficult to change without costly repercussions \cite{Spielberg2002}.
-One defense against such an attack is \textit{tacit authentication}, in which the user does not know exactly how s/he performs the authenticating action.
-
-Past work has exploited tacit skills (skills we know how to do, but cannot readily explain our method for doing, e.g.
-riding a bike or walking \cite{Bojinov2012}.
-In practice, these skills require time to learn, and the fact that they are performed visibly could open up opportunities for recording and replay attacks.
-
-In this work, we explore a different solution to rubber-hose attacks: a thought, which is secret (and thus changeable), but has a particular expression unique to an individual, the performance of which cannot be described  (and thus cannot be coerced).
-Furthermore, the performance of the chosen thought is invisible to outside observers, making the actual authentication impervious to shoulder-surfing.
-
-\subsection{One-Step, Multi-Factor Authentication}
-Behavioral authentication methods such as keystroke dynamics and speaker
-authentication can be categorized as one-step two-factor authentication
-schemes. In both cases, the knowledge factor (password or passphrase) and
-inherence factor (typing rhythm or speaker's voice) are employed \cite{Monrose1997}.
-In contrast, the Nymi band supports one-step two-factor authentication via the inherence
-factor (cardiac rhythm that is supposed to be unique to each individual) and the
-possession factor (the wearing of the band on the wrist) \cite{Nymi}.
-However, as far as we know, no one has proposed or demonstrated a one-step three-factor
-authentication scheme, in which possession of a unique device also serves to authenticate the user.
-In this paper, we introduce custom-built EEG devices, incorporating an added possession factor to the already two-step authentication provided by passthoughts.
 
@@
 the passthoughts approach is no longer constrained by the high cost (\textgreater \$10,000 USD)
-and low usability (gel-based electrodes; aesthetic challenges of an EEG cap) of
+and low usability (gel-based electrodes; aesthetic challenges of a full EEG cap) of
 medical-grade multi-channel devices. Second, because users can choose and
@@
 
+By employing scalp-based consumer-grade electroencephalography (EEG), it was demonstrated in a 2014 passthoughts study that a user can submit both a knowledge factor (i.e., secret thought) and an inherence factor (i.e., brainwave signal unique to the individual) in a single step by performing a single mental task \cite{Chuang2014}.
+Additionally, the robustness of this method against impersonation attacks was demonstrated, including conditions where the attacker may have learned the target'۪s secret thought and/or secret task \cite{Johnson2014}.
+
+Following this, we investigate custom-fit in-ear EEG technology as the platform for investigating the feasibility, performance, and usability of one-step three-factor authentication worn unobtrusively.
+The system we propose and test here uses the choice of a mental task or "passthought" to perform as knowledge (factor one), the uniqueness of an individual's brain activity as measured by EEG as inherence (factor two), and the physical token of custom-fit earpieces, which could easily contain a hardware key-pair, as a possession factor (factor 3).
+Because three-factor authentication (3FA) requires the user to submit one distinct instance of each type of authenticator, it represents the strongest level of authentication security possible.
+The ability to utilize all three of these security factors in a single step by performing a mental task of a few seconds is a promising in pursuit of extremely strong security while maintaining a low amount of effort and obtrusiveness to the user.
+ %% In addition to the dual knowledge and inherence factors established in previous work, this study incorporates a possession factor in the form of the EEG-sensing ear-piece(s) that are custom-fitted to and worn in their ear.
+These earpieces can serve as physical tokens in the same way as bank ATM cards and wearable hardware tokens by implementing a hardware key-pair.
+ %% Furthermore, because the earpieces are custom-fitted to each individual, we predicted they would likely not be able to produce good electrical impedances when worn by a different individual.
+
 \subsection{In-Ear EEG}
-
 Even consumer-grade headsets can be uncomfortable to wear, and are awkwardly visible to outside observers.
-Earbuds present a more discreet, comfortable location for an EEG sensor, as many people already wear earbuds in day-to-day life.
+Sensors placed around the ear however, present a more discreet, comfortable location for an EEG sensor, as many people already wear technology like earbuds in day-to-day life.
 
@@
 concept of in-ear EEG, demonstrating for the first time the feasibility of recording
-brainwave signals from within the ear canal
-\cite{Looney2011}.
-Follow-up work from the same
-group demonstrated its ability to produce signal-to-noise ratios comparable to
+brainwave signals from within the ear canal \cite{Looney2011}.
+Follow-up work from the same group demonstrated its ability to produce signal-to-noise ratios comparable to
 those from conventional EEG electrode placements, robustness to common
@@
 
-\cite{curranpassthoughts} was the first to merge in-ear EEG with passthought authentication,
- using a modified consumer grade EEG device with a single electrode, achieving approximately 80 percent authentication accuracy.
+\cite{curran2016passthoughts} was the first to merge in-ear EEG with passthought authentication,
+ using a modified consumer grade EEG device with a single electrode, achieving approximately 80\% authentication accuracy.
+
+\subsection{One-Step, Multi-Factor Authentication}
+Behavioral authentication methods such as keystroke dynamics and speaker
+authentication can be categorized as one-step two-factor authentication
+schemes. In both cases, the knowledge factor (password or passphrase) and
+inherence factor (typing rhythm or speaker's voice) are employed \cite{Monrose1997}.
+In contrast, the Nymi band supports one-step two-factor authentication via the inherence
+factor (cardiac rhythm that is supposed to be unique to each individual) and the
+possession factor (the wearing of the band on the wrist) \cite{Nymi}.
+However, as far as we know, no one has proposed or demonstrated a one-step three-factor
+authentication scheme, in which possession of a unique device also serves to authenticate the user.
+In this paper, we introduce custom-built EEG devices, incorporating an added possession factor to the already one-step two-factor authentication provided by passthoughts.
+
+\subsection{Usable Authentication}
+
+Typical authentication protocols are often susceptible to a so-called \textit{rubber-hose attack}, in which users are coerced into giving up their chosen secret (e.g.
+alphanumeric password), biometric, or unique token, voluntarily or otherwise \cite{Bojinov2012, Martinovic2012}.
+This attack is particularly effective against protocols that rely only on inherence factors, as inherent traits such as fingerprints are difficult to change without costly repercussions \cite{Spielberg2002}.
+One defense against such an attack is \textit{tacit authentication}, in which the user does not know exactly how s/he performs the authenticating action and thus cannot fully give it away even under duress.
+
+Past work has exploited tacit skills (skills we know how to do, but cannot readily explain our method for doing, e.g.
+riding a bike or walking \cite{Bojinov2012}.
+In practice, these skills require time to learn, and the fact that they are performed visibly could open up opportunities for recording and replay attacks.
+
+Our work explores a different solution to rubber-hose attacks: a thought, which is secret (and thus changeable), but has a particular expression unique to an individual, the performance of which cannot be described (and thus cannot be coerced).
+Furthermore, the performance of the chosen thought is largely invisible to outside observers, ensuring the actual authentication is impervious to shoulder-surfing.
 
 \section{Methods}
+
+\subsection{Study Overview}
+
+7 male participants (P1-P7), 5 students and 2 non-students, completed our study protocol that was approved by our local Institutional Review Board.
+Three study visits took place per participant, in the first the 3D molds of participants' ears to use in creating the earpieces were obtained, the second was a fit and electrical impedance check once earpieces were manufactured, and the third to collect data using the earpieces while participants performed a set mental tasks to be used in authentication analysis.
+Informed consent was obtained prior to study procedures.
+The third study visit consisted of participants completing a short demographics questionnaire, a set up period with the OpenBCI system and earpieces including a second impedance check, the performance of 9 mental tasks presented on a laptop, and finally a post-experiment questionnaire.
+Approximately two weeks after the third study visit, a subset of participants reported via e-mail whether or not they remembered the passthoughts they chose and performed during the third visit.
 
@@
 \includegraphics[width=.9\linewidth]{./figures/CFEEEG_piecefig_Right.jpg}
-\caption{Labeled photo of one of our manufactured custom-fit earpieces with 3 embedded electrodes located in the concha, and front-facing in the ear canal, and back-facing in the ear canal.}
+\caption{Labeled photo of one of our manufactured custom-fit earpieces with 3 embedded electrodes located in the concha, front-facing (anterior) in the ear canal, and back-facing (posterior) in the ear canal.}
+\label{fig:earpiece_diagram}
 \end{figure}
 
-To produce custom ear impressions, we cleaned subjects' ears and injected silicon into the ear canal.
+To produce custom ear impressions during the first study visit, we cleaned subjects' ears and injected silicon into the ear canals.
 A cotton ball with a string attached is placed into the ear canal first.
@@
 This 3D model is then sent to a 3D printer.
-Following this wires leads and associated AgCl electrodes are installed.
+Following this wires, leads, and associated AgCl electrodes are installed.
 
-The electrode positions were simplified from the positions described in \cite{Mikkelsen2015}.
-We reduced the canal electrodes in order to help prevent bridging and positioned them approximately 180 degrees apart in the canal (posterior/back and anterior/front locations in the canal).
+The positions of the earpiece electrodes were simplified from those described in \cite{Mikkelsen2015}.
+We reduced the number of canal electrodes in order to prevent electrical bridging and positioned them approximately 180 degrees apart in the canal (posterior/back and anterior/front locations in the canal).
 We also reduced the number of electrodes in the concha to one.
-An example of one of the manufactured earpieces is shown in Figure 1.
-
-\subsection{Study Overview}
-
-7 male participants (P1-P7), 5 students and 2 non-students, completed our study protocol that was approved by our local Institutional Review Board.
-Three study visits took place per participant, in the first the 3D molds of participants' ears to use in creating the earpieces were obtained, the second to do a fit and electrical impedance check once earpieces were manufactured, and a third to collect data using the earpieces while participants performed a set of mental tasks to be used in authentication analysis.
-Informed consent was obtained prior to study procedures.
-The third study visit consisted of participants completing a short demographics questionnaire, a set up period with the OpenBCI system and earpieces including a second impedance check, the performance of 9 mental tasks presented on a laptop, and finally a post-experiment questionnaire.
-Approximately two weeks after the third study visit, a subset of participants reported via e-mail whether or not they remembered the passthoughts they chose and performed.
+An example of one of the manufactured earpieces is shown in Figure \ref{fig:earpiece_diagram}.
 
 \label{sec:orgaf30da9}
-\subsection{Tasks}
+\subsection{Mental Tasks}
 
-We used a set of mental tasks based on findings in related work regarding the relative strengths of different mental tasks in authentication accuracy and usability as reported by participants.
-Furthermore, given the in-ear placement of the electrodes and therefore the proximity to the temporal lobes containing the auditory cortex, we tested several novel authentication tasks based specifically on auditory imagery or stimuli.
+We used a set of mental tasks based on findings in related work regarding the relative strengths of different tasks in authentication accuracy and usability as reported by participants.
+Furthermore, given the in-ear placement of the electrodes and therefore the proximity to the temporal lobes containing the auditory cortex, we tested several novel authentication tasks based specifically on aural imagery or stimuli.
 The 9 authentication tasks and their attributes are listed in Table \ref{tab:tasks}.
@@
 Breathe - Open & Relaxed breathing with eyes open & No & No & Open & None\\
-Sport & Imagine acting out a sport-related task & No & Yes & Closed & Motor\\
+Sport & Imagine attempting a chosen physical activity & No & Yes & Closed & Motor\\
 Song & Imagine hearing a song & No & Yes & Closed & Aural\\
 Song - Open & Song task, with eyes open & No & Yes & Open & Aural\\
-Speech & Imagine a spoken phrase & No & Yes & Closed & Aural\\
+Speech & Imagine a chosen spoken phrase & No & Yes & Closed & Aural\\
 Listen & Listen to noise modulated at 40 Hz & Yes & No & Closed & None\\
-Face & Imagine a person's face & No & Yes & Closed & Visual\\
-Sequence & Imagine face, a number, and word on timed cues & Yes & Yes & Open & Visual\\
+Face & Imagine a chosen person's face & No & Yes & Closed & Visual\\
+Sequence & Imagine a chosen face, number, and word on timed cues & Yes & Yes & Open & Visual\\
 \hline
@@
 \subsection{Data Collection Protocol}
-
+\label{sec:org2041857}
 The data collection visit took approximately 90 minutes for set up and experiment execution.
 All collection sites were cleaned with ethanol prior to electrode placement, and a small amount of conductive gel was used on each electrode.
-For EEG recording we used OpenBCI \cite{Frey2016}, an open-source biosensing system to maintain an overall low cost our set up.
+For EEG recording we used OpenBCI \cite{michalska2009openbci}, an open-source biosensing system to maintain an overall low cost for our setup.
 OpenBCI costs about 600 USD, and thus is an affordable alternative to medical-grade EEG systems that can cost tens of thousands of dollars.
@@
 Data was collected with the ground placed at the center of the forehead, approximately AFz according to the 10-20 International Standard for Electrode Placement (ISEP), and using the left mastoid as reference.
-Notably, when examining data from the right earpiece, we re-referenced to the right mastoid channel so that our results reflect data from a single earpiece.
-Each earpiece (shown in Figure 1) contains three channels: one placed in the concha, and two inside the canal - one on the anterior canal wall (front-facing) and the other on the posterior wall (back-facing).
-The remaining two channels, AgCl ring electrodes, were placed on the right mastoid for later re-referencing, and at approximately Fp1 (left frontal lobe region, above the left eye in accordance with the ISEP) for validating the data collected in the ears against a common scalp-based placement.
-Before beginning the experiment, the data from each channel was visually inspected using the OpenBCI GUI and participants were asked to blink and clench their jaws to confirm that all channels were active and properly connected.
+Notably, when examining data from the right earpiece, we re-referenced to the right mastoid channel so that our results reflect data from a single ear.
+Each earpiece (shown in Figure \ref{fig:earpiece_diagram}) contains three channels, for the remaining two channels AgCl ring electrodes were placed on the right mastoid for later re-referencing, and at approximately Fp1 (left frontal lobe region, above the left eye in accordance with the ISEP) for validating the data collected in the ears against a common scalp-based placement.
+Before beginning the experiment, the data from each channel was visually inspected using the OpenBCI interface and participants were asked to blink and clench their jaws to confirm that all channels were active and properly connected.
 Audio stimuli were delivered through small tubes in the earpieces opening into the ear canal.
@@
 The instructions were read aloud to the participant by the experimenter, and the experiment was advanced using a pointer held in the participant's lap to minimize motion artifacts in the data.
-The experimenter also recorded the participant's chosen secrets for the sport, song, face, speech, and sequence tasks and reminded the participant of these for the second set of trials.
+The experimenter also recorded the participant's chosen secrets for the \textit{sport}, \textit{song}, \textit{face}, \textit{speech}, and \textit{sequence} tasks and reminded the participant of these for the second set of trials.
 
- After completing the experiment, a subset of participants completed a usability questionnaire asking about the ease of performing, level of engagement, perceived repeatability, and likeliness of using each task.
-The questionnaire also asked participants to rank the tasks overall from most to least favorite, as well as several open response questions regarding potential use cases of ear EEG and this method of authentication, level of comfort wearing the earpieces, and any other comments they chose to provide.
+ After completing the experiment, a subset of participants completed a usability questionnaire in which they were asked to rate their ease of performing, level of engagement, perceived repeatability, and likeliness of using each task.
+The questionnaire also asked participants to rank the tasks overall from most to least favorite, as well as several open response questions regarding potential use cases of in-ear EEG and this method of authentication, level of comfort wearing the earpieces, and any other comments they chose to provide.
 
@@
 In this section, we establish that the data we collected were of a neural origin, and had relatively little noise.
-We were able to confirm the custom-fit earpieces are able to collect EEG data using two tests: good impedances measured for the ear electrodes, and alpha-band activity attenuation when a participant's eyes were open versus closed.
+We were able to confirm the custom-fit earpieces are able to collect EEG data via two metrics: good impedances measured for the ear electrodes, and alpha-band EEG activity attenuation when a participant's eyes were open versus closed.
 
-The first quality check was examining the electrical impedances achieved for the ear pieces as a low impedance ($<$10 kOhm) 
+The first quality check was examining the electrical impedances achieved for the ear pieces as a low impedance (<10 kOhm) 
 is best for obtaining quality EEG signals.
@@
 With the exception of a few channels in select participants, impedances achieved were overall good.
+Most of the recorded impedances of the earpiece electrodes were less than 5 k\(\Omega\), a benchmark used widely in previous ear EEG work, and all except two were less than 10 k\(\Omega\).
+Nonetheless, the data from all electrodes were tested in the remaining two data quality tests.
 
@@
 
-Most of the recorded impedances of the earpiece electrodes were less than 5 k\(\Omega\), a benchmark used widely in previous
-ear EEG work, and all except two were less than 10 k\(\Omega\). Nonetheless, the data from all electrodes were tested in the remaining two data quality tests.
-
 For the alpha-attenuation test, data from the \textit{breathe} task was compared with that of the \textit{breathe - open} task. It is a well-
@@
 a single trial's data. To further validate, we also performed this calculation on the data collected from the Fp1 electrode and see
-the effect clearly here as well. The figure below shows the alpha attenuation in the left ear channels, as well as Fp1 of one participant as an example.
-We see the same effect in the right ear channels referenced to the right mastoid.
+the effect clearly here as well to compare.
+Figure \ref{fig:alpha_atten} shows the alpha attenuation in the left ear channels, as well as Fp1 of one participant as an example.
+We see the same effect in the right ear channels.
 
@@
 Red indicates breathing data with eyes open, blue indicates the same task with eyes closed.}
+\label{fig:alpha_atten}
 \end{figure}
@@
 
-To produce feature vectors, we took slices of 100 raw values from each electrode (about 500ms of data), and performed an FFT to produce power spectra for each electrode during that slice.
-We concatenated all electrode power spectra together, and performed PCA on all concatenated vectors such that the resulting vectors described 95\% of the variance in the full power spectrum data.
-For each task, for each participant, 100 seconds of data were collected in total across 10 trials of 10 seconds each, resulting in 200 samples per participant, per task, following preprocessing.
+To produce feature vectors, we took slices of 100 raw values from each electrode (about 500ms of data), and performed a fourier transform to produce power spectra for each electrode during that slice.
+We concatenated all electrode power spectra together, and performed principal component analysis on all concatenated vectors such that the resulting vectors described 95\% of the variance in the full power spectrum data.
+For each task, for each participant, 100 seconds of data were collected in total across 10 trials of 10 seconds each, resulting in 200 samples per participant, per task, following this preprocessing.
 
@@
 For each configuration of electrodes, we calculated the mean FAR and FRR across all participants using each task as the passthought (Figure \ref{fig:meanByElectrode}).
-Incorporating all electrodes data results in a perfect score for all tasks.
-Using data from all left-ear electrodes achieves the next lowest FAR.
-Interestingly, no single electrode performs as well as the aggregate left or both-ear plus Fp1 (all) conditions.
+Incorporating all electrodes' data results in a perfect score for all tasks.
+Using data from all left-ear electrodes achieves the next lowest FAR, followed by all right ear electrodes.
+Notably, no single electrode from the left or right ear performs as well as the aggregate left and right ear conditions.
 
@@
 than 1\%. 
-For each position, FAR was about ten times lower than FRR, which is preferable for authentication, as false authentications are potentially more costly than false rejections.
-% Further, while FRR seemed to correlate roughly with FAR for most electrodes, the right concha and right canal front electrodes achieved extremeley high FRRs, while their FARs were among the lowest. 
-% Since our results were similar in the right and left ear aggregate conditions, we proceed with only one ear (the left) in the following analyses.
+Further, while FRR seemed to correlate roughly with FAR for most electrodes, the right concha and right canal front electrodes achieved extremely high FRRs, while their FARs were among the lowest.
 
 Our results indicate acceptable accuracy using electrodes on the left ear alone. 
-This corresponds to our original scenario, in which the device could be worn as an earbud (ideally, only one earbud would need sensors).
-As such, we focus on results from the left ear alone in our following analysis.
+This corresponds to our original scenario, in which the device could be worn like an earbud (ideally, only one earbud would need sensors).
+As such, we focus on results from the left ear alone in our following analyses.
 
@@
 In the previous section, we trained and tested a passthought classifier with each task as the passthought, for all participants.
-Our analyses revealed the left produced decent results.
+Our analyses revealed the choice between left and right ear to have little effect on the results and this enables us to postulate around a more usable device using sensors only around the left ear.
 Focusing on the left ear, we filter our results for the best-performing tasks.
 We rank tasks by lowest FAR and, given a tie, the lowest FRR (Table \ref{tab:best}).
-Overall, we find  a mean FAR of zero and mean FRR of 0.017\%.
 
@@
 \end{center}
-\caption{Best-performing passthought, with FAR and FRR, for each participant, using data from the left ear.}
+\caption{Best-performing passthought, with FAR and FRR, for each participant (P), using data from the left ear.}
 \label{tab:best}
@@
 
-Overall, our original training strategy achieves the lowest FAR (Table \ref{tab:compare}). Within-tasks FAR ten times higher, and within-participants FAR is one hundred times higher.
+Overall, our original training strategy achieves the lowest FAR (Table \ref{tab:compare}).
+Within-tasks FAR ten times higher, and within-participants FAR is one hundred times higher, though all scenarios still less than 1\%.
 However, FRR is \textit{lower} in the within-tasks training strategy than in our original strategy's FRR. Within-participants again results in the highest FRR.
@@
 
-While our left-ear results establish that passthoughts achieve low FAR and FRR when tested against other participants' passthoughts, we do not know how robust passthoughts are against a spoofing attack, in which both a participant's custom-fit electrode, and details of that participant's chosen passthought, are leaked.
+While our left ear results establish that passthoughts achieve low FAR and FRR when tested against other participants' passthoughts, we do not know how robust passthoughts are against a spoofing attack, in which both a participant's custom-fit electrode, and details of that participant's chosen passthought, are leaked and used by an imposter.
 
-The first aspect of this scenario we tested was the ability of an imposter to wear an earpiece acquired from someone else and achieve viable impedance values for EEG collection.
-P1 tried on each of the other participants' earpieces, which firstly were able to fit at least somewhat in P1's ears.
+The first aspect of this scenario we tested was the ability of an imposter to wear an earpiece acquired from someone else and achieve viable impedance values for EEG collection based on the fit of the pieces in their ears.
+P1 tried on each of the other participants' earpieces, which were able to at least somewhat fit in P1's ears.
 The impedances of P1 wearing other participants' earpieces were then recorded and are listed in Table \ref{tab:imposter_impedances} below.
+While some are a better fit than others, overall they are higher than those achieved by the pieces' intended owners themselves.
 
@@
 \end{center}
-\caption{Electrical impedances measured while P1 wore each other participant's custom-fitted earpieces, for concha (C), front (F) and back (B).}
+\caption{Electrical impedances achieved with P1 wearing each other participant's (P) custom-fitted earpieces, for concha (C), front (F) and back (B).}
 \label{tab:imposter_impedances}
@@
 Since every participant has one classifier per task (for which that task is the passthought), we are able to make 200 spoofed attempts with the correct passthought on each of P6's classifiers (Table \ref{tab:imposter}).
-We find no successful spoof attempts for tasks with a chosen secret (e.g., song, face).
-However, we also do not find any successful spoof attacks for tasks with no chosen secret (e.g., breathe).
-In all 1,800 spoof attempts (200 attempts for each of the 9 classifiers), we do not find a single successful attack on any of P6's classifiers.
+We find no successful spoof attempts for tasks with a chosen secret (e.g., \textit{song} or \textit{face}).
+However, we also do not find any successful spoof attacks for tasks with no chosen secret (e.g., \textit{breathe}).
+In fact, in all 1,800 spoof attempts (200 attempts for each of the 9 classifiers), we do not find a single successful attack on any of P6's classifiers.
 
 However, since this participant's data appeared in the initial pool, the classifier may have been trained on his or her recordings as negative examples.
-To explore the efficacy of an outsider spoofing recordings, we repeated the same protocol with an individual who did not appear in our initial set of participants (an ``outside imposter,'' Table \ref{tab:imposter}).
-Again, we do not find any successful authentication attempts.
+To explore the efficacy of an outsider spoofing recordings, we repeated the same protocol with an individual who did not appear in our initial set of participants (an "outside imposter,'' Table \ref{tab:imposter}).
+Again, find zero successful authentication attempts.
 
@@
 
-Our findings demonstrate the apparent feasibility of single earpiece, achieving good results with only three electrodes and a reference, all on or around the left ear.
-FARs and FRRs are low across all participants and tasks, with FARs overall lower than FRRs, a desirable pattern in terms of authenticating access to potentially sensitive information.
+Our findings demonstrate the apparent feasibility of a single earpiece, achieving good results with only three electrodes and a reference, all on or around the left ear.
+FARs and FRRs are very low across all participants and tasks, with FARs overall lower than FRRs, a desirable pattern in terms of authenticating access to potentially sensitive information.
 Participants' best-performing passthoughts typically see no errors in our training.
@@
 We feel that more participants from a more diverse pool would greatly improve our understanding and interpretation of the capabilities of this technology.
-This does not lessen the importance of this work however, as this sample size is comparable to that of previous scalp-based EEG passthoughts work \cite{Ashby2011, Marcel2007a, Palaniappan2008, palaniappan2006electroencephalogram, Poulos2002, Chuang2013b}, the only other in-ear EEG passthoughts study we are aware of \cite{curranpassthoughts} (notably a generic fit system was used here), and other custom-fit in-ear EEG research \cite{kidmose2013study}.
-The fitting and manufacturing of custom-fit earpieces was the main limitation to increasing our sample size, and may very well pose a limitation in adoption of such a technology.
-Recently, however there have been developments in at-home kits for creating one's own custom-fitted earpieces \cite{voix2015settable} that could help overcome this barrier in the future.
-
-The powerful interactions between inherence and knowledge emerged in our spoofing attack.
-Although our target participant documented their chosen passthought, the spoofers found ambiguity in how these passthoughts could be expressed.
-For the \textit{face} task, the spoofers did not know the precise friend the original participant had chosen.
-For the \textit{song} and \textit{song - open} tasks, though the song was known, the spoofers did not know what part of the song the original participant had imagined, or how it was imagined (humming, imagining a full performance, melody, vocals, etc).
-This experience sheds light on the highly individual nature of passthoughts, and provides a positive indication that there may be some intrinsic difficulty in spoofing attempts of passthoughts.
+This does not lessen the importance of this work however, as this sample size is comparable to that of previous scalp-based EEG passthoughts work\cite{Ashby2011, Marcel2007a, Palaniappan2008, palaniappan2006electroencephalogram, Poulos2002, Chuang2013b}, the only other in-ear EEG passthoughts study we are aware of \cite{curran2016passthoughts} (notably a generic fit system was used here), and other custom-fit in-ear EEG research \cite{kidmose2013study}.
+The fitting and manufacturing of custom-fit earpieces was the main limitation to increasing our sample size, and may very well pose a limitation in proliferation and adoption of such a technology.
+Recently however, there have been developments in at-home kits for creating one's own custom-fitted earpieces \cite{voix2015settable} that could help overcome this barrier.
 
@@
 
-Furthermore, the use of conductive gel results in low impedances on other participants' custom-fit earpieces, despite the uniqueness of ear canal shapes between individuals \cite{Akkermans2005}.
+Furthermore, likely due to the use of conductive gel, low impedances are still achievable using other participants' custom-fit earpieces, despite the uniqueness of ear canal shapes between individuals \cite{Akkermans2005}.
 Nevertheless, classifiers appear to resists spoofing attacks, indicating that task-related signals are unique to individuals.
-In the future, the custom-fit earbuds could easily include a hardware keypair to sign authentication attempts, providing a more secure method for establishing the possession factor in our three-factor, one-step scheme.
+In terms of establishing a possession factor, the custom-fit earpiecs could easily include a hardware keypair to sign authentication attempts in a three-factor, one-step scheme.
+
+The powerful interactions between inherence and knowledge emerged in our spoofing attack.
+Although our target participant documented their chosen passthought, the spoofers found ambiguity in how these passthoughts could be expressed.
+For the \textit{face} task, the spoofers did not know the precise friend the original participant had chosen.
+For the \textit{song} and \textit{song - open} tasks, though the song was known, the spoofers did not know what part of the song the original participant had imagined, or how it was imagined (humming, imagining a full performance, melody, vocals, etc).
+This experience sheds light on the highly individual nature of passthoughts, and provides a positive indication that there may be some intrinsic difficulty in spoofing attempts of passthoughts.
 
@@
 
-One primary question surrounds how our passthought system performance will change with a greater number of users, and with more diverse data.
-Our system specifically trains on negative examples of non-users; we do not yet know how this approach will scale.
-At the same time, we must investigate the stability of EEG readings for a passthought are over time.
+One primary question surrounds how our passthoughts system performance will change with a greater number of users, and with more diverse data.
+Our system specifically trains on negative examples of incorrect users; we do not yet know how this approach will scale.
+At the same time, we must investigate the stability of EEG readings for a passthought are over time to establish long-term usability.
 We must also collect EEG data from the variety of different user states: ambulatory settings, during physical exertion or exercise, under the influence of caffeine or alcohol, etc.
@@
 Future work should try using dry electrodes, commonly found in consumer EEG devices, for comfort and usability. The electrodes could be grounded to the ear, instead of the forehead.
-Additionally, future work could easily place a speaker inside our current custom-fit earbuds to produce working ``hearables'' that can be used as ordinary headphones.
+Additionally, future work could easily place a speaker inside our current custom-fit earbuds to produce working "hearables'' that can be used as ordinary headphones.
 
@@
 
-As demonstrated by these preliminary results, custom-fit, in-ear EEG earpieces provide three factors of authentication in a authentication single step: thinking one's password, using the discreet form factor of an earpiece.
+As demonstrated by these preliminary results, custom-fit, in-ear EEG earpieces provide three factors of authentication in a single authentication single: thinking one's password, using the discreet form factor of an earpiece.
 In this paper, we demonstrate quite high authentication accuracy using a single sensing earpiece.

### 2017-02-16 paper.tex

@@
 We find that we can achieve low false acceptance rates (FAR) and false rejection rates (FRR) with a single, 
-three-electrode earpiece.
-Interestingly, we found that performance in our protocol improves in the ear compared to a single electrode placed more traditionally on the scalp.
-Additionally, we find that passthoughts are not able to be spoofed by imposters, either from within the data set or outside of it, even when the imposters had a user's earpiece that fit their ear and knew their chosen passthoughts.
-We discuss the benefits of passthoughts for usable authentication, and raise questions for future pursuit about how and why passthoughts work as well as they do.
+three-electrode earpiece. Interestingly, we found that performance improves in the ear compared to a single electrode on the scalp.
+Additionally, we find that a passthoughts could not be spoofed by imposters, even when the imposters had the user's earpiece and knew their chosen passthoughts.
+We discuss future work to investigate the robustness of passthoughts in day-to-day life, and raise questions about how and why passthoughts work as well as they do.
 
@@
 For each configuration of electrodes, we calculated the mean FAR and FRR across all participants using each task as the passthought (Figure \ref{fig:meanByElectrode}).
-Incorporating all electrodes' data results in a perfect score for all tasks.
-Using data from all left-ear electrodes achieves the next lowest FAR, followed by all right ear electrodes.
-Notably, no single electrode from the left or right ear performs as well as the aggregate left and right ear conditions.
+Incorporating all electrodes data results in a perfect score for all tasks.
+Using data from all left-ear electrodes achieves the next lowest FAR.
+Interestingly, no single electrode performs as well as the aggregate left or both-ear plus Fp1 (all) conditions.
 
@@
 than 1\%. 
-Further, while FRR seemed to correlate roughly with FAR for most electrodes, the right concha and right canal front electrodes achieved extremely high FRRs, while their FARs were among the lowest.
+For each position, FAR was about ten times lower than FRR, which is preferable for authentication, as false authentications are potentially more costly than false rejections.
+% Further, while FRR seemed to correlate roughly with FAR for most electrodes, the right concha and right canal front electrodes achieved extremeley high FRRs, while their FARs were among the lowest. 
+% Since our results were similar in the right and left ear aggregate conditions, we proceed with only one ear (the left) in the following analyses.
 
@@
 In the previous section, we trained and tested a passthought classifier with each task as the passthought, for all participants.
-Our analyses revealed the choice between left and right ear to have little effect on the results and this enables us to postulate around a more usable device using sensors only around the left ear.
+Our analyses revealed the left produced decent results.
 Focusing on the left ear, we filter our results for the best-performing tasks.
 We rank tasks by lowest FAR and, given a tie, the lowest FRR (Table \ref{tab:best}).
+Overall, we find  a mean FAR of zero and mean FRR of 0.017\%.
 

### 2017-02-16 paper.tex
Adding FRR to captions of figures 3 and 4

@@
 %make title bold and 14 pt font (Latex default is non-bold, 16 pt)
-\title{\Large \bf One-Step, Three-Factor Authentication With Custom-Fit, In-Ear EEG}
+\title{\Large \bf One-Step, Three-Factor Authentication with Custom-Fit, In-Ear EEG}
 
@@
 We find that we can achieve low false acceptance rates (FAR) and false rejection rates (FRR) with a single, 
-three-electrode earpiece. Interestingly, we found that performance improves in the ear compared to a single electrode on the scalp.
+three-electrode earpiece. Interestingly, we found that performance improves in the ear compared to a single electrode on the scalp, a site typically used for collecting EEG data.
 Additionally, we find that a passthoughts could not be spoofed by imposters, even when the imposters had the user's earpiece and knew their chosen passthoughts.
@@
 \includegraphics[width=.9\linewidth]{./figures/mean-far-and-frr-by-electrode-config.png}
-\caption{FAR by electrode configuration. All electrodes combined achieves a perfect score. We achieve the next best scores using data from the left ear only.}
+\caption{FAR and FRR by electrode configuration.
+All electrodes (Fp1, right, and left ear channels) combined achieves a perfect FAR score.
+We achieve the next best scores using data from the left ear only.}
 \label{fig:meanByElectrode}
@@
 
-In the previous section, we trained and tested a passthought classifier with each task as the passthought, for all participants.
-Our analyses revealed the left produced decent results.
+In the previous section, we trained and tested a passthoughts classifier with each task as the passthought, for all participants.
+Our analyses revealed the left ear alone produced decent results.
 Focusing on the left ear, we filter our results for the best-performing tasks.
@@
 \includegraphics[width=.9\linewidth]{./figures/mean-far-and-frr-by-task.png}
-\caption{FAR by task, across all subjects, using data from the left ear only.}
+\caption{FAR and FRR results by task, across all subjects, using data from the left ear only.}
 \label{fig:meanByTask}

### 2017-02-16 paper.tex
Tiny mistake in abstract

@@
 In this paper, we present a system that provides all three factors of authentication (knowledge, possession, and inherence) in a single step by using brain-based authentication via custom-fit, in-ear electroencephalography (EEG).
-We demonstrate its potential by collecting electroencephalography (EEG) data from seven participants using manufactured custom-fit earpieces with embedded electrodes.
+We demonstrate its potential by collecting EEG data from 7 participants using manufactured custom-fit earpieces with embedded electrodes.
 Across all participants, we achieve mean 0\% false acceptance and 0.017\% false rejection rates with data from only one earpiece with three electrodes.

### 2017-02-16 paper.tex
minor proofs

--- 2017-02-16 paper.tex
@@
 \subsection*{Abstract}
-In this paper, we present a system that provides all three factors of authentication (knowledge, possession, and inherence) in a single step by using brain-based authentication via custom-fit, in-ear electroencephalography (EEG).
+We present a system that provides all three factors of authentication (knowledge, possession, and inherence) in a single step by using brain-based authentication via custom-fit, in-ear electroencephalography (EEG).
 We demonstrate its potential by collecting electroencephalography (EEG) data from seven participants using manufactured custom-fit earpieces with embedded electrodes.

### 2017-02-16 paper.tex
Fixing abstract again for some reason

@@
 We present a system that provides all three factors of authentication (knowledge, possession, and inherence) in a single step by using brain-based authentication via custom-fit, in-ear electroencephalography (EEG).
-We demonstrate its potential by collecting electroencephalography (EEG) data from seven participants using manufactured custom-fit earpieces with embedded electrodes.
+We demonstrate its potential by collecting EEG data from seven participants using manufactured custom-fit earpieces with embedded electrodes.
 Across all participants, we achieve mean 0\% false acceptance and 0.017\% false rejection rates with data from only one earpiece with three electrodes.

### 2017-02-17 paper.tex
Runaway argument? Can't compile PDF from tex file

@@
 We demonstrate its potential by collecting EEG data from seven participants using manufactured custom-fit earpieces with embedded electrodes.
-Across all participants, we achieve mean 0\% false acceptance and 0.017\% false rejection rates with data from only one earpiece with three electrodes.
+Across all participants, we are able to achieve perfect performance when we select participants' best performing tasks, mean 0\% false acceptance and 0\% false rejection rates, with data from only one earpiece with three electrodes.
 Furthermore, we find a 0\% false acceptance rate in a preliminary simulation of an impersonation attack.
@@
 three-electrode earpiece. Interestingly, we found that performance improves in the ear compared to a single electrode on the scalp, a site typically used for collecting EEG data.
-Additionally, we find that a passthoughts could not be spoofed by imposters, even when the imposters had the user's earpiece and knew their chosen passthoughts.
+Additionally, we find that passthoughts could not be spoofed by imposters, even when the imposters had the user's earpiece and knew their chosen passthoughts.
 We discuss future work to investigate the robustness of passthoughts in day-to-day life, and raise questions about how and why passthoughts work as well as they do.
@@
 Because three-factor authentication (3FA) requires the user to submit one distinct instance of each type of authenticator, it represents the strongest level of authentication security possible.
-The ability to utilize all three of these security factors in a single step by performing a mental task of a few seconds is a promising in pursuit of extremely strong security while maintaining a low amount of effort and obtrusiveness to the user.
- %% In addition to the dual knowledge and inherence factors established in previous work, this study incorporates a possession factor in the form of the EEG-sensing ear-piece(s) that are custom-fitted to and worn in their ear.
-These earpieces can serve as physical tokens in the same way as bank ATM cards and wearable hardware tokens by implementing a hardware key-pair.
- %% Furthermore, because the earpieces are custom-fitted to each individual, we predicted they would likely not be able to produce good electrical impedances when worn by a different individual.
+The ability to utilize all three of these security factors in a single step by performing a mental task of a few seconds is promising in pursuit of extremely strong security while maintaining a low amount of effort and obtrusiveness to the user.
 
@@
 During the experiment, participants were seated in a comfortable position in a quiet room facing a laptop screen on which the instructions and stimuli were presented using PsychoPy \cite{peirce2007psychopy}.
-Each task was completed once in sets five trials each, and then each was completed again for another five trials.
+Each task was completed once in sets of five trials each, and then each was completed again for another five trials.
 Each trial was 10 seconds in length, for a total of 10 trials and 100 seconds of data collected per task.
@@
 Our analyses revealed the left ear alone produced decent results.
-Focusing on the left ear, we filter our results for the best-performing tasks.
-We rank tasks by lowest FAR and, given a tie, the lowest FRR (Table \ref{tab:best}).
-Overall, we find  a mean FAR of zero and mean FRR of 0.017\%.
+Using only data from the left ear electrodes, the performance of each task for each participant is shown in Table \ref{tab:farfrrall}.
+For each participant we find at least one task for which they achieve 0\% FAR and FRR, indicating perfect performance for this pool of users.
 
-\begin{table}[h]
-\begin{center}
-\begin{tabular}{rrrl}
-\textbf{P} & \textbf{FAR} & \textbf{FRR} & \textbf{Task}\\
-\hline
-1 & 0.000 & 0.000 & Listen\\
-2 & 0.000 & 0.000 & Breathe\\
-3 & 0.000 & 0.000 & Breathe\\
-4 & 0.000 & 0.000 & Breathe\\
-5 & 0.000 & 0.012 & Breathe\\
-6 & 0.000 & 0.000 & Breathe\\
-7 & 0.000 & 0.000 & Breathe\\
-\end{tabular}
-\end{center}
-\caption{Best-performing passthought, with FAR and FRR, for each participant (P), using data from the left ear.}
-\label{tab:best}
-\end{table}
+\begin{table*}[t]
+\centering
+\begin{tabularx}{\textwidth}{lrrrrrrrrrrrrrr}
+& \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{P2}} & \multicolumn{2}{c}{\textbf{P3}} & \multicolumn{2}{c}{\textbf{P4}} & \multicolumn{2}{c}{\textbf{P5}} & \multicolumn{2}{c}{\textbf{P6}} & \multicolumn{2}{c}{\textbf{P7}}\\
+\textbf{Task} & FAR & FRR & FAR & FRR & FAR & FRR & FAR & FRR & FAR & FRR & FAR & FRR & FAR & FRR\\ \hline
+Breathe & 0.0002 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0.0127 & 0 & 0 & 0 & 0\\
+Breathe - open & 0.0002 & 0.0127 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0.0253 & 0 & 0 & 0 & 0\\
+Face & 0.0002 & 0.0253 & 0.0005 & 0.0253 & 0 & 0.0127 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
+Listen & 0 & 0 & 0.0005 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
+Sequence & 0 & 0.0506 & 0.0002 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0.0007 & 0.0127\\
+Song	 & 0.0002 & 0.0380 & 0 & 0 & 0	 & 0 & 0 & 0 & 0 & 0.0127 & 0 & 0 & 0.0007 & 0.0127\\
+Song - open & 0.0002 & 0.0127 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0.0127\\
+Speech & 0.0002 & 0 & 0.0005 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
+Sport & 0.0002 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0	 & 0.0127\\
+\textbf{Best Task} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\ \hline
+\end{tabularx}
+\caption{FAR and FRR performance of each task for each participant using data from the left ear.}
+\label{tab:farfrrall}
+\end{table*}
 
-All best-performing tasks in our best-case set achieved perfect FAR and FRRs, with the exception of P5, whose best-performing task (\textit{breathe}) had a nonzero FRR.
-\textit{Breathe} appeared as the best task across all participants, except P1.
+All best-performing tasks in our best-case set achieved perfect FAR and FRRs.
+Interestingly, \textit{breathe} appeared as the best task across all participants, except P1 whose best task was \textit{listen} and P5 who had several other best performing tasks.
 Given our training strategy, these results indicate that a given person's \textit{breathe} task is distinguishable not only among other tasks, but among \textit{breathe} tasks from other participants.
@@
 Overall, our original training strategy achieves the lowest FAR (Table \ref{tab:compare}).
-Within-tasks FAR ten times higher, and within-participants FAR is one hundred times higher, though all scenarios still less than 1\%.
+Within-tasks FAR is ten times higher, and within-participants FAR is one hundred times higher, though for all scenarios still less than 1\%.
 However, FRR is \textit{lower} in the within-tasks training strategy than in our original strategy's FRR. Within-participants again results in the highest FRR.
@@
 
-While our left ear results establish that passthoughts achieve low FAR and FRR when tested against other participants' passthoughts, we do not know how robust passthoughts are against a spoofing attack, in which both a participant's custom-fit electrode, and details of that participant's chosen passthought, are leaked and used by an imposter.
+While our authentication analysis establishes that passthoughts achieve low FAR and FRR when tested against other participants' passthoughts, we do not know how robust passthoughts are against a spoofing attack, in which both a participant's custom-fit electrode, and details of that participant's chosen passthought, are leaked and used by an imposter.
 
@@
 To explore the efficacy of an outsider spoofing recordings, we repeated the same protocol with an individual who did not appear in our initial set of participants (an "outside imposter,'' Table \ref{tab:imposter}).
-Again, find zero successful authentication attempts.
+Again, we find zero successful authentication attempts out of 1,800 attempts.
 
@@
 In our analysis, some notable patterns emerged.
-First, \textit{breathe} tended to be the best-performing task among participants.
-Classifiers overall distinguished the \textit{breathe} task even compared to \textit{breathe} tasks from other participants, implying that the task is expressed differently for each participant, i.e.
-that this task has an inherence factor sufficient for authentication, even though the task does not have an explicit secondary knowledge factor as in \textit{song}, for example.
+First, the \textit{breathe}, \textit{breathe-open}, and \textit{listen} tasks performed exceedingly well among participants.
+Classifiers overall distinguished the \textit{breathe}  and \texit{listen} tasks even compared to the same tasks from other participants, implying that these tasks are expressed differently for each participant, i.e.
+that they have an inherence factor sufficient for authentication, even though they task do not involve an explicit secondary knowledge factor as in \textit{sport} or \texit{song}, for example.
 Second, we were able to achieve good results by generating feature vectors based on only 500ms (300 voltage readings across the three electrodes).
@@
 Nevertheless, classifiers appear to resists spoofing attacks, indicating that task-related signals are unique to individuals.
-In terms of establishing a possession factor, the custom-fit earpiecs could easily include a hardware keypair to sign authentication attempts in a three-factor, one-step scheme.
+In terms of establishing a possession factor, the custom-fit earpieces could easily include a hardware keypair to sign authentication attempts in a three-factor, one-step scheme.
 
@@
 Our system specifically trains on negative examples of incorrect users; we do not yet know how this approach will scale.
-At the same time, we must investigate the stability of EEG readings for a passthought are over time to establish long-term usability.
+At the same time, we must investigate the stability of EEG readings for a passthought over time to establish long-term usability.
 We must also collect EEG data from the variety of different user states: ambulatory settings, during physical exertion or exercise, under the influence of caffeine or alcohol, etc.
@@
 Future work should perform statistical analysis on passthoughts, such as clustering (perhaps with t-SNE) to better understand the space of possible passthoughts.
-This work will allow us simulate cracking attempts, and to develop empirically motivated strategies for prevention, e.g. locking users out after a certain number of attempts.
+This work will allow us simulate cracking attempts, and to develop empirically motivated strategies for prevention, e.g., locking users out after a certain number of attempts.
 This work could also reveal interesting tradeoffs between the usability or accuracy of passthoughts and their security.
 
-Finally, our work leaves room for some clear UX improvements.
+Finally, our work leaves room for some clear user experience (UX) improvements.
 Future work should try using dry electrodes, commonly found in consumer EEG devices, for comfort and usability. The electrodes could be grounded to the ear, instead of the forehead.
@@
 
-As demonstrated by these preliminary results, custom-fit, in-ear EEG earpieces provide three factors of authentication in a single authentication single: thinking one's password, using the discreet form factor of an earpiece.
+As demonstrated by these preliminary results, custom-fit, in-ear EEG earpieces provide three factors of authentication in a single authentication step: thinking one's passthought, using the discreet form factor of an earpiece.
 In this paper, we demonstrate quite high authentication accuracy using a single sensing earpiece.

### 2017-02-17 paper.tex
fixed compiler error

@@
 
-In our analysis, some notable patterns emerged.
-First, the \textit{breathe}, \textit{breathe-open}, and \textit{listen} tasks performed exceedingly well among participants.
-Classifiers overall distinguished the \textit{breathe}  and \texit{listen} tasks even compared to the same tasks from other participants, implying that these tasks are expressed differently for each participant, i.e.
-that they have an inherence factor sufficient for authentication, even though they task do not involve an explicit secondary knowledge factor as in \textit{sport} or \texit{song}, for example.
-Second, we were able to achieve good results by generating feature vectors based on only 500ms (300 voltage readings across the three electrodes).
-This short timespan is somewhat surprising, given that some tasks (like songs) presumably rely on changes or patterns over a longer period of time.
+In our analysis, some notable patterns emerged. First, the \textit{breathe},
+\textit{breathe-open}, and \textit{listen} tasks performed exceedingly well among participants.
+Classifiers overall distinguished the \textit{breathe}  and \textit{listen} tasks even compared
+to the same tasks from other participants, implying that these tasks are expressed differently
+for each participant, i.e. that they have an inherence factor sufficient for authentication,
+even though they task do not involve an explicit secondary knowledge factor as in \textit{sport}
+or \textit{song}, for example. Second, we were able to achieve good results by generating feature
+vectors based on only 500ms (300 voltage readings across the three electrodes).
+This short timespan is somewhat surprising, given that some tasks (like songs)
+presumably rely on changes or patterns over a longer period of time.
 

### 2017-02-17 paper.tex
Fixing table 3, abstract, results, and discussion for 0 FRR and FAR update

@@
 \centering
-\begin{tabularx}{\textwidth}{lrrrrrrrrrrrrrr}
-& \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{P2}} & \multicolumn{2}{c}{\textbf{P3}} & \multicolumn{2}{c}{\textbf{P4}} & \multicolumn{2}{c}{\textbf{P5}} & \multicolumn{2}{c}{\textbf{P6}} & \multicolumn{2}{c}{\textbf{P7}}\\
-\textbf{Task} & FAR & FRR & FAR & FRR & FAR & FRR & FAR & FRR & FAR & FRR & FAR & FRR & FAR & FRR\\ \hline
-Breathe & 0.0002 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0.0127 & 0 & 0 & 0 & 0\\
-Breathe - open & 0.0002 & 0.0127 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0.0253 & 0 & 0 & 0 & 0\\
-Face & 0.0002 & 0.0253 & 0.0005 & 0.0253 & 0 & 0.0127 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
-Listen & 0 & 0 & 0.0005 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
-Sequence & 0 & 0.0506 & 0.0002 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0.0007 & 0.0127\\
-Song	 & 0.0002 & 0.0380 & 0 & 0 & 0	 & 0 & 0 & 0 & 0 & 0.0127 & 0 & 0 & 0.0007 & 0.0127\\
-Song - open & 0.0002 & 0.0127 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0.0127\\
-Speech & 0.0002 & 0 & 0.0005 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
-Sport & 0.0002 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0	 & 0.0127\\
-\textbf{Best Task} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\ \hline
+\begin{tabularx}{\textwidth}{lrrrrrrrrrr}
+& \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{P2}} & \multicolumn{2}{c}{\textbf{P3}} & \multicolumn{2}{c}{\textbf{P5}} & \multicolumn{2}{c}{\textbf{P7}}\\
+\textbf{Task} & FAR & FRR & FAR & FRR & FAR & FRR & FAR & FRR & FAR & FRR\\ \hline
+Breathe & 0.0002 & 0 & 0 & 0 & 0 & 0 & 0 & 0.0127 & 0 & 0\\
+Breathe - open & 0.0002 & 0.0127 & 0 & 0 & 0 & 0 & 0 & 0.0253 & 0 & 0\\
+Face & 0.0002 & 0.0253 & 0.0005 & 0.0253 & 0 & 0.0127 & 0 & 0 & 0 & 0\\
+Listen & 0 & 0 & 0.0005 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
+Sequence & 0 & 0.0506 & 0.0002 & 0 & 0 & 0 & 0 & 0 & 0.0007 & 0.0127\\
+Song	 & 0.0002 & 0.0380 & 0 & 0 & 0	 & 0 & 0 & 0.0127 & 0.0007 & 0.0127\\
+Song - open & 0.0002 & 0.0127 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0.0127\\
+Speech & 0.0002 & 0 & 0.0005 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
+Sport & 0.0002 & 0 & 0 & 0 & 0 & 0 & 0 & 0  & 0 & 0.0127\\
+\textbf{Best Task} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\ \hline
 \end{tabularx}
-\caption{FAR and FRR performance of each task for each participant using data from the left ear.}
+\caption{FAR and FRR performance of each task for each participant using data from the left ear. P4 and P6 achieve perfect zero FARs and FRRs across all tasks and so are not shown here.}
 \label{tab:farfrrall}

### 2017-03-31 paper.tex
Reworked usable authentication section, removed imposter table, added keywords, reduced usability results text

@@
-% TEMPLATE for Usenix papers, specifically to meet requirements of
+\documentclass{sigchi}
 
-% https://www.usenix.org/conference/usenixsecurity17/submitting-papers
+% Use this command to override the default ACM copyright statement (e.g. for preprints). 
+% Consult the conference website for the camera-ready copyright statement.
 
-% Complaints to /dev/null.
-% This version uses the latex2e styles, not the very ancient 2.09 stuff.
-\documentclass[letterpaper,twocolumn,10pt]{article}
-\usepackage{lib/usenix,epsfig,endnotes,tabularx}
+%% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
+% \toappear{Permission to make digital or hard copies of all or part of this work for personal or classroom use is 	granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page.
+Copyrights for components of this work owned by others than ACM must be honored.
+Abstracting with credit is permitted.
+To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee.
+Request permissions from permissions@acm.org.
+\\
+% {\emph{CHI'14}}, April 26--May 1, 2014, Toronto, Canada. \\
+% Copyright \copyright~2014 ACM ISBN/14/04...\$15.00. \\
+% DOI string from ACM form confirmation}
+%% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
+
+% Arabic page numbers for submission. 
+% Remove this line to eliminate page numbers for the camera ready copy
+% \pagenumbering{arabic}
+
+% Load basic packages
+%\usepackage{balance}  % to better equalize the last page
+%\usepackage{graphics} % for EPS, load graphicx instead
+\usepackage{epsfig} % Max added
+\usepackage{times}    % comment if you want LaTeX's default font
+\usepackage{url}      % llt: nicely formatted URLs
+\usepackage{tabularx} % Max added
+
+% llt: Define a global style for URLs, rather that the default one
+\makeatletter
+\def\url@leostyle{%
+  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\bf\ttfamily}}}
+\makeatother
+\urlstyle{leo}
+
+% To make various LaTeX processors do the right thing with page size.
+\def\pprw{8.5in}
+\def\pprh{11in}
+\special{papersize=\pprw,\pprh}
+\setlength{\paperwidth}{\pprw}
+\setlength{\paperheight}{\pprh}
+\setlength{\pdfpagewidth}{\pprw}
+\setlength{\pdfpageheight}{\pprh}
+
+% Make sure hyperref comes last of your loaded packages, 
+% to give it a fighting chance of not being over-written, 
+% since its job is to redefine many LaTeX commands.
+\usepackage[pdftex]{hyperref}
+\hypersetup{
+pdftitle={SIGCHI Conference Proceedings Format},
+pdfauthor={LaTeX},
+pdfkeywords={SIGCHI, proceedings, archival format},
+bookmarksnumbered,
+pdfstartview={FitH},
+colorlinks,
+citecolor=black,
+filecolor=black,
+linkcolor=black,
+urlcolor=black,
+breaklinks=true,
+}
+
+% create a shortcut to typeset table headings
+\newcommand\tabhead[1]{\small\textbf{#1}}
+
+% End of preamble. Here it comes the document.
 \begin{document}
 
-%don't want date printed
-\date{}
+\title{One-Step, Three-Factor Authentication via Ear EEG}
 
-%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
-\title{\Large \bf One-Step, Three-Factor Authentication with Custom-Fit, In-Ear EEG}
-
-%forsupose single author (just remove % characters)
+\numberofauthors{4}
 \author{
-{\rm First Name, Second Name, Third Name}\\
-First Institution
-\and
-{\rm Second Name}\\
-Second Institution
-% copy the following lines to add more authors
-% \and
-% {\rm Name}\\
-%Name Institution
-} % end author
+  \alignauthor 1st Author\\
+    \affaddr{Affiliation}\\
+    \email{e-mail}\\
+  \alignauthor 2nd Author\\
+    \affaddr{Affiliation}\\
+    \email{e-mail}\\
+  \alignauthor 3rd Author\\
+    \affaddr{Affiliation}\\
+    \email{e-mail}\\
+  \alignauthor 4th Author\\
+    \affaddr{Affiliation}\\
+    \email{e-mail}\\
+}
 
@@
 
-% Use the following at camera-ready time to suppress page numbers.
-% Comment it out when you first submit the paper for review.
-\thispagestyle{empty}
+\begin{abstract}
+ Multifactor authentication presents a robust method to secure our increasingly digitized private information, but typically requires multiple actions on the part of the user resulting in a high cost to usability and limiting adoption.
+Furthermore, a truly usable system must be unobtrusive and inconspicuous.
+Here, we present a system that provides all three factors of authentication (knowledge, possession, and inherence) in a single step in the form of an earpiece which implements brain-based authentication via custom-fit, in-ear electroencephalography (EEG).
+We demonstrate its potential by collecting EEG data using manufactured custom-fit earpieces with embedded electrodes.
+Across all participants, we are able to achieve perfect performance, mean 0\% false acceptance and 0\% false rejection rates, using participants' best performing tasks with data from only one earpiece with three electrodes.
+Furthermore, we find a 0\% false acceptance rate in a simulation of an impersonation attack.
+We also report perspectives from our participants and discuss constructive directions for future work toward real-world use.
+Our results indicate that a single earpiece with embedded electrodes could provide a discreet, convenient, and robust method for secure one-step, three-factor authentication.
+\end{abstract}
 
-\subsection*{Abstract}
-We present a system that provides all three factors of authentication (knowledge, possession, and inherence) in a single step by using brain-based authentication via custom-fit, in-ear electroencephalography (EEG).
-We demonstrate its potential by collecting EEG data from seven participants using manufactured custom-fit earpieces with embedded electrodes.
-Across all participants, we are able to achieve perfect performance when we select participants' best performing tasks, mean 0\% false acceptance and 0\% false rejection rates, with data from only one earpiece with three electrodes.
-Furthermore, we find a 0\% false acceptance rate in a preliminary simulation of an impersonation attack.
-We also report some positive usability perspectives from our participants and discuss constructive directions for future work.
-Our results indicate that in-ear EEG could provide a discreet, convenient, and usable method for secure one-step, three-factor authentication.
+\keywords{
+  usable security; multi-factor authentication; wearable authentication; bio-sensory computing; passthoughts
+}
+
+%\category{H.5.m.}{Information Interfaces and Presentation (e.g. HCI)}{Miscellaneous}
+
+%See: \url{http://www.acm.org/about/class/1998/}
+%for more information and the full list of ACM classifiers
+%and descriptors. \newline
+%\textcolor{red}{Optional section to be included in your final version, 
+%but strongly encouraged. On the submission page only the classifiers’ 
+%letter-number combination will need to be entered.}
 
 \section{Introduction}
-\label{sec:org7196b99}
 
@@
 
-In previous work, "one-step two-factor authentication" has been proposed as a new approach to authentication that can provide the security benefits of two-factor authentication without incurring the hassle cost of two-step verification.
+"One-step two-factor authentication" has been proposed as a new approach
+to authentication that can provide the security benefits of two-factor authentication without incurring the hassle cost of two-step verification.
 In this study we undertake, to the best of our knowledge, the first
@@
 in the form of personalized earpieces, the uniqueness of an individual's brainwaves, and
-a choice of mental task to use as one's passthoughts, we seek to achieve all three factors 
+a choice of mental task to use as one's "passthought", we seek to achieve all three factors 
 of authentication in a single step by the user.
 
-We find that we can achieve low false acceptance rates (FAR) and false rejection rates (FRR) with a single, 
-three-electrode earpiece. Interestingly, we found that performance improves in the ear compared to a single electrode on the scalp, a site typically used for collecting EEG data.
+Furthermore, the form factor of an earpiece is a significant improvement over scalp-based passthoughts systems toward real-world use.
+Technology worn in the ear is already an acceptable practice in examples such as earphones and bluetooth headsets.
+
+We find that we can achieve very low false acceptance rates (FAR) and false rejection rates (FRR) with a single, 
+three-electrode earpiece.
+Interestingly, we found that performance improves in the ear compared to a single electrode on the scalp, a site typically used for collecting EEG data.
 Additionally, we find that passthoughts could not be spoofed by imposters, even when the imposters had the user's earpiece and knew their chosen passthoughts.
@@
 \subsection{Passthoughts Authentication}
-The use of EEG as a biometric signal for user authentication has a short history.
+The use of EEG as a biometric signal for user authentication has a relatively short history.
 In 2005, Thorpe et al. motivated and outlined the design of a passthoughts system \cite{Thorpe2005}.
@@
 In 2013, one group showed that 99\% authentication accuracy can also be
-achieved using a consumer-grade single-channel sensor \cite{Chuang2013b}. In particular, the
-lack of signal diversity from multiple EEG channels can be overcome by allowing
-the users to choose their own personalized passthoughts (e.g., sing their favorite
-song in their head). There are two significant consequences of this result. First,
+achieved using a consumer-grade single-channel sensor on the scalp \cite{Chuang2013b}. In particular, they proposed that the
+lack of signal diversity from multiple EEG channels can be overcome by allowing users to choose their own personalized passthoughts (e.g., sing their favorite song in their head).
+There are two significant consequences of this result.
+First,
 the passthoughts approach is no longer constrained by the high cost (\textgreater \$10,000 USD)
-and low usability (gel-based electrodes; aesthetic challenges of a full EEG cap) of
+and low usability (gel-based electrodes in hair; aesthetic challenges of a full EEG cap) of
 medical-grade multi-channel devices. Second, because users can choose and
@@
 By employing scalp-based consumer-grade electroencephalography (EEG), it was demonstrated in a 2014 passthoughts study that a user can submit both a knowledge factor (i.e., secret thought) and an inherence factor (i.e., brainwave signal unique to the individual) in a single step by performing a single mental task \cite{Chuang2014}.
-Additionally, the robustness of this method against impersonation attacks was demonstrated, including conditions where the attacker may have learned the target'۪s secret thought and/or secret task \cite{Johnson2014}.
+Additionally, the robustness of this method against impersonation attacks was demonstrated, including conditions where the attacker may have learned the target's secret thought and/or secret task \cite{Johnson2014}.
 
 Following this, we investigate custom-fit in-ear EEG technology as the platform for investigating the feasibility, performance, and usability of one-step three-factor authentication worn unobtrusively.
-The system we propose and test here uses the choice of a mental task or "passthought" to perform as knowledge (factor one), the uniqueness of an individual's brain activity as measured by EEG as inherence (factor two), and the physical token of custom-fit earpieces, which could easily contain a hardware key-pair, as a possession factor (factor 3).
+The system we propose and test here uses the choice of a mental task or "passthought" to perform as knowledge (factor one), the uniqueness of an individual's brain activity as measured by EEG as inherence (factor two), and the physical token of a custom-fit earpiece that could easily contain a hardware key-pair, as a possession factor (factor 3).
 Because three-factor authentication (3FA) requires the user to submit one distinct instance of each type of authenticator, it represents the strongest level of authentication security possible.
-The ability to utilize all three of these security factors in a single step by performing a mental task of a few seconds is promising in pursuit of extremely strong security while maintaining a low amount of effort and obtrusiveness to the user.
+The ability to utilize all three of these security factors in a single step by performing a mental task of a few seconds is promising in pursuit of extremely strong security while maintaining a low amount of effort and obtrusiveness to the user, and could even be enjoyable.
 
@@
 Even consumer-grade headsets can be uncomfortable to wear, and are awkwardly visible to outside observers.
-Sensors placed around the ear however, present a more discreet, comfortable location for an EEG sensor, as many people already wear technology like earbuds in day-to-day life.
+Sensors placed around the ear, however, present a far more discreet, comfortable location for EEG electrodes, as many people already wear technology like earbuds in day-to-day life.
 
 Research in in-ear EEG is only several years old. Nonetheless, the concept has
-attracted a lot of attention because of the discreetness factor of in-ear EEG over
+attracted attention because of the discreetness factor of in-ear EEG over
 traditional scalp-based EEG. A research team at the Imperial College London
@@
 \cite{Looney2012a,Kidmose2013a,Kidmose2013b}.
-United Sciences is currently developing a consumer "hearable'' (in-ear wearable) called The Aware, which will measure EEG from the ear, among other biometrics \cite{UnitedSciences}.
+United Sciences is currently developing a consumer "hearable" (in-ear wearable) called The Aware, which will measure EEG from the ear, among other biometrics \cite{UnitedSciences}.
 
 \cite{curran2016passthoughts} was the first to merge in-ear EEG with passthought authentication,
- using a modified consumer grade EEG device with a single electrode, achieving approximately 80\% authentication accuracy.
+ using a minimally modified consumer-grade EEG device with a single electrode, achieving approximately 80\% authentication accuracy.
 
 \subsection{One-Step, Multi-Factor Authentication}
-Behavioral authentication methods such as keystroke dynamics and speaker
-authentication can be categorized as one-step two-factor authentication
-schemes. In both cases, the knowledge factor (password or passphrase) and
-inherence factor (typing rhythm or speaker's voice) are employed \cite{Monrose1997}.
-In contrast, the Nymi band supports one-step two-factor authentication via the inherence
-factor (cardiac rhythm that is supposed to be unique to each individual) and the
-possession factor (the wearing of the band on the wrist) \cite{Nymi}.
-However, as far as we know, no one has proposed or demonstrated a one-step three-factor
-authentication scheme, in which possession of a unique device also serves to authenticate the user.
-In this paper, we introduce custom-built EEG devices, incorporating an added possession factor to the already one-step two-factor authentication provided by passthoughts.
+Behavioral authentication methods such as keystroke dynamics and speaker authentication can be categorized as one-step two-factor authentication schemes.
+In both cases, the knowledge factor (password or passphrase) and inherence factor (typing rhythm or speaker's voice) are employed \cite{Monrose1997}.
+In contrast, the Nymi band supports one-step two-factor authentication via the inherence factor (cardiac rhythm that is supposed to be unique to each individual) and the possession factor (the wearing of the band on the wrist) \cite{Nymi}.
+However, as far as we know, no one has proposed or demonstrated a one-step three-factor authentication scheme, in which possession of a unique device also serves to authenticate the user.
+In this paper, we introduce custom-built EEG devices, incorporating an added possession factor to the already one-step two-factor authentication of passthoughts.
 
@@
 
-Typical authentication protocols are often susceptible to a so-called \textit{rubber-hose attack}, in which users are coerced into giving up their chosen secret (e.g.
+When proposing or evaluating authentication paradigms, robustness against imposters is often the first consideration, but the usability of these systems is of equal importantance as they must conform to a person's needs and lifestyle to warrant adoption and prolonged use.
+In \cite{sasse2001}, the authors describe usability issues with knowledge-based systems like alphanumeric passwords, in particular that it should not be the burden of the user to remember complex passwords that have to be frequently changed.
+\cite{braz2006} analyze some of the complexities applying traditional interface human factors heuristics to authentication, and indicate the importance of social acceptibility, learnability, and simplicity of authentication methods.
+
+Head-worn devices face particular usability issues; in their analysis of user perceptions of such devices, \cite{Genaro2014} identify design, usability, ease of use, and obtrusiveness among the top 10 concerns of users of these devices and qualitative concerns about comfort or "looking weird".
+
+Mobile and wearable technologies' continuous proximity to the user's body provides favorable conditions for unobtrusively capturing biometrics for authentication.
+Many such uses have been proposed that embrace usability such as touch-based interactions \cite{Tartz2015, Holz2015} and walking patterns \cite{Lu2014} using mobile phones, as well as identification via head movements and blinking in head-worn devices \cite{Rogers2015}.
+However, these typically draw only from the inherence factor (though could incorporate the possession factor of the device).
+\cite{Chen2015} proposed an inherence and knowledge two-factor method for multi-touch mobile devices based on a user's unique finger tapping of a song, though this may be vulnerable to "shoulder surfing": imposters observing and mimicking the behavior.
+By comparison, passthoughts are largely invisible to attackers.
+This system also presents a solution to "rubber-hose attacks" (forceful coercion to divulge a password): a thought, which is secret (and thus changeable), but has a particular expression unique to an individual, the performance of which cannot be described (and thus cannot be coerced).
+
+%% 3/28
+
+% Typical authentication protocols are often susceptible to a so-called \textit{rubber-hose attack}, in which users are coerced into giving up their chosen secret (e.g.
 alphanumeric password), biometric, or unique token, voluntarily or otherwise \cite{Bojinov2012, Martinovic2012}.
@@
 
-Past work has exploited tacit skills (skills we know how to do, but cannot readily explain our method for doing, e.g.
+% Past work has exploited tacit skills (skills we know how to do, but cannot readily explain our method for doing, e.g.
 riding a bike or walking \cite{Bojinov2012}.
@@
 
-Our work explores a different solution to rubber-hose attacks: a thought, which is secret (and thus changeable), but has a particular expression unique to an individual, the performance of which cannot be described (and thus cannot be coerced).
-Furthermore, the performance of the chosen thought is largely invisible to outside observers, ensuring the actual authentication is impervious to shoulder-surfing.
+% Our work explores a different solution to rubber-hose attacks: a thought, which is secret (and thus changeable), but has a particular expression unique to an individual, the performance of which cannot be described (and thus cannot be coerced).
+% Furthermore, the performance of the chosen thought is largely invisible to outside observers, ensuring the actual authentication is impervious to shoulder-surfing.
 
@@
 
-7 male participants (P1-P7), 5 students and 2 non-students, completed our study protocol that was approved by our local Institutional Review Board.
-Three study visits took place per participant, in the first the 3D molds of participants' ears to use in creating the earpieces were obtained, the second was a fit and electrical impedance check once earpieces were manufactured, and the third to collect data using the earpieces while participants performed a set mental tasks to be used in authentication analysis.
-Informed consent was obtained prior to study procedures.
-The third study visit consisted of participants completing a short demographics questionnaire, a set up period with the OpenBCI system and earpieces including a second impedance check, the performance of 9 mental tasks presented on a laptop, and finally a post-experiment questionnaire.
-Approximately two weeks after the third study visit, a subset of participants reported via e-mail whether or not they remembered the passthoughts they chose and performed during the third visit.
+Seven male, right-handed participants (P1-P7), 5 students and 2 non-students, completed our study protocol approved by our local ethics review board.
+Though this sample is relatively homogenous, this quality interestingly functions to strengthen the results of this initial exploration (see details in Discussion).
+After participants' 3D ear molds were obtained and their fit and electrical impedance was checked, the collection of data for authentication analyses commenced.
+Data collection consisted of participants completing a short questionnaire, a set up period with the OpenBCI system and earpieces including a second impedance check, the performance of 9 mental tasks presented on a laptop, and finally a post-experiment questionnaire.
 
@@
 \centering
-\includegraphics[width=.9\linewidth]{./figures/CFEEEG_piecefig_Right.jpg}
+\includegraphics[width=.75\linewidth]{./figures/CFEEEG_piecefig_Right.jpg}
 \caption{Labeled photo of one of our manufactured custom-fit earpieces with 3 embedded electrodes located in the concha, front-facing (anterior) in the ear canal, and back-facing (posterior) in the ear canal.}
@@
 
-\label{sec:orgaf30da9}
+%\label{sec:orgaf30da9}
 \subsection{Mental Tasks}
@@
 \subsection{Data Collection Protocol}
-\label{sec:org2041857}
-The data collection visit took approximately 90 minutes for set up and experiment execution.
-All collection sites were cleaned with ethanol prior to electrode placement, and a small amount of conductive gel was used on each electrode.
+%\label{sec:org2041857}
+All sites were cleaned with ethanol prior to electrode placement and a small amount of conductive gel was used on each electrode.
 For EEG recording we used OpenBCI \cite{michalska2009openbci}, an open-source biosensing system to maintain an overall low cost for our setup.
-OpenBCI costs about 600 USD, and thus is an affordable alternative to medical-grade EEG systems that can cost tens of thousands of dollars.
-Recent work has demonstrated the robustness of OpenBCI compared to an industry standard medical-grade EEG system, particularly for non-medical use cases such as ours \cite{Frey2016}.
+OpenBCI costs about 600 USD, and thus is an affordable alternative to medical-grade EEG systems (about 20,000 USD), and has demonstrated effectiveness for non-medical use cases such as this one \cite{Frey2016}.
 The OpenBCI system we used allows for 8 channels of simultaneous recording, along with separate ground and reference channels.
 Data was collected with the ground placed at the center of the forehead, approximately AFz according to the 10-20 International Standard for Electrode Placement (ISEP), and using the left mastoid as reference.
-Notably, when examining data from the right earpiece, we re-referenced to the right mastoid channel so that our results reflect data from a single ear.
-Each earpiece (shown in Figure \ref{fig:earpiece_diagram}) contains three channels, for the remaining two channels AgCl ring electrodes were placed on the right mastoid for later re-referencing, and at approximately Fp1 (left frontal lobe region, above the left eye in accordance with the ISEP) for validating the data collected in the ears against a common scalp-based placement.
+6 channels were used for the three electrodes on Eech earpiece (shown in Figure \ref{fig:earpiece_diagram}), for the remaining two channels AgCl ring electrodes were placed on the right mastoid for later re-referencing, and at approximately Fp1 (above the left eye in in the ISEP) for validating the data collected in the ears against a common scalp-based placement.
 Before beginning the experiment, the data from each channel was visually inspected using the OpenBCI interface and participants were asked to blink and clench their jaws to confirm that all channels were active and properly connected.
-Audio stimuli were delivered through small tubes in the earpieces opening into the ear canal.
+Audio stimuli were delivered through small tubes in the earpieces.
 
-During the experiment, participants were seated in a comfortable position in a quiet room facing a laptop screen on which the instructions and stimuli were presented using PsychoPy \cite{peirce2007psychopy}.
-Each task was completed once in sets of five trials each, and then each was completed again for another five trials.
+During the experiment, participants were seated in a comfortable position in a quiet room facing a laptop on which the instructions and stimuli were presented using PsychoPy \cite{peirce2007psychopy}.
+The entire set of tasks was completed once over with five trials each, followed by another five trials each in order to reduce boredom and repetition effects of a single task.
 Each trial was 10 seconds in length, for a total of 10 trials and 100 seconds of data collected per task.
@@
 \section{Analysis}
-\label{sec:org6c1a839}
+%\label{sec:org6c1a839}
 \subsection{Data Validation}
-\label{sec:org800f2bd}
+%\label{sec:org800f2bd}
 
-In this section, we establish that the data we collected were of a neural origin, and had relatively little noise.
 We were able to confirm the custom-fit earpieces are able to collect EEG data via two metrics: good impedances measured for the ear electrodes, and alpha-band EEG activity attenuation when a participant's eyes were open versus closed.
 
-The first quality check was examining the electrical impedances achieved for the ear pieces as a low impedance ($<$10 kOhm) 
-is best for obtaining quality EEG signals.
+It is important that the electrical impedances achieved for electrodes are low ($<$10 kOhm) 
+to obtain quality EEG signals.
 Table \ref{tab:impedances} below summarizes the impedances across the seven participants' six ear channels.
-With the exception of a few channels in select participants, impedances achieved were overall good.
+With the exception of a few channels in select participants, impedances achieved were good overall.
 Most of the recorded impedances of the earpiece electrodes were less than 5 k\(\Omega\), a benchmark used widely in previous ear EEG work, and all except two were less than 10 k\(\Omega\).
@@
 
-For the alpha-attenuation test, data from the \textit{breathe} task was compared with that of the \textit{breathe - open} task. It is a well-
-known feature of EEG data that activity in the alpha-band (approximately 8-12 Hz range) increases when the eyes are closed
-compared with a similar state with eyes open. For our participants, this attenuation is clearly visible even in just
-a single trial's data. To further validate, we also performed this calculation on the data collected from the Fp1 electrode and see
-the effect clearly here as well to compare.
+For the alpha-attenuation test, data from the \textit{breathe} task was compared with that of the \textit{breathe - open} task.
+It is a well-known feature of EEG data that activity in the alpha-band (approximately 8-12 Hz range) increases when the eyes are closed compared with a similar state with eyes open.
+For our participants, this attenuation is clearly visible even in just a single trial's data.
+We also performed this comparison on the data collected from the Fp1 electrode and see the effect clearly there as well to compare.
 Figure \ref{fig:alpha_atten} shows the alpha attenuation in the left ear channels, as well as Fp1 of one participant as an example.
@@
 We analyzed the EEG signals collected during the tasks using a support vector classifier (SVC).
-Since past work has shown that classification tasks in EEG-based BCI are linear \cite{Garrett2003a}, we used XGBoost, a tool for logistic linear classification \cite{Chen2016}.
+Since past work has shown that classification tasks in EEG-based BCI are linear \cite{Garrett2003a}, we used XGBoost, a popular tool for logistic linear classification \cite{Chen2016}.
 Compared to other linear classifiers, XGBoost uses gradient boosting; in which an algorithm generates an ensemble (in this case, a decision tree) of weak linear classifiers that minimizes a given loss function.
-Gradient boosting gives better results in linear classification problems, without our needing to manually tune classifier hyperparameters.
+Gradient boosting gives better results in linear classification problems, without our needing to manually tune classifier hyperparameter.
 
@@
 The remaining training set was fed into a XGBoost's cross-validation method, which we set to iteratively tweak parameters over a maximum of fifty rounds of cross-validation to minimize loss.
-After cross-validation, the updated classifier (with parameters applied) predicted labels on each sample in the test set, and we calculated FAR and FRR on its results.
+After cross-validation, the updated classifier (with parameters applied) predicted labels on each sample in the test set, and we calculated FAR and FRR from its results.
 
 \section{Results}
-\label{sec:org6705b1d}
+%\label{sec:org6705b1d}
 \subsection{Combinations of electrodes}
-\label{sec:org21b14ae}
+%\label{sec:org21b14ae}
 
@@
 
-Counter to our expectations, Fp1 does not perform as well as most ear electrodes, though overall these reported rates are far less 
-than 1\%. 
+Counter to our expectations, Fp1 does not perform as well as most ear electrodes, though overall these reported rates are far less than 1\%. 
 For each position, FAR was about ten times lower than FRR, which is preferable for authentication, as false authentications are potentially more costly than false rejections.
-% Further, while FRR seemed to correlate roughly with FAR for most electrodes, the right concha and right canal front electrodes achieved extremeley high FRRs, while their FARs were among the lowest. 
-% Since our results were similar in the right and left ear aggregate conditions, we proceed with only one ear (the left) in the following analyses.
 
@@
 \centering
-\begin{tabularx}{\textwidth}{lrrrrrrrrrr}
+\begin{tabularx}{.85\textwidth}{lrrrrrrrrrr}
 & \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{P2}} & \multicolumn{2}{c}{\textbf{P3}} & \multicolumn{2}{c}{\textbf{P5}} & \multicolumn{2}{c}{\textbf{P7}}\\
@@
 Within-participants & 0.002523 & 0.039702\\
+\hline
 \end{tabular}
@@
 This questionnaire asked them to rank each of the mental tasks on 7-point likert-type scales on ease of use, level of engagement, perceived repeatability, and likeliness to use in a real-world authentication setting.
-The \textit{breathe} and \textit{listen} (\(\mu\)=6.75) tasks were ranked easiest to use, while the \textit{sequence} (\(\mu\)=2.25) and \textit{face} (\(\mu\)=2.75) tasks were ranked the most difficult.
-\textit{Sequence} was rated highly in engagement however (\(\mu\)=5), as was \textit{song}  (\(\mu\)=5), while \textit{breathe-open} and \textit{listen} were ranked least engaging (\(\mu\)=2.25).
-\textit{Breathe} (\(\mu\)=7) and \textit{listen} (\(\mu\)=6.75) were ranked highest in repeatability, with \textit{sequence} (\(\mu\)=2.5) along with \textit{face} and \textit{sport} (\(\mu\)=3) ranked least repeatable.
-Finally in terms of likeliness of use for authentication, \textit{song-open} (\(\mu\)=5) and \textit{sequence} (\(\mu\)=4.25) were rated highest, though modestly, while \textit{breathe} (\(\mu\)=2.75) and \textit{listen} (\(\mu\)=3) were rated least likely to use.
-
-In addition to these rating scales we asked participants to rank the tasks from most (1) to least (9) favorite overall.
+The \textit{breathe} and \textit{listen} (\(\mu\)=6.75) tasks were rated easiest to use.
+\textit{Sequence} (\(\mu\)=5) and \textit{song} were rated highest in engagement, \textit{Breathe} (\(\mu\)=7) and \textit{listen} (\(\mu\)=6.75) were ranted highest in repeatability.
+In terms of likeliness of use for authentication, \textit{song-open} (\(\mu\)=5) and \textit{sequence} (\(\mu\)=4.25) were rated highest, though modestly.
+We also asked participants to rank the tasks from most (1) to least (9) favorite overall.
 The \textit{song - open} task ranked highest among favorites (\(\mu\)=4.25) followed by a tie between \textit{breathe - open}, \textit{song}, and \textit{speech} (\(\mu\)=4.75).
-In line with some of the results above, \textit{sequence} (\(\mu\)=7.75) and \textit{face} (\(\mu\)=6.75) were rated as least favorites.
+\textit{Sequence} (\(\mu\)=7.75) and \textit{face} (\(\mu\)=6.75) were rated as least favorites.
 
@@
 
-A final component of usability we measured was the ability of the participants to recall their specific chosen passthoughts for the \textit{song}, \textit{sport}, \textit{speech}, \textit{face}, and \textit{sequence} tasks.
-Participants were contacted approximately two weeks after their data collection study visit and were prompted with these categories and asked to respond with what they remembered their choices being.
-As evidenced by their responses, all participants were able to recall all of their chosen secrets, with the exception of one participant who incorrectly remembered their chosen word for the \textit{sequence} task.
+A final component of usability we acquired was the ability of the participants to recall their specific chosen passthoughts for the \textit{song}, \textit{sport}, \textit{speech}, \textit{face}, and \textit{sequence} tasks.
+Participants were contacted approximately two weeks after their data collection study visit and were prompted with these categories and asked to respond with what they chose during the experiment.
+All participants were able to recall all of their chosen secrets, with the exception of one participant who incorrectly remembered their chosen word for the \textit{sequence} task.
 
@@
 The first aspect of this scenario we tested was the ability of an imposter to wear an earpiece acquired from someone else and achieve viable impedance values for EEG collection based on the fit of the pieces in their ears.
-P1 tried on each of the other participants' earpieces, which were able to at least somewhat fit in P1's ears.
+P1 tried on each of the other participants' earpieces, which were able to at least physically fit in P1's ears.
 The impedances of P1 wearing other participants' earpieces were then recorded and are listed in Table \ref{tab:imposter_impedances} below.
@@
 
-To explore the scenario of an imposter attempting to gain access, we chose the worst case participant, P6, whose earpieces P1 had the lowest impedances while wearing.
+To explore the scenario of an imposter attempting to gain access, we chose the most vulnerable case participant, P6, whose earpieces P1 had the lowest impedances while wearing.
 We collected data using the same data collection protocol, but had P1 refer to P6's report of chosen passsthoughts.
-P1 performed each of P6's passthoughts (simulating an "inside imposter'').
+P1 performed each of P6's passthoughts (simulating an "inside imposter").
 Following the same classification and preprocessing steps, we generated 200 samples per task for our imposters, using data from all left ear electrodes.
 
-\begin{table}[h]
-\begin{center}
-\begin{tabular}{lll}
-Task & FAR (Insider) & FAR (Outsider)\\
-\hline
-Breathe & 0.0 & 0.0\\
-Breathe - Open & 0.0 & 0.0\\
-Sport & 0.0 & 0.0\\
-Song & 0.0 & 0.0\\
-Song - Open & 0.0 & 0.0\\
-Speech & 0.0 & 0.0\\
-Listen & 0.0 & 0.0\\
-Face & 0.0 & 0.0\\
-Sequence & 0.0 & 0.0\\
-\end{tabular}
-\end{center}
-\caption{False acceptance rate for spoofed versions of P6's passthoughts, performed by an inside imposter (P1 from the original participant pool) and an outside imposter (not from the original participant pool).}
-\label{tab:imposter}
-\end{table}
+% \begin{table}[h]
+% \begin{center}
+% \begin{tabular}{lll}
+% Task & FAR (Insider) & FAR (Outsider)\\
+% \hline
+% Breathe & 0.0 & 0.0\\
+% Breathe - Open & 0.0 & 0.0\\
+% Sport & 0.0 & 0.0\\
+% Song & 0.0 & 0.0\\
+% Song - Open & 0.0 & 0.0\\
+% Speech & 0.0 & 0.0\\
+% Listen & 0.0 & 0.0\\
+% Face & 0.0 & 0.0\\
+% Sequence & 0.0 & 0.0\\
+% \end{tabular}
+% \end{center}
+% \caption{False acceptance rate for spoofed versions of P6's passthoughts, performed by an inside imposter (P1 from the original participant pool) and an outside imposter (not from the original participant pool).}
+% \label{tab:imposter}
+% \end{table}
 
-Since every participant has one classifier per task (for which that task is the passthought), we are able to make 200 spoofed attempts with the correct passthought on each of P6's classifiers (Table \ref{tab:imposter}).
+Since every participant has one classifier per task (for which that task is the passthought), we are able to make 200 spoofed attempts with the correct passthought on each of P6's classifiers.
 We find no successful spoof attempts for tasks with a chosen secret (e.g., \textit{song} or \textit{face}).
@@
 However, since this participant's data appeared in the initial pool, the classifier may have been trained on his or her recordings as negative examples.
-To explore the efficacy of an outsider spoofing recordings, we repeated the same protocol with an individual who did not appear in our initial set of participants (an "outside imposter,'' Table \ref{tab:imposter}).
+To explore the efficacy of an outsider spoofing recordings, we repeated the same protocol with an individual who did not appear in our initial set of participants (an "outside imposter").
 Again, we find zero successful authentication attempts out of 1,800 attempts.
@@
 This study was conducted with a small, relatively homogeneous sample of participants.
-We feel that more participants from a more diverse pool would greatly improve our understanding and interpretation of the capabilities of this technology.
-This does not lessen the importance of this work however, as this sample size is comparable to that of previous scalp-based EEG passthoughts work\cite{Ashby2011, Marcel2007a, Palaniappan2008, palaniappan2006electroencephalogram, Poulos2002, Chuang2013b}, the only other in-ear EEG passthoughts study we are aware of \cite{curran2016passthoughts} (notably a generic fit system was used here), and other custom-fit in-ear EEG research \cite{kidmose2013study}.
-The fitting and manufacturing of custom-fit earpieces was the main limitation to increasing our sample size, and may very well pose a limitation in proliferation and adoption of such a technology.
-Recently however, there have been developments in at-home kits for creating one's own custom-fitted earpieces \cite{voix2015settable} that could help overcome this barrier.
+In order to establish the validity of this system for widespread real-world use we feel it is necessary to expand the size and diversity of participants in future studies.
+In the case of this initial evaluation however, the homogeneity of our participant pool strengthens the reported results given that system attempts to distinguish between individuals.
+We feel that a greater number of  participants from a more diverse pool would greatly improve our understanding and interpretation of the capabilities of this technology.
+This sample size is in line with this area of research as it is comparable to that of other scalp-based EEG passthoughts work\cite{Ashby2011, Marcel2007a, Palaniappan2008, palaniappan2006electroencephalogram, Poulos2002, Chuang2013b}, the only other in-ear EEG passthoughts study we are aware of \cite{curran2016passthoughts} (notably a generic fit system was used here), and other custom-fit in-ear EEG research \cite{Kidmose2013a}.
+The fitting and manufacturing of custom-fit earpieces was the main limitation to increasing our sample size, and may very well pose a limitation in proliferation and adoption of such a technology in the world.
+Recently, there have been developments in at-home kits for creating one's own custom-fitted earpieces \cite{voix2015settable} that could help overcome this barrier.
 
@@
 
-Furthermore, likely due to the use of conductive gel, low impedances are still achievable using other participants' custom-fit earpieces, despite the uniqueness of ear canal shapes between individuals \cite{Akkermans2005}.
-Nevertheless, classifiers appear to resists spoofing attacks, indicating that task-related signals are unique to individuals.
+Furthermore, low impedances are still achievable by an imposter using other participants' custom-fit earpieces, despite the uniqueness of ear canal shapes between individuals \cite{Akkermans2005} likely in part due to the our of conductive gel.
+This discovery is not detrimental, however, as the inherence factor of this system is drawn from the uniqueness of EEG and not ear canal shape.
+Classifiers appear to still resists spoofing attacks, indicating that task-related signals are unique to individuals.
 In terms of establishing a possession factor, the custom-fit earpieces could easily include a hardware keypair to sign authentication attempts in a three-factor, one-step scheme.
@@
 Although our target participant documented their chosen passthought, the spoofers found ambiguity in how these passthoughts could be expressed.
-For the \textit{face} task, the spoofers did not know the precise friend the original participant had chosen.
+For the \textit{face} task, the spoofers did not know the precise face the original participant had chosen.
 For the \textit{song} and \textit{song - open} tasks, though the song was known, the spoofers did not know what part of the song the original participant had imagined, or how it was imagined (humming, imagining a full performance, melody, vocals, etc).
@@
 Finally, performance on Fp1 was not as high as performance in the ear, despite Fp1's popularity in past work on passthoughts \cite{Chuang2013b}.
-This could be explained by the greater number of electrodes in the ear (compared to just one on Fp1).
-Additionally, Fp1 is best poised to pick up on frontal lobe activity (e..g, concentration), but our tasks did not generally involve frontal lobe activity; in fact, a good number of them involved audio, which we would expect to be better observed near the auditory cortex at the ears.
-Future work should continue to investigate what sorts of mental tasks lend themselves to in-ear recording.
+This could be explained by the greater number of electrodes in the ear in this analysis (compared to just one on Fp1).
+Additionally, Fp1 is best poised to pick up on frontal lobe activity (e..g, concentration), but our tasks did not generally involve frontal lobe activity; in fact, a good number of them involved audio, which we would expect to be better observed from the auditory cortex near the ears.
+Future work should continue to investigate what sorts of mental tasks best lend themselves to in-ear recording.
 
@@
 Finally, our work leaves room for some clear user experience (UX) improvements.
-Future work should try using dry electrodes, commonly found in consumer EEG devices, for comfort and usability. The electrodes could be grounded to the ear, instead of the forehead.
+Future work should try using dry electrodes, commonly found in consumer EEG devices, for comfort and usability.
+The electrodes could be grounded to the ear, instead of the forehead.
 Additionally, future work could easily place a speaker inside our current custom-fit earbuds to produce working "hearables'' that can be used as ordinary headphones.
@@
 Future work should also attempt a closed-loop (or online) passthought system, in which users receive immediate feedback on the result of their authentication attempt.
-A closed-loop BCI system could help us understand how learning effects
-on the human side might impact authentication performance, as the human and machine co-adapt through authentication attempts.
+A closed-loop BCI system could help us understand how learning effects on the human side might impact authentication performance, as the human and machine co-adapt through authentication attempts.
 
@@
 
-As demonstrated by these preliminary results, custom-fit, in-ear EEG earpieces provide three factors of authentication in a single authentication step: thinking one's passthought, using the discreet form factor of an earpiece.
-In this paper, we demonstrate quite high authentication accuracy using a single sensing earpiece.
-By expanding our corpus of EEG readings (in population size, time, and diversity of settings), we hope to better understand the underlying distribution of EEG signals, so that we may better understand the security properties of passthoughts.
+As demonstrated by these preliminary results, custom-fit, in-ear EEG earpieces provide three factors of authentication in one highly usable authentication step: thinking one's passthought, using the discreet form factor of an earpiece.
+In this paper, we demonstrate quite high authentication accuracy using a single sensing earpiece with potential for integration with technology already used in everyday life like earphones.
+By expanding our corpus of EEG readings (in population size, time, and diversity of settings), we hope to better understand the underlying distribution of EEG signals and security properties of passthoughts as well usability issues that may arise in different contexts.
 
-{\footnotesize \bibliographystyle{acm}
-\bibliography{references}}
+\section{Acknowledgments}
+
+This work was funded by X.
+
+% Balancing columns in a ref list is a bit of a pain because you
+% either use a hack like flushend or balance, or manually insert
+% a column break.  http://www.tex.ac.uk/cgi-bin/texfaq2html?label=balance
+% multicols doesn't work because we're already in two-column mode,
+% and flushend isn't awesome, so I choose balance.  See this
+% for more info: http://cs.brown.edu/system/software/latex/doc/balance.pdf
+%
+% Note that in a perfect world balance wants to be in the first
+% column of the last page.
+%
+% If balance doesn't work for you, you can remove that and
+% hard-code a column break into the bbl file right before you
+% submit:
+%
+% http://stackoverflow.com/questions/2149854/how-to-manually-equalize-columns-
+% in-an-ieee-paper-if-using-bibtex
+%
+% Or, just remove \balance and give up on balancing the last page.
+%
+%\balance
+
+% REFERENCES FORMAT
+% References must be the same font size as other body text.
+
+\bibliographystyle{acm-sigchi}
+\bibliography{references.bib}
 

### 2017-04-01 paper.tex
John's changes to related work, overall reducing text

@@
 
-\title{One-Step, Three-Factor Authentication via Ear EEG}
+\title{One-Step, Three-Factor Authentication via an Earpiece}
 
-\numberofauthors{4}
+\numberofauthors{2}
 \author{
-  \alignauthor 1st Author\\
+  \alignauthor 1st Author, 2nd Author, 3rd Author\\
     \affaddr{Affiliation}\\
-    \email{e-mail}\\
-  \alignauthor 2nd Author\\
-    \affaddr{Affiliation}\\
-    \email{e-mail}\\
-  \alignauthor 3rd Author\\
-    \affaddr{Affiliation}\\
-    \email{e-mail}\\
+    \email{1st e-mail, 2nd e-mail, 3rd e-mail}\\
   \alignauthor 4th Author\\
@@
 \keywords{
-  usable security; multi-factor authentication; wearable authentication; bio-sensory computing; passthoughts
+  usable security; multi-factor authentication; wearable authentication; passthoughts; biosensing
 }
@@
 
-\subsection{Passthoughts Authentication}
+\subsection{Passthoughts and Behavioral Authentication}
 The use of EEG as a biometric signal for user authentication has a relatively short history.
 In 2005, Thorpe et al. motivated and outlined the design of a passthoughts system \cite{Thorpe2005}.
-Since 2002, a number of independent groups have achieved 99-
-100\% authentication accuracy using multi-channel sensors placed on the scalp \cite{Poulos2002,Marcel2007a,Palaniappan2008,Ashby2011}.
-In 2013, one group showed that 99\% authentication accuracy can also be
-achieved using a consumer-grade single-channel sensor on the scalp \cite{Chuang2013b}. In particular, they proposed that the
-lack of signal diversity from multiple EEG channels can be overcome by allowing users to choose their own personalized passthoughts (e.g., sing their favorite song in their head).
+Since 2002, a number of independent groups have achieved 99-100\% authentication accuracy for small populations using research-grade and consumer-grade scalp-based EEG systems \cite{Poulos2002,Marcel2007a,Ashby2011,Chuang2013b}.
+%Since 2002, a number of independent groups have achieved 99-
+%100\% authentication accuracy using multi-channel sensors placed on the scalp \cite{Poulos2002,Marcel2007a,Palaniappan2008,Ashby2011}.
+%In 2013, one group showed that 99\% authentication accuracy can also be
+%achieved using a consumer-grade single-channel sensor on the scalp \cite{Chuang2013b}. In particular, they proposed that the
+%lack of signal diversity from multiple EEG channels can be overcome by allowing users to choose their own personalized passthoughts (e.g., sing their favorite song in their head).
 There are two significant consequences of this result.
 First,
-the passthoughts approach is no longer constrained by the high cost (\textgreater \$10,000 USD)
-and low usability (gel-based electrodes in hair; aesthetic challenges of a full EEG cap) of
-medical-grade multi-channel devices. Second, because users can choose and
-easily change their secret mental task, this approach can support one-step two-
-factor authentication via the simultaneous presentation of the inherence factor
-(brainwave signatures due to the unique folding structures of the cortex) and the
-knowledge factor (the secret mental task) \cite{Chuang2014}.
+%the passthoughts approach is no longer constrained by the high cost (\textgreater \$10,000 USD)
+%and low usability (gel-based electrodes in hair; aesthetic challenges of a full EEG cap) of
+%medical-grade multi-channel devices. Second, because users can choose and
+%easily change their secret mental task, this approach can support one-step two-
+%factor authentication via the simultaneous presentation of the inherence factor
+%(brainwave signatures due to the unique folding structures of the cortex) and the
+%knowledge factor (the secret mental task) \cite{Chuang2014}.
 
-By employing scalp-based consumer-grade electroencephalography (EEG), it was demonstrated in a 2014 passthoughts study that a user can submit both a knowledge factor (i.e., secret thought) and an inherence factor (i.e., brainwave signal unique to the individual) in a single step by performing a single mental task \cite{Chuang2014}.
+%By employing scalp-based consumer-grade electroencephalography (EEG), it was demonstrated in a 2014 passthoughts study that a user can submit both a knowledge factor (i.e., secret thought) and an inherence factor (i.e., brainwave signal unique to the individual) in a single step by performing a single mental task \cite{Chuang2014}.
 Additionally, the robustness of this method against impersonation attacks was demonstrated, including conditions where the attacker may have learned the target's secret thought and/or secret task \cite{Johnson2014}.
 
-Following this, we investigate custom-fit in-ear EEG technology as the platform for investigating the feasibility, performance, and usability of one-step three-factor authentication worn unobtrusively.
+%Following this, we investigate custom-fit in-ear EEG technology as the platform for investigating the feasibility, performance, and usability of one-step three-factor authentication worn unobtrusively.
 The system we propose and test here uses the choice of a mental task or "passthought" to perform as knowledge (factor one), the uniqueness of an individual's brain activity as measured by EEG as inherence (factor two), and the physical token of a custom-fit earpiece that could easily contain a hardware key-pair, as a possession factor (factor 3).
@@
 
-\subsection{In-Ear EEG}
-Even consumer-grade headsets can be uncomfortable to wear, and are awkwardly visible to outside observers.
+%\subsection{In-Ear EEG}
+%Even consumer-grade headsets can be uncomfortable to wear, and are awkwardly visible to outside observers.
 Sensors placed around the ear, however, present a far more discreet, comfortable location for EEG electrodes, as many people already wear technology like earbuds in day-to-day life.
 
-Research in in-ear EEG is only several years old. Nonetheless, the concept has
-attracted attention because of the discreetness factor of in-ear EEG over
-traditional scalp-based EEG. A research team at the Imperial College London
-and Aarhus University published a landmark paper in 2011 that introduced the
-concept of in-ear EEG, demonstrating for the first time the feasibility of recording
-brainwave signals from within the ear canal \cite{Looney2011}.
-Follow-up work from the same group demonstrated its ability to produce signal-to-noise ratios comparable to
-those from conventional EEG electrode placements, robustness to common
-sources of artifacts, and use in a brain-computer interface (BCI) system based on
-auditory evoked potentials and visual evoked potentials
-\cite{Looney2012a,Kidmose2013a,Kidmose2013b}.
-United Sciences is currently developing a consumer "hearable" (in-ear wearable) called The Aware, which will measure EEG from the ear, among other biometrics \cite{UnitedSciences}.
+The concept of in-ear EEG was introduced in 2011 with a demonstration of the feasibility of recording brainwave signals from within the ear canal \cite{Looney2011}.
+The in-ear placement can produce signal-to-noise ratios comparable to those from conventional EEG electrode placements, is robust to common sources of artifacts, and can be used in a brain-computer interface (BCI) system based on auditory and visual evoked potentials \cite{Kidmose2013a}.
+An 80\% accuracy level was achieved for user authentication using in-ear EEG captured with a modified single-channel consumer-grade device \cite{curran2016passthoughts}.
 
-\cite{curran2016passthoughts} was the first to merge in-ear EEG with passthought authentication,
- using a minimally modified consumer-grade EEG device with a single electrode, achieving approximately 80\% authentication accuracy.
+%Research in in-ear EEG is only several years old. Nonetheless, the concept has
+%attracted attention because of the discreetness factor of in-ear EEG over
+%traditional scalp-based EEG. A research team at the Imperial College London
+%and Aarhus University published a landmark paper in 2011 that introduced the
+%concept of in-ear EEG, demonstrating for the first time the feasibility of recording
+%brainwave signals from within the ear canal \cite{Looney2011}.
+%Follow-up work from the same group demonstrated its ability to produce signal-to-noise ratios comparable to
+%those from conventional EEG electrode placements, robustness to common
+%sources of artifacts, and use in a brain-computer interface (BCI) system based on
+%auditory evoked potentials and visual evoked potentials
+%\cite{Looney2012a,Kidmose2013a,Kidmose2013b}.
+%United Sciences is currently developing a consumer "hearable" (in-ear wearable) called The Aware, which will measure EEG from the ear, among other biometrics \cite{UnitedSciences}.
 
-\subsection{One-Step, Multi-Factor Authentication}
+%\cite{curran2016passthoughts} was the first to merge in-ear EEG with passthought authentication,
+ %using a minimally modified consumer-grade EEG device with a single electrode, achieving approximately 80\% authentication accuracy.
+
+%\subsection{One-Step, Multi-Factor Authentication}
 Behavioral authentication methods such as keystroke dynamics and speaker authentication can be categorized as one-step two-factor authentication schemes.
@@
 In contrast, the Nymi band supports one-step two-factor authentication via the inherence factor (cardiac rhythm that is supposed to be unique to each individual) and the possession factor (the wearing of the band on the wrist) \cite{Nymi}.
-However, as far as we know, no one has proposed or demonstrated a one-step three-factor authentication scheme, in which possession of a unique device also serves to authenticate the user.
-In this paper, we introduce custom-built EEG devices, incorporating an added possession factor to the already one-step two-factor authentication of passthoughts.
+However, as far as we know, no one has proposed or demonstrated a one-step three-factor authentication scheme.%, in which possession of a unique device also serves to authenticate the user.
+%In this paper, we introduce custom-built EEG devices, incorporating an added possession factor to the already one-step two-factor authentication of passthoughts.
 
@@
 
-When proposing or evaluating authentication paradigms, robustness against imposters is often the first consideration, but the usability of these systems is of equal importantance as they must conform to a person's needs and lifestyle to warrant adoption and prolonged use.
-In \cite{sasse2001}, the authors describe usability issues with knowledge-based systems like alphanumeric passwords, in particular that it should not be the burden of the user to remember complex passwords that have to be frequently changed.
-\cite{braz2006} analyze some of the complexities applying traditional interface human factors heuristics to authentication, and indicate the importance of social acceptibility, learnability, and simplicity of authentication methods.
+When proposing or evaluating authentication paradigms robustness against imposters is often the first consideration, but the usability of these systems is of equal importance as they must conform to a person's needs and lifestyle to warrant adoption and prolonged use.
+The authors of \cite{sasse2001} describe usability issues with knowledge-based systems like alphanumeric passwords, in particular that it should not be the burden of the user to remember complex passwords that have to be frequently changed.
+\cite{braz2006} analyzed some of the complexities applying interface human factors heuristics to authentication, and indicate the importance of social acceptibility, learnability, and simplicity of authentication methods.
+Technology worn on the head faces particular usability issues; in their analysis of user perceptions of such devices, \cite{Genaro2014} identified design, usability, ease of use, and obtrusiveness among the top 10 concerns of users posting online about these devices, as well as qualitative concerns around comfort and "looking weird".
 
-Head-worn devices face particular usability issues; in their analysis of user perceptions of such devices, \cite{Genaro2014} identify design, usability, ease of use, and obtrusiveness among the top 10 concerns of users of these devices and qualitative concerns about comfort or "looking weird".
+In the proposed system we seek to incorporate the perspectives of this research.
+Passthoughts such as a favorite song or relaxed breathing are easy for a user to remember and perform, and the choice of an earpiece form-factor of our system seeks to address wearability and social perception concerns.
 
@@
 Many such uses have been proposed that embrace usability such as touch-based interactions \cite{Tartz2015, Holz2015} and walking patterns \cite{Lu2014} using mobile phones, as well as identification via head movements and blinking in head-worn devices \cite{Rogers2015}.
-However, these typically draw only from the inherence factor (though could incorporate the possession factor of the device).
-\cite{Chen2015} proposed an inherence and knowledge two-factor method for multi-touch mobile devices based on a user's unique finger tapping of a song, though this may be vulnerable to "shoulder surfing": imposters observing and mimicking the behavior.
+However, these typically draw only from the inherence factor.
+\cite{Chen2015} proposed an inherence and knowledge two-factor method for multi-touch mobile devices based on a user's unique finger tapping of a song, though it may be vulnerable to "shoulder surfing": imposters observing and mimicking the behavior.
 By comparison, passthoughts are largely invisible to attackers.
-This system also presents a solution to "rubber-hose attacks" (forceful coercion to divulge a password): a thought, which is secret (and thus changeable), but has a particular expression unique to an individual, the performance of which cannot be described (and thus cannot be coerced).
-
-%% 3/28
+Furthermore, this system also presents a solution to "rubber-hose attacks" (forceful coercion to divulge a password): a thought, which is secret (and thus changeable), but has a particular expression unique to an individual, the performance of which cannot be described (and thus cannot be coerced).
 
@@
 Seven male, right-handed participants (P1-P7), 5 students and 2 non-students, completed our study protocol approved by our local ethics review board.
-Though this sample is relatively homogenous, this quality interestingly functions to strengthen the results of this initial exploration (see details in Discussion).
+Though this sample is relatively homogenous and greater diversity is necessary for a larger real-world feasibility assessment, this quality interestingly functions to strengthen the results of this initial exploration (see details in Discussion).
 After participants' 3D ear molds were obtained and their fit and electrical impedance was checked, the collection of data for authentication analyses commenced.
@@
 
-To produce custom ear impressions during the first study visit, we cleaned subjects' ears and injected silicon into the ear canals.
-A cotton ball with a string attached is placed into the ear canal first.
-When the silicon dries after a few minutes, the string is pulled to remove the impression from the ear canal.
-This impression is then scanned with a 3D scanner and the resulting scan modified based on some heuristics to achieve a comfortable fit and to ensure the intended electrode sites will make good contact with the skin.
-Channels are created in the 3D model to allow wire leads and associated EEG electrodes as well as a plastic tube to deliver audio.
-This 3D model is then sent to a 3D printer.
-Following this wires, leads, and associated AgCl electrodes are installed.
-
+To produce custom ear impressions we first cleaned subjects' ears and injected silicon into the ear canals.
+A cotton ball with a string attached was placed into the ear canal first.
+When the silicon dried after a few minutes, the string was pulled to remove the impression from the ear canal.
+This impression was then scanned with a 3D scanner and the resulting scan modified based on some heuristics to achieve a comfortable fit and to ensure the intended electrode sites will make good contact with the skin.
+Channels were created in the 3D model to allow wire leads and associated EEG electrodes as well as a plastic tube to deliver audio.
+This 3D model was then sent to a 3D printer after which wires, leads, and associated AgCl electrodes were installed.
 The positions of the earpiece electrodes were simplified from those described in \cite{Mikkelsen2015}.
@@
 All sites were cleaned with ethanol prior to electrode placement and a small amount of conductive gel was used on each electrode.
-For EEG recording we used OpenBCI \cite{michalska2009openbci}, an open-source biosensing system to maintain an overall low cost for our setup.
-OpenBCI costs about 600 USD, and thus is an affordable alternative to medical-grade EEG systems (about 20,000 USD), and has demonstrated effectiveness for non-medical use cases such as this one \cite{Frey2016}.
-The OpenBCI system we used allows for 8 channels of simultaneous recording, along with separate ground and reference channels.
-Data was collected with the ground placed at the center of the forehead, approximately AFz according to the 10-20 International Standard for Electrode Placement (ISEP), and using the left mastoid as reference.
-6 channels were used for the three electrodes on Eech earpiece (shown in Figure \ref{fig:earpiece_diagram}), for the remaining two channels AgCl ring electrodes were placed on the right mastoid for later re-referencing, and at approximately Fp1 (above the left eye in in the ISEP) for validating the data collected in the ears against a common scalp-based placement.
-Before beginning the experiment, the data from each channel was visually inspected using the OpenBCI interface and participants were asked to blink and clench their jaws to confirm that all channels were active and properly connected.
+For EEG recording we used an 8-channel OpenBCI system \cite{michalska2009openbci} which is open-source and costs about 600 USD; an alternative to medical-grade EEG systems (\textgreater20,000 USD), with demonstrated effectiveness \cite{Frey2016}.
+The ground was placed at the center of the forehead, approximately AFz according to the 10-20 International Standard for Electrode Placement (ISEP), and reference on the left mastoid.
+6 channels were used for the 3 electrodes on each earpiece (shown in Figure \ref{fig:earpiece_diagram}); for the remaining 2 channels one AgCl ring electrode was placed on the right mastoid for later re-referencing, and one at approximately Fp1 (ISEP location above the left eye) to validate the data collected in the ears against a common scalp-based placement.
+Before beginning the experiment, the data from each channel was visually inspected using the OpenBCI interface.
 Audio stimuli were delivered through small tubes in the earpieces.
@@
 During the experiment, participants were seated in a comfortable position in a quiet room facing a laptop on which the instructions and stimuli were presented using PsychoPy \cite{peirce2007psychopy}.
-The entire set of tasks was completed once over with five trials each, followed by another five trials each in order to reduce boredom and repetition effects of a single task.
-Each trial was 10 seconds in length, for a total of 10 trials and 100 seconds of data collected per task.
+All tasks were performed in five trials each, followed by another set of five trials each to reduce boredom and repetition effects.
+Each trial was 10 seconds in length, for a total of 10 trials or 100 seconds of data collected per task.
 The instructions were read aloud to the participant by the experimenter, and the experiment was advanced using a pointer held in the participant's lap to minimize motion artifacts in the data.
 The experimenter also recorded the participant's chosen secrets for the \textit{sport}, \textit{song}, \textit{face}, \textit{speech}, and \textit{sequence} tasks and reminded the participant of these for the second set of trials.
-
- After completing the experiment, a subset of participants completed a usability questionnaire in which they were asked to rate their ease of performing, level of engagement, perceived repeatability, and likeliness of using each task.
-The questionnaire also asked participants to rank the tasks overall from most to least favorite, as well as several open response questions regarding potential use cases of in-ear EEG and this method of authentication, level of comfort wearing the earpieces, and any other comments they chose to provide.
+After EEG data collection, participants completed a usability questionnaire.
 
@@
 
-We were able to confirm the custom-fit earpieces are able to collect EEG data via two metrics: good impedances measured for the ear electrodes, and alpha-band EEG activity attenuation when a participant's eyes were open versus closed.
+We were able to confirm the custom-fit earpieces are able to collect quality EEG data via two metrics: good impedances measured for the ear electrodes, and alpha-band EEG activity attenuation when a participant's eyes were open versus closed.
 
-It is important that the electrical impedances achieved for electrodes are low ($<$10 kOhm) 
-to obtain quality EEG signals.
+It is important that the electrical impedances achieved for electrodes are low ($<$10 kOhm) to obtain quality EEG signals.
 Table \ref{tab:impedances} below summarizes the impedances across the seven participants' six ear channels.
@@
 \end{center}
-\caption{Electrical impedances measured for earpiece electrodes, for concha (C), front (F) and back (B).}
+\caption{Electrical impedances measured for concha (C), front (F) and back (B) earpiece electrodes.}
 \label{tab:impedances}
@@
 For the alpha-attenuation test, data from the \textit{breathe} task was compared with that of the \textit{breathe - open} task.
-It is a well-known feature of EEG data that activity in the alpha-band (approximately 8-12 Hz range) increases when the eyes are closed compared with a similar state with eyes open.
-For our participants, this attenuation is clearly visible even in just a single trial's data.
-We also performed this comparison on the data collected from the Fp1 electrode and see the effect clearly there as well to compare.
+It is a well-known feature of EEG data that activity in the alpha-band (approx.
+8-12 Hz) increases when the eyes are closed compared to when the eyes are open.
+This attenuation is clearly visible even in just a single trial's data from our ear pieces and matches that seen in our Fp1 scalp electrode data.
 Figure \ref{fig:alpha_atten} shows the alpha attenuation in the left ear channels, as well as Fp1 of one participant as an example.
-We see the same effect in the right ear channels.
+We see the same validation in the right ear channels.
 
@@
 We analyzed the EEG signals collected during the tasks using a support vector classifier (SVC).
-Since past work has shown that classification tasks in EEG-based BCI are linear \cite{Garrett2003a}, we used XGBoost, a popular tool for logistic linear classification \cite{Chen2016}.
+Since past work has shown that classification tasks in EEG-based brain-computer interfaces (BCI) are linear \cite{Garrett2003a}, we used XGBoost, a popular tool for logistic linear classification \cite{Chen2016}.
 Compared to other linear classifiers, XGBoost uses gradient boosting; in which an algorithm generates an ensemble (in this case, a decision tree) of weak linear classifiers that minimizes a given loss function.
@@
 Using data from all left-ear electrodes achieves the next lowest FAR.
-Interestingly, no single electrode performs as well as the aggregate left or both-ear plus Fp1 (all) conditions.
+No single electrode performs as well as the aggregate left or both-ear plus Fp1 (all) conditions.
 
@@
 
-Our results indicate acceptable accuracy using electrodes on the left ear alone. 
-This corresponds to our original scenario, in which the device could be worn like an earbud (ideally, only one earbud would need sensors).
+Our results indicate acceptable accuracy using data from the left ear alone.
+This corresponds to our desired scenario, in which the device could be worn like an earbud.
 As such, we focus on results from the left ear alone in our following analyses.
@@
 
-A subset of four participants completed our usability questionnaire.
+A subset of participants completed our usability questionnaire.
 This questionnaire asked them to rank each of the mental tasks on 7-point likert-type scales on ease of use, level of engagement, perceived repeatability, and likeliness to use in a real-world authentication setting.
@@
 
-While our authentication analysis establishes that passthoughts achieve low FAR and FRR when tested against other participants' passthoughts, we do not know how robust passthoughts are against a spoofing attack, in which both a participant's custom-fit electrode, and details of that participant's chosen passthought, are leaked and used by an imposter.
+While our authentication analysis establishes that passthoughts achieve low FAR and FRR when tested against other participants' passthoughts, this does not tell us how robust passthoughts are against a spoofing attack, in which both a participant's custom-fit electrode, and details of that participant's chosen passthought, are leaked and authentication is attempted by an imposter.
 
 The first aspect of this scenario we tested was the ability of an imposter to wear an earpiece acquired from someone else and achieve viable impedance values for EEG collection based on the fit of the pieces in their ears.
-P1 tried on each of the other participants' earpieces, which were able to at least physically fit in P1's ears.
+P1 tried on each of the other participants' customized earpieces, which were able to at least physically fit in P1's ears.
 The impedances of P1 wearing other participants' earpieces were then recorded and are listed in Table \ref{tab:imposter_impedances} below.
-While some are a better fit than others, overall they are higher than those achieved by the pieces' intended owners themselves.
+While some are a better fit than others, overall they are higher (worse) than those achieved by the pieces' intended owners themselves.
 
@@
 
-To explore the scenario of an imposter attempting to gain access, we chose the most vulnerable case participant, P6, whose earpieces P1 had the lowest impedances while wearing.
+To explore the scenario of an imposter attempting to gain access, we chose the case of the most vulnerable participant, P6, whose earpieces P1 had the lowest impedances while wearing.
 We collected data using the same data collection protocol, but had P1 refer to P6's report of chosen passsthoughts.
-P1 performed each of P6's passthoughts (simulating an "inside imposter").
+P1 performed each of P6's passthoughts (simulating an "inside imposter" from within the system).
 Following the same classification and preprocessing steps, we generated 200 samples per task for our imposters, using data from all left ear electrodes.
@@
 Since every participant has one classifier per task (for which that task is the passthought), we are able to make 200 spoofed attempts with the correct passthought on each of P6's classifiers.
-We find no successful spoof attempts for tasks with a chosen secret (e.g., \textit{song} or \textit{face}).
+We find zero successful spoof attempts for tasks with a chosen secret (e.g., \textit{song} or \textit{face}).
 However, we also do not find any successful spoof attacks for tasks with no chosen secret (e.g., \textit{breathe}).
@@
 To explore the efficacy of an outsider spoofing recordings, we repeated the same protocol with an individual who did not appear in our initial set of participants (an "outside imposter").
-Again, we find zero successful authentication attempts out of 1,800 attempts.
+Again, we find zero successful authentications out of 1,800 attempts.
 
@@
 
-Our findings demonstrate the apparent feasibility of a single earpiece, achieving good results with only three electrodes and a reference, all on or around the left ear.
+Our findings demonstrate the apparent feasibility of a passthoughts system consisting of a single earpiece with three electrodes and a reference, all on or around the left ear.
 FARs and FRRs are very low across all participants and tasks, with FARs overall lower than FRRs, a desirable pattern in terms of authenticating access to potentially sensitive information.
@@
 In order to establish the validity of this system for widespread real-world use we feel it is necessary to expand the size and diversity of participants in future studies.
-In the case of this initial evaluation however, the homogeneity of our participant pool strengthens the reported results given that system attempts to distinguish between individuals.
-We feel that a greater number of  participants from a more diverse pool would greatly improve our understanding and interpretation of the capabilities of this technology.
-This sample size is in line with this area of research as it is comparable to that of other scalp-based EEG passthoughts work\cite{Ashby2011, Marcel2007a, Palaniappan2008, palaniappan2006electroencephalogram, Poulos2002, Chuang2013b}, the only other in-ear EEG passthoughts study we are aware of \cite{curran2016passthoughts} (notably a generic fit system was used here), and other custom-fit in-ear EEG research \cite{Kidmose2013a}.
-The fitting and manufacturing of custom-fit earpieces was the main limitation to increasing our sample size, and may very well pose a limitation in proliferation and adoption of such a technology in the world.
+In the case of this initial evaluation however, the homogeneity of our participant pool strengthens the reported results given that system is meant to distinguish between individuals.
+%We feel that a greater number of  participants from a more diverse pool would greatly improve our understanding and interpretation of the capabilities of this technology. 
+%This sample size is in line with this area of research as it is comparable to that of other scalp-based EEG passthoughts work\cite{Ashby2011, Marcel2007a, Palaniappan2008, palaniappan2006electroencephalogram, Poulos2002, Chuang2013b}, the only other in-ear EEG passthoughts study we are aware of \cite{curran2016passthoughts} (notably a generic fit system was used here), and other custom-fit in-ear EEG research \cite{Kidmose2013a}.
+This sample size is comparable to that of other EEG passthoughts work \cite{Ashby2011, Marcel2007a, Poulos2002, Chuang2013b, curran2016passthoughts} and other custom-fit in-ear EEG research \cite{Kidmose2013a, Mikkelsen2015}.
+The fitting and manufacturing of custom-fit earpieces was the main limitation to increasing our sample size, and may very well pose a limitation in proliferation and adoption of such a technology.
 Recently, there have been developments in at-home kits for creating one's own custom-fitted earpieces \cite{voix2015settable} that could help overcome this barrier.
@@
 
-Furthermore, low impedances are still achievable by an imposter using other participants' custom-fit earpieces, despite the uniqueness of ear canal shapes between individuals \cite{Akkermans2005} likely in part due to the our of conductive gel.
-This discovery is not detrimental, however, as the inherence factor of this system is drawn from the uniqueness of EEG and not ear canal shape.
-Classifiers appear to still resists spoofing attacks, indicating that task-related signals are unique to individuals.
+Contrary to our expectations, relatively low impedances are still achievable by an imposter using other participants' custom-fit earpieces, despite the uniqueness of ear canal shapes between individuals \cite{Akkermans2005}.
+This could likely have been due to our use of conductive gel and warrants further exploration.
+This discovery is not detrimental, however, as the primary inherence factor of this system is drawn from the uniqueness of EEG and not ear canal shape.
+Classifiers appear to still resist spoofing attacks, indicating that task-related signals are unique to individuals.
 In terms of establishing a possession factor, the custom-fit earpieces could easily include a hardware keypair to sign authentication attempts in a three-factor, one-step scheme.
@@
 Finally, performance on Fp1 was not as high as performance in the ear, despite Fp1's popularity in past work on passthoughts \cite{Chuang2013b}.
-This could be explained by the greater number of electrodes in the ear in this analysis (compared to just one on Fp1).
+This could be explained by the greater number of electrodes in the ear in this analysis (compared to one on Fp1).
 Additionally, Fp1 is best poised to pick up on frontal lobe activity (e..g, concentration), but our tasks did not generally involve frontal lobe activity; in fact, a good number of them involved audio, which we would expect to be better observed from the auditory cortex near the ears.
@@
 Another important question surrounds how passthoughts might be cracked.
-Generally, we do not understand how an individual's passthought is drawn from the distribution of EEG signals that an individual produces throughout the day.
+Generally, we do not understand how an individual's passthought is drawn from the distribution of EEG signals an individual produces throughout the day.
 Given a large enough corpus of EEG data, are some passthoughts as easy to guess as \textit{password1234} is for passwords?
@@
 The electrodes could be grounded to the ear, instead of the forehead.
-Additionally, future work could easily place a speaker inside our current custom-fit earbuds to produce working "hearables'' that can be used as ordinary headphones.
+Additionally, future work could easily place a speaker inside our current custom-fit earbuds to produce working "hearables" that can be used as ordinary headphones.
 
@@
 
-As demonstrated by these preliminary results, custom-fit, in-ear EEG earpieces provide three factors of authentication in one highly usable authentication step: thinking one's passthought, using the discreet form factor of an earpiece.
-In this paper, we demonstrate quite high authentication accuracy using a single sensing earpiece with potential for integration with technology already used in everyday life like earphones.
+As demonstrated by these preliminary results, custom-fit, in-ear EEG earpieces can provide three factors of security in one highly usable step: thinking one's passthought, using the discreet form factor of an earpiece.
+Among this initial sample, we are able to achieve 100\% authentication accuracy using a single sensing earpiece, showing potential for integration with technology already used in everyday life (like earphones).
 By expanding our corpus of EEG readings (in population size, time, and diversity of settings), we hope to better understand the underlying distribution of EEG signals and security properties of passthoughts as well usability issues that may arise in different contexts.

### 2017-04-02 paper.tex
Small changes to get to 8 pages

@@
 
-\title{One-Step, Three-Factor Authentication via an Earpiece}
+\title{One-Step, Three-Factor Authentication Using an Earpiece}
 
@@
 
-Furthermore, the form factor of an earpiece is a significant improvement over scalp-based passthoughts systems toward real-world use.
-Technology worn in the ear is already an acceptable practice in examples such as earphones and bluetooth headsets.
+Furthermore, the form factor of an earpiece carries significantly less stigama versus scalp-based passthoughts systems.
+Technology worn in the ear is already an acceptable practice, for example earphones or bluetooth headsets.
 
@@
 \cite{braz2006} analyzed some of the complexities applying interface human factors heuristics to authentication, and indicate the importance of social acceptibility, learnability, and simplicity of authentication methods.
-Technology worn on the head faces particular usability issues; in their analysis of user perceptions of such devices, \cite{Genaro2014} identified design, usability, ease of use, and obtrusiveness among the top 10 concerns of users posting online about these devices, as well as qualitative concerns around comfort and "looking weird".
+Technology worn on the head faces particular usability issues; in their analysis of user perceptions of such devices, \cite{Genaro2014} identified design, usability, ease of use, and obtrusiveness among the top 10 concerns of users online postings, and qualitatively comments around comfort and "looking weird".
 
 In the proposed system we seek to incorporate the perspectives of this research.
-Passthoughts such as a favorite song or relaxed breathing are easy for a user to remember and perform, and the choice of an earpiece form-factor of our system seeks to address wearability and social perception concerns.
+Passthoughts such as a favorite song or relaxed breathing are easy for a user to remember and perform, and the choice of an earpiece form factor of our system seeks to address wearability and social perception concerns.
 
@@
 After participants' 3D ear molds were obtained and their fit and electrical impedance was checked, the collection of data for authentication analyses commenced.
-Data collection consisted of participants completing a short questionnaire, a set up period with the OpenBCI system and earpieces including a second impedance check, the performance of 9 mental tasks presented on a laptop, and finally a post-experiment questionnaire.
+Data collection consisted of participants completing a demographics questionnaire, a set up period with the OpenBCI system and earpieces with a second impedance check, their performance of 9 mental tasks, and finally a post-experiment questionnaire.
 
@@
 The 9 authentication tasks and their attributes are listed in Table \ref{tab:tasks}.
-Our strategy was to select tasks that captured a diversity of possibilities across the dimensions of external stimuli, involving a personal secret, eyes open or closed (due to known significant effects on EEG), and different types of mental imagery.
+Our strategy was to select tasks that captured a diversity across dimensions of external stimuli, involving a personal secret, eyes open or closed (due to known effects on EEG), and different types of mental imagery.
 
@@
 During the experiment, participants were seated in a comfortable position in a quiet room facing a laptop on which the instructions and stimuli were presented using PsychoPy \cite{peirce2007psychopy}.
-All tasks were performed in five trials each, followed by another set of five trials each to reduce boredom and repetition effects.
+All tasks were performed for five trials each, followed by another set of five trials each to reduce boredom and repetition effects.
 Each trial was 10 seconds in length, for a total of 10 trials or 100 seconds of data collected per task.
-The instructions were read aloud to the participant by the experimenter, and the experiment was advanced using a pointer held in the participant's lap to minimize motion artifacts in the data.
+The instructions were read aloud to the participant by the experimenter, and the participant advanced using a pointer held in their lap to minimize motion artifacts in the data.
 The experimenter also recorded the participant's chosen secrets for the \textit{sport}, \textit{song}, \textit{face}, \textit{speech}, and \textit{sequence} tasks and reminded the participant of these for the second set of trials.
@@
 
-We were able to confirm the custom-fit earpieces are able to collect quality EEG data via two metrics: good impedances measured for the ear electrodes, and alpha-band EEG activity attenuation when a participant's eyes were open versus closed.
+We confirm the custom-fit earpieces are able to collect quality EEG data via two metrics: low impedances measured for the ear electrodes, and alpha-band EEG activity attenuation when a participant's eyes were open versus closed.
 
@@
 8-12 Hz) increases when the eyes are closed compared to when the eyes are open.
-This attenuation is clearly visible even in just a single trial's data from our ear pieces and matches that seen in our Fp1 scalp electrode data.
+This attenuation is clearly visible even in just a single trial's data from our earpieces and matches that seen in our Fp1 scalp electrode data.
 Figure \ref{fig:alpha_atten} shows the alpha attenuation in the left ear channels, as well as Fp1 of one participant as an example.
@@
 Incorporating all electrodes data results in a perfect score for all tasks.
-Using data from all left-ear electrodes achieves the next lowest FAR.
-No single electrode performs as well as the aggregate left or both-ear plus Fp1 (all) conditions.
+Using data from all left ear electrodes achieves the next lowest FAR.Counter to our expectations, Fp1 does not perform as well as most ear electrodes, though overall these reported rates are \textless\textless 1\%.
 
-Counter to our expectations, Fp1 does not perform as well as most ear electrodes, though overall these reported rates are far less than 1\%. 
-For each position, FAR was about ten times lower than FRR, which is preferable for authentication, as false authentications are potentially more costly than false rejections.
+For each position, FAR was about ten times lower than FRR, which is preferable for authentication, as false authentications are more costly than false rejections.
 
@@
 This corresponds to our desired scenario, in which the device could be worn like an earbud.
-As such, we focus on results from the left ear alone in our following analyses.
+As such, we focus on results from only the left ear in remaining analyses.
 
@@
 Within-tasks FAR is ten times higher, and within-participants FAR is one hundred times higher, though for all scenarios still less than 1\%.
-However, FRR is \textit{lower} in the within-tasks training strategy than in our original strategy's FRR. Within-participants again results in the highest FRR.
+However, FRR is \textit{lower} in the within-tasks training strategy than in our original strategy. Within-participants again results in the highest FRR.
 
@@
 A final component of usability we acquired was the ability of the participants to recall their specific chosen passthoughts for the \textit{song}, \textit{sport}, \textit{speech}, \textit{face}, and \textit{sequence} tasks.
-Participants were contacted approximately two weeks after their data collection study visit and were prompted with these categories and asked to respond with what they chose during the experiment.
+Participants were contacted approximately two weeks after EEG data collection and were prompted with these categories and asked to respond with what they chose during the experiment.
 All participants were able to recall all of their chosen secrets, with the exception of one participant who incorrectly remembered their chosen word for the \textit{sequence} task.
@@
 
-One primary question surrounds how our passthoughts system performance will change with a greater number of users, and with more diverse data.
+One primary question is how our passthoughts system performance will change with a greater number of users and with more diverse data.
 Our system specifically trains on negative examples of incorrect users; we do not yet know how this approach will scale.
@@
 
-% We provide cursory evidence that passthoughts are difficult to spoof, though further work should expand on ours with more subjects.
 Another important question surrounds how passthoughts might be cracked.
@@
 Additionally, future work could easily place a speaker inside our current custom-fit earbuds to produce working "hearables" that can be used as ordinary headphones.
-
 Future work should also attempt a closed-loop (or online) passthought system, in which users receive immediate feedback on the result of their authentication attempt.
@@
 
-This work was funded by X.
+%This work was funded by X.
 

### 2017-04-05 paper.tex
Minor fixes to authors/title
Incorporating Nick's edits

@@
 
-\title{One-Step, Three-Factor Authentication Using an Earpiece}
+\title{One-Step, Three-Factor Authentication in a Single Earpiece}
 
-\numberofauthors{2}
+\numberofauthors{3}
 \author{
-  \alignauthor 1st Author, 2nd Author, 3rd Author\\
+  \alignauthor 1st Author, 2nd Author\\
     \affaddr{Affiliation}\\
-    \email{1st e-mail, 2nd e-mail, 3rd e-mail}\\
+    \email{1st e-mail, 2nd e-mail}\\
+  \alignauthor 3rd Author\\
+    \affaddr{Affiliation}\\
+    \email{e-mail}\\
   \alignauthor 4th Author\\
@@
 \begin{abstract}
- Multifactor authentication presents a robust method to secure our increasingly digitized private information, but typically requires multiple actions on the part of the user resulting in a high cost to usability and limiting adoption.
+ Multifactor authentication presents a robust method to secure our digital private information, but typically requires multiple actions on the part of the user resulting in a high cost to usability and limiting adoption.
 Furthermore, a truly usable system must be unobtrusive and inconspicuous.
@@
 Furthermore, we find a 0\% false acceptance rate in a simulation of an impersonation attack.
-We also report perspectives from our participants and discuss constructive directions for future work toward real-world use.
+We also report perspectives from our participants and discuss constructive directions for future work.
 Our results indicate that a single earpiece with embedded electrodes could provide a discreet, convenient, and robust method for secure one-step, three-factor authentication.
@@
 Additionally, we find that passthoughts could not be spoofed by imposters, even when the imposters had the user's earpiece and knew their chosen passthoughts.
-We discuss future work to investigate the robustness of passthoughts in day-to-day life, and raise questions about how and why passthoughts work as well as they do.
+Finally we discuss interesting patterns in our promising results, and future work to investigate the robustness of passthoughts in day-to-day life.
 
@@
 Since 2002, a number of independent groups have achieved 99-100\% authentication accuracy for small populations using research-grade and consumer-grade scalp-based EEG systems \cite{Poulos2002,Marcel2007a,Ashby2011,Chuang2013b}.
-%Since 2002, a number of independent groups have achieved 99-
-%100\% authentication accuracy using multi-channel sensors placed on the scalp \cite{Poulos2002,Marcel2007a,Palaniappan2008,Ashby2011}.
-%In 2013, one group showed that 99\% authentication accuracy can also be
-%achieved using a consumer-grade single-channel sensor on the scalp \cite{Chuang2013b}. In particular, they proposed that the
-%lack of signal diversity from multiple EEG channels can be overcome by allowing users to choose their own personalized passthoughts (e.g., sing their favorite song in their head).
-There are two significant consequences of this result.
-First,
-%the passthoughts approach is no longer constrained by the high cost (\textgreater \$10,000 USD)
-%and low usability (gel-based electrodes in hair; aesthetic challenges of a full EEG cap) of
-%medical-grade multi-channel devices. Second, because users can choose and
-%easily change their secret mental task, this approach can support one-step two-
-%factor authentication via the simultaneous presentation of the inherence factor
-%(brainwave signatures due to the unique folding structures of the cortex) and the
-%knowledge factor (the secret mental task) \cite{Chuang2014}.
-
-%By employing scalp-based consumer-grade electroencephalography (EEG), it was demonstrated in a 2014 passthoughts study that a user can submit both a knowledge factor (i.e., secret thought) and an inherence factor (i.e., brainwave signal unique to the individual) in a single step by performing a single mental task \cite{Chuang2014}.
-Additionally, the robustness of this method against impersonation attacks was demonstrated, including conditions where the attacker may have learned the target's secret thought and/or secret task \cite{Johnson2014}.
-
-%Following this, we investigate custom-fit in-ear EEG technology as the platform for investigating the feasibility, performance, and usability of one-step three-factor authentication worn unobtrusively.
-The system we propose and test here uses the choice of a mental task or "passthought" to perform as knowledge (factor one), the uniqueness of an individual's brain activity as measured by EEG as inherence (factor two), and the physical token of a custom-fit earpiece that could easily contain a hardware key-pair, as a possession factor (factor 3).
-Because three-factor authentication (3FA) requires the user to submit one distinct instance of each type of authenticator, it represents the strongest level of authentication security possible.
-The ability to utilize all three of these security factors in a single step by performing a mental task of a few seconds is promising in pursuit of extremely strong security while maintaining a low amount of effort and obtrusiveness to the user, and could even be enjoyable.
-
-%\subsection{In-Ear EEG}
-%Even consumer-grade headsets can be uncomfortable to wear, and are awkwardly visible to outside observers.
-Sensors placed around the ear, however, present a far more discreet, comfortable location for EEG electrodes, as many people already wear technology like earbuds in day-to-day life.
 
@@
 
-%Research in in-ear EEG is only several years old. Nonetheless, the concept has
-%attracted attention because of the discreetness factor of in-ear EEG over
-%traditional scalp-based EEG. A research team at the Imperial College London
-%and Aarhus University published a landmark paper in 2011 that introduced the
-%concept of in-ear EEG, demonstrating for the first time the feasibility of recording
-%brainwave signals from within the ear canal \cite{Looney2011}.
-%Follow-up work from the same group demonstrated its ability to produce signal-to-noise ratios comparable to
-%those from conventional EEG electrode placements, robustness to common
-%sources of artifacts, and use in a brain-computer interface (BCI) system based on
-%auditory evoked potentials and visual evoked potentials
-%\cite{Looney2012a,Kidmose2013a,Kidmose2013b}.
-%United Sciences is currently developing a consumer "hearable" (in-ear wearable) called The Aware, which will measure EEG from the ear, among other biometrics \cite{UnitedSciences}.
-
-%\cite{curran2016passthoughts} was the first to merge in-ear EEG with passthought authentication,
- %using a minimally modified consumer-grade EEG device with a single electrode, achieving approximately 80\% authentication accuracy.
-
-%\subsection{One-Step, Multi-Factor Authentication}
 Behavioral authentication methods such as keystroke dynamics and speaker authentication can be categorized as one-step two-factor authentication schemes.
@@
 In contrast, the Nymi band supports one-step two-factor authentication via the inherence factor (cardiac rhythm that is supposed to be unique to each individual) and the possession factor (the wearing of the band on the wrist) \cite{Nymi}.
-However, as far as we know, no one has proposed or demonstrated a one-step three-factor authentication scheme.%, in which possession of a unique device also serves to authenticate the user.
-%In this paper, we introduce custom-built EEG devices, incorporating an added possession factor to the already one-step two-factor authentication of passthoughts.
+However, as far as we know, no one has proposed or demonstrated a one-step three-factor authentication scheme.
 
@@
 Mobile and wearable technologies' continuous proximity to the user's body provides favorable conditions for unobtrusively capturing biometrics for authentication.
-Many such uses have been proposed that embrace usability such as touch-based interactions \cite{Tartz2015, Holz2015} and walking patterns \cite{Lu2014} using mobile phones, as well as identification via head movements and blinking in head-worn devices \cite{Rogers2015}.
+Many such uses have been proposed that embrace usability like touch-based interactions \cite{Tartz2015, Holz2015} and walking patterns \cite{Lu2014} using mobile phones, as well as identification via head movements and blinking in head-worn devices \cite{Rogers2015}.
 However, these typically draw only from the inherence factor.
@@
 Furthermore, this system also presents a solution to "rubber-hose attacks" (forceful coercion to divulge a password): a thought, which is secret (and thus changeable), but has a particular expression unique to an individual, the performance of which cannot be described (and thus cannot be coerced).
-
-% Typical authentication protocols are often susceptible to a so-called \textit{rubber-hose attack}, in which users are coerced into giving up their chosen secret (e.g.
-alphanumeric password), biometric, or unique token, voluntarily or otherwise \cite{Bojinov2012, Martinovic2012}.
-This attack is particularly effective against protocols that rely only on inherence factors, as inherent traits such as fingerprints are difficult to change without costly repercussions \cite{Spielberg2002}.
-One defense against such an attack is \textit{tacit authentication}, in which the user does not know exactly how s/he performs the authenticating action and thus cannot fully give it away even under duress.
-
-% Past work has exploited tacit skills (skills we know how to do, but cannot readily explain our method for doing, e.g.
-riding a bike or walking \cite{Bojinov2012}.
-In practice, these skills require time to learn, and the fact that they are performed visibly could open up opportunities for recording and replay attacks.
-
-% Our work explores a different solution to rubber-hose attacks: a thought, which is secret (and thus changeable), but has a particular expression unique to an individual, the performance of which cannot be described (and thus cannot be coerced).
-% Furthermore, the performance of the chosen thought is largely invisible to outside observers, ensuring the actual authentication is impervious to shoulder-surfing.
 
@@
 
-\begin{figure}[htbp]
+\begin{figure}[t]
 \centering
@@
 \includegraphics[width=0.5\textwidth]{figures/002_AlphaAtt_all.jpg}
-\caption{Alpha-attenuation (8-12 Hz range) in left ear channels compared against the Fp1 channel, referenced at left mastoid.
-Red indicates breathing data with eyes open, blue indicates the same task with eyes closed.}
+\caption{Alpha-attenuation (8-12 Hz range) in left ear and Fp1 channels, referenced at left mastoid. Red indicates breathing data with eyes open, blue indicates the same task with eyes closed.}
 \label{fig:alpha_atten}
@@
 We concatenated all electrode power spectra together, and performed principal component analysis on all concatenated vectors such that the resulting vectors described 95\% of the variance in the full power spectrum data.
-For each task, for each participant, 100 seconds of data were collected in total across 10 trials of 10 seconds each, resulting in 200 samples per participant, per task, following this preprocessing.
+For each task, for each participant, 100 seconds of data were collected in total across 10 trials of 10 seconds each, resulting in 200 samples per participant, per task.
 
@@
 
-\begin{table*}[t]
+\begin{table*}[h]
 \centering
@@
 
-These results establish good performance in our original training strategy, in which we count as negative examples recordings from the wrong participant performing any task.
-For comparison, we try two additional training strategies: one in which negative examples are the correct task recorded from the wrong participant (within-tasks), and one in which negative examples are the incorrect task recorded from the correct participant (within-participants).
+These results establish good performance in our original training strategy (between-participants, any task), in which we counted as negative examples recordings from the wrong participant performing any task.
+For comparison, we report two additional training strategies: one in which negative examples are the correct task recorded from the wrong participant (between participants, same tasks), and one in which negative examples are the wrong task recorded from the correct participant (within-participants).
+Positive examples were always correct participant, correct task.
 
@@
 \begin{tabular}{lrr}
- & \textbf{FAR} & \textbf{FRR}\\
+ \textbf{Training Scheme} & \textbf{FAR} & \textbf{FRR}\\
 \hline
-Original & 0.000074 & 0.004424\\
-Within-tasks & 0.000724 & 0.001522\\
+Between-participants, any task & 0.000074 & 0.004424\\
+Between-participants, same task & 0.000724 & 0.001522\\
+\hline
 Within-participants & 0.002523 & 0.039702\\
@@
 \end{center}
-\caption{Mean FAR and FRR for all participants and passthoughts across three different training strategies.}
+\caption{Mean FAR and FRR for all participants and passthoughts across three different training schemes.}
 \label{tab:compare}
@@
 
-Overall, our original training strategy achieves the lowest FAR (Table \ref{tab:compare}).
+Overall, our between-participants training strategy achieves the lowest FAR (Table \ref{tab:compare}).
 Within-tasks FAR is ten times higher, and within-participants FAR is one hundred times higher, though for all scenarios still less than 1\%.
@@
 
-A subset of participants completed our usability questionnaire.
-This questionnaire asked them to rank each of the mental tasks on 7-point likert-type scales on ease of use, level of engagement, perceived repeatability, and likeliness to use in a real-world authentication setting.
-The \textit{breathe} and \textit{listen} (\(\mu\)=6.75) tasks were rated easiest to use.
-\textit{Sequence} (\(\mu\)=5) and \textit{song} were rated highest in engagement, \textit{Breathe} (\(\mu\)=7) and \textit{listen} (\(\mu\)=6.75) were ranted highest in repeatability.
-In terms of likeliness of use for authentication, \textit{song-open} (\(\mu\)=5) and \textit{sequence} (\(\mu\)=4.25) were rated highest, though modestly.
-We also asked participants to rank the tasks from most (1) to least (9) favorite overall.
-The \textit{song - open} task ranked highest among favorites (\(\mu\)=4.25) followed by a tie between \textit{breathe - open}, \textit{song}, and \textit{speech} (\(\mu\)=4.75).
-\textit{Sequence} (\(\mu\)=7.75) and \textit{face} (\(\mu\)=6.75) were rated as least favorites.
+A subset of participants completed a usability questionnaire.
+This questionnaire asked them to rate each mental task on four 7-point likert-type scales: ease of use, level of engagement, perceived repeatability, and likeliness to use in a real-world authentication setting.
+The \textit{breathe} and \textit{listen} tasks were rated easiest to use (\(\mu\)=6.75), \textit{Sequence}, \textit{song}, and \textit{song - open} as most engaging (\(\mu\)=5), \textit{Breathe} (\(\mu\)=7) and \textit{listen} (\(\mu\)=6.75) as most repeatable.
+For likeliness to use for authentication, \textit{song - open} (\(\mu\)=5) and \textit{sequence} (\(\mu\)=4.25) were rated highest, though modestly.
+Participants also ranked the tasks overall from most (1) to least (9) favorite.
+\textit{Song - open} ranked most favorites (\(\mu\)=4.25) followed by a tie between \textit{breathe - open}, \textit{song}, and \textit{speech} (\(\mu\)=4.75).
+\textit{Sequence} (\(\mu\)=7.75) and \textit{face} (\(\mu\)=6.75) were ranked least favorite.
 
-In addition to the scales and rankings, we included in our questionnaire a few open response questions to ascertain attitudes about the use cases for in-ear EEG and passthoughts, and the comfort of wearing an in-ear EEG device in everyday life.
+In addition to the scales and rankings, we included a few open response questions to ascertain attitudes around use cases for in-ear EEG and passthoughts, and the comfort of wearing an in-ear EEG device in everyday life.
 Participants first read the prompt, "Imagine a commercially available wireless earbud product is now available based on this technology that you've just experienced.
@@
 P5 and P6 also indicated a use for measuring engagement with media like movies and music, and relatedly P4 wrote "music playback optimized for current mental state and feelings".
-In terms of comfort wearing such a device, participants generally responded they would be comfortable, though P5 and P6 stipulated only when they would otherwise be wearing something like earphones in their ears already.
-In response to an "any other comments" prompt, notably three participants pointed out the mental imagery of a face was difficult for them and some concerns about their ability to repeat tasks in the same exact way each time.
+In terms of comfort wearing such a device, participants generally responded they would be comfortable, though P5 and P6 stipulated only when they already would be wearing something in the ears like earphones.
+Notably, three participants also added that imaginging a face was difficult and were concerned about their ability to repeat tasks in the same exact way each time.
 
-A final component of usability we acquired was the ability of the participants to recall their specific chosen passthoughts for the \textit{song}, \textit{sport}, \textit{speech}, \textit{face}, and \textit{sequence} tasks.
-Participants were contacted approximately two weeks after EEG data collection and were prompted with these categories and asked to respond with what they chose during the experiment.
-All participants were able to recall all of their chosen secrets, with the exception of one participant who incorrectly remembered their chosen word for the \textit{sequence} task.
+A final component of usability we acquired was the ability of the participants to recall their specific chosen passthoughts.
+Participants were contacted via e-mail approximately two weeks after data collection and asked to reply with the passthoughts they chose for the \textit{song}, \textit{sport}, \textit{speech}, \textit{face}, and \textit{sequence} tasks.
+All participants correctly recalled all chosen passthoughts, with the exception of one participant who did not recall their chosen word for the \textit{sequence} task.
 
@@
 \end{center}
-\caption{Electrical impedances achieved with P1 wearing each other participant's (P) custom-fitted earpieces, for concha (C), front (F) and back (B).}
+\caption{Electrical impedances with P1 wearing each other participant's (P) custom-fitted earpieces, for concha (C), front (F) and back (B).}
 \label{tab:imposter_impedances}
@@
 This study was conducted with a small, relatively homogeneous sample of participants.
+In the case of this initial evaluation however, the homogeneity of our participant pool strengthens the reported results given that system is meant to distinguish between individuals.
 In order to establish the validity of this system for widespread real-world use we feel it is necessary to expand the size and diversity of participants in future studies.
-In the case of this initial evaluation however, the homogeneity of our participant pool strengthens the reported results given that system is meant to distinguish between individuals.
-%We feel that a greater number of  participants from a more diverse pool would greatly improve our understanding and interpretation of the capabilities of this technology. 
-%This sample size is in line with this area of research as it is comparable to that of other scalp-based EEG passthoughts work\cite{Ashby2011, Marcel2007a, Palaniappan2008, palaniappan2006electroencephalogram, Poulos2002, Chuang2013b}, the only other in-ear EEG passthoughts study we are aware of \cite{curran2016passthoughts} (notably a generic fit system was used here), and other custom-fit in-ear EEG research \cite{Kidmose2013a}.
 This sample size is comparable to that of other EEG passthoughts work \cite{Ashby2011, Marcel2007a, Poulos2002, Chuang2013b, curran2016passthoughts} and other custom-fit in-ear EEG research \cite{Kidmose2013a, Mikkelsen2015}.
-The fitting and manufacturing of custom-fit earpieces was the main limitation to increasing our sample size, and may very well pose a limitation in proliferation and adoption of such a technology.
-Recently, there have been developments in at-home kits for creating one's own custom-fitted earpieces \cite{voix2015settable} that could help overcome this barrier.
+The fitting and manufacturing of custom-fit earpieces was the main limitation to increasing our sample size.
+This may very well pose a limitation in proliferation and adoption of such a technology, although recently there have been developments in at-home kits for creating one's own custom-fitted earpieces \cite{voix2015settable} that could help overcome this barrier.
 
-In our analysis, some notable patterns emerged. First, the \textit{breathe},
-\textit{breathe-open}, and \textit{listen} tasks performed exceedingly well among participants.
-Classifiers overall distinguished the \textit{breathe}  and \textit{listen} tasks even compared
-to the same tasks from other participants, implying that these tasks are expressed differently
-for each participant, i.e. that they have an inherence factor sufficient for authentication,
-even though they task do not involve an explicit secondary knowledge factor as in \textit{sport}
-or \textit{song}, for example. Second, we were able to achieve good results by generating feature
-vectors based on only 500ms (300 voltage readings across the three electrodes).
-This short timespan is somewhat surprising, given that some tasks (like songs)
-presumably rely on changes or patterns over a longer period of time.
+Among our authentication training schemes, the between-participants analyses achieved lower FAR than within-participants, indicating the inherence factor (a person's brainwaves) is likely stronger than the knowledge factor (their choice of task), though the knowledge factor is not trivial.
+The \textit{breathe}, \textit{breathe-open}, and \textit{listen} tasks performed exceedingly well among participants.
+Classifiers overall distinguished the \textit{breathe} and \textit{listen} tasks even compared to the same tasks from other participants, implying that these tasks are expressed differently for each participant, i.e.
+that they have an inherence factor sufficient for authentication, even though they task do not involve an explicit secondary knowledge factor as in \textit{sport} or \textit{song}.
+We were able to achieve these results by generating feature vectors based on only 500ms (300 voltage readings across the three electrodes).
+This short timespan is somewhat surprising, given that tasks like \textit{song} presumably change over longer time periods.
 

### 2017-04-05 paper.tex
minor fixes

@@
 Sport & 0.0002 & 0 & 0 & 0 & 0 & 0 & 0 & 0  & 0 & 0.0127\\
-\textbf{Best Task} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\ \hline
+\textbf{Best Task} & \textbf{0} & \textbf{0} & \textbf{0} & \textbf{0} & \textbf{0} & \textbf{0} & \textbf{0} & \textbf{0} & \textbf{0} & \textbf{0}\\ \hline
 \end{tabularx}
@@
 \begin{tabular}{lrr}
- \textbf{Training Scheme} & \textbf{FAR} & \textbf{FRR}\\
+ \textbf{Analysis Scheme} & \textbf{FAR} & \textbf{FRR}\\
 \hline
@@
 Between-participants, same task & 0.000724 & 0.001522\\
-\hline
 Within-participants & 0.002523 & 0.039702\\
@@
 \end{center}
-\caption{Mean FAR and FRR for all participants and passthoughts across three different training schemes.}
+\caption{Mean FAR and FRR for all participants and passthoughts across three analysis schemes.}
 \label{tab:compare}
@@
 
-Among our authentication training schemes, the between-participants analyses achieved lower FAR than within-participants, indicating the inherence factor (a person's brainwaves) is likely stronger than the knowledge factor (their choice of task), though the knowledge factor is not trivial.
+Among our authentication analysis schemes, the between-participants analyses achieved lower FAR than within-participants, indicating the inherence factor (a person's brainwaves) is likely stronger than the knowledge factor (their choice of task), though the knowledge factor is not trivial.
 The \textit{breathe}, \textit{breathe-open}, and \textit{listen} tasks performed exceedingly well among participants.
@@
 \section{Acknowledgments}
+Witheld for blind review.
 
@@
 % Or, just remove \balance and give up on balancing the last page.
-%
-%\balance
+% \balance
 

### 2017-04-12 paper.tex
Reworking table 4, results text, and discussion text to interrogate factor presence

@@
 By comparison, passthoughts are largely invisible to attackers.
-Furthermore, this system also presents a solution to "rubber-hose attacks" (forceful coercion to divulge a password): a thought, which is secret (and thus changeable), but has a particular expression unique to an individual, the performance of which cannot be described (and thus cannot be coerced).
+Furthermore, this system also presents a possible solution to "rubber-hose attacks" (forceful coercion to divulge a password): a thought, which is secret (and thus changeable), but has a particular expression unique to an individual, the specific performance of which cannot be described (and thus cannot be coerced).
 
@@
 We used a set of mental tasks based on findings in related work regarding the relative strengths of different tasks in authentication accuracy and usability as reported by participants.
-Furthermore, given the in-ear placement of the electrodes and therefore the proximity to the temporal lobes containing the auditory cortex, we tested several novel authentication tasks based specifically on aural imagery or stimuli.
+\cite{Chuang2013b, curran2016passthoughts} Furthermore, given the in-ear placement of the electrodes and therefore the proximity to the temporal lobes containing the auditory cortex, we tested several novel authentication tasks based specifically on aural imagery or stimuli.
 The 9 authentication tasks and their attributes are listed in Table \ref{tab:tasks}.
@@
 Since past work has shown that classification tasks in EEG-based brain-computer interfaces (BCI) are linear \cite{Garrett2003a}, we used XGBoost, a popular tool for logistic linear classification \cite{Chen2016}.
-Compared to other linear classifiers, XGBoost uses gradient boosting; in which an algorithm generates an ensemble (in this case, a decision tree) of weak linear classifiers that minimizes a given loss function.
-Gradient boosting gives better results in linear classification problems, without our needing to manually tune classifier hyperparameter.
+Compared to other linear classifiers, XGBoost uses gradient boosting in which an algorithm generates an ensemble (in this case, a decision tree) of weak linear classifiers that minimizes a given loss function.
+Gradient boosting gives better results in linear classification problems without manually tuning hyperparameters.
 
@@
 
-These results establish good performance in our original training strategy (between-participants, any task), in which we counted as negative examples recordings from the wrong participant performing any task.
-For comparison, we report two additional training strategies: one in which negative examples are the correct task recorded from the wrong participant (between participants, same tasks), and one in which negative examples are the wrong task recorded from the correct participant (within-participants).
+These results establish good performance in our default training strategy, in which we count as negative examples recordings from the wrong participant performing any task.
+For comparison, we report three other analyses with differing negative examples: the correct task recorded from the wrong participant (inherence only), the wrong task recorded from the correct participant (knowledge only), and a combination of these two.
 Positive examples were always correct participant, correct task.
@@
 \begin{center}
-\begin{tabular}{lrr}
- \textbf{Analysis Scheme} & \textbf{FAR} & \textbf{FRR}\\
+\begin{tabular}{llrrr}
+ \textbf{+ve Ex.'s} & \textbf{-ve Ex.'s} & \textbf{Factors} & \textbf{FAR} & \textbf{FRR} \\
 \hline
-Between-participants, any task & 0.000074 & 0.004424\\
-Between-participants, same task & 0.000724 & 0.001522\\
-Within-participants & 0.002523 & 0.039702\\
+$P_c, T_c$ & $P_i, T_*$ & I & 0.000074 & 0.004424\\
+$P_c, T_c$ & $P_i, T_c$ & I & 0.000724 & 0.001522\\
+$P_c, T_c$ & $P_c, T_i$ & K & 0.002523 & 0.039702\\
+$P_c, T_c$ & $P_i, T_* + P_c, T_i$ & I \& K & 0.000186 & 0.052565\\
 \hline
@@
 \end{center}
-\caption{Mean FAR and FRR for all participants and passthoughts across three analysis schemes.}
+\caption{Four analyses training classifiers on different negative examples with resulting mean FAR and FRR across all participants and tasks.
+$P_c$ indicates correct participant, $P_i$ incorrect participant, $T_c$ correct task, $T_i$ incorrect task, and $T_*$ any task.
+I indicates inherence factor and K knowledge factor was interrogated.}
 \label{tab:compare}
@@
 
-Overall, our between-participants training strategy achieves the lowest FAR (Table \ref{tab:compare}).
-Within-tasks FAR is ten times higher, and within-participants FAR is one hundred times higher, though for all scenarios still less than 1\%.
-However, FRR is \textit{lower} in the within-tasks training strategy than in our original strategy. Within-participants again results in the highest FRR.
+Overall, our default training strategy achieves the lowest FAR (Table \ref{tab:compare}).
+Within-task FAR is ten times higher, and within-participants FAR is one hundred times higher, though for all scenarios still less than 1\%.
+However, FRR is \textit{lower} in the within-tasks training strategy than the default. The highest FRR is in the combined negative example case, though FAR remains low.
 
@@
 P1 performed each of P6's passthoughts (simulating an "inside imposter" from within the system).
-Following the same classification and preprocessing steps, we generated 200 samples per task for our imposters, using data from all left ear electrodes.
+Following the same analysis steps, we generated 200 samples per task for our imposters, using data from all left ear electrodes.
 
@@
 
-\section{Discussion}
+\section{Discussion \& Limitations}
 
@@
 
-This study was conducted with a small, relatively homogeneous sample of participants.
+The \textit{breathe}, \textit{breathe-open}, and \textit{listen} tasks performed exceedingly well among participants, despite not having an explicit secondary knowledge factor as in \textit{sport} or \textit{song}.
+We were able to achieve these results by generating feature vectors based on only 500 ms (300 voltage readings across the three electrodes), which is somewhat surprising given that tasks like \textit{song} presumably change over longer periods.
+
+Our multiple classifier training strategies establish the presence of both knowledge and inherence factors as schemes isolating each achieve low FARs.
+The inherence factor performs strongest, while the knowledge factor contributes to a sizable increase in FRR.
+Interestingly, by training classifiers to reject both wrong participants and wrong tasks from the correct participant, thus incorporating both the knowledge and inherence factors, the FRR is highest suggesting multi-factor authentication's added security may come at a small cost to convenience.
+As preliminary evidence of a possession factor in the current prototypes, we had P1 use their best task (listen) with P6's earpieces but tested on P1's classifier, with a resultant FAR of 0.
+The custom-fit earpieces could easily include a hardware keypair to sign authentication attempts presenting a more explicit possession factor.
+
+The powerful interactions between inherence and knowledge emerged in our spoofing attacks.
+Although our target participant documented their chosen passthought, the spoofers found ambiguity in how these passthoughts could be expressed.
+For the \textit{face} task, the spoofers did not know the precise face the original participant had chosen.
+For the \textit{song} tasks, though the song was known, the spoofers did not know what part of the song the original participant had imagined, or how it was imagined.
+This experience sheds light on passthoughts' highly individual nature and suggests there may be intrinsic difficulty in spoofing attempts.
+
+Contrary to our expectations, relatively low impedances were still achievable by an imposter using other participants' custom-fit earpieces, despite the uniqueness of ear canal shapes between individuals \cite{Akkermans2005}.
+This may have been due to our use of conductive gel and warrants further exploration.
+This discovery is not detrimental, however, as the primary inherence factor of this system is drawn from the uniqueness of EEG and not ear canal shape.
+
+Finally, performance on Fp1 was not as high as performance in the ear, despite Fp1's popularity in past work on passthoughts \cite{Chuang2013b}.
+This could be explained by the greater number of electrodes in the ear in this analysis (compared to one on Fp1).
+Additionally, Fp1 is best poised to pick up on frontal lobe activity (e.g, concentration), that our tasks did not generally involve; in fact, several involved audio, which we would expect to be better observed from the auditory cortex near the ears.
+Future work should continue to investigate what sorts of mental tasks best lend themselves to in-ear recording.
+
+The real-world implications of this study are limited by the small, relatively homogeneous sample of participants.
 In the case of this initial evaluation however, the homogeneity of our participant pool strengthens the reported results given that system is meant to distinguish between individuals.
@@
 This may very well pose a limitation in proliferation and adoption of such a technology, although recently there have been developments in at-home kits for creating one's own custom-fitted earpieces \cite{voix2015settable} that could help overcome this barrier.
-
-Among our authentication analysis schemes, the between-participants analyses achieved lower FAR than within-participants, indicating the inherence factor (a person's brainwaves) is likely stronger than the knowledge factor (their choice of task), though the knowledge factor is not trivial.
-The \textit{breathe}, \textit{breathe-open}, and \textit{listen} tasks performed exceedingly well among participants.
-Classifiers overall distinguished the \textit{breathe} and \textit{listen} tasks even compared to the same tasks from other participants, implying that these tasks are expressed differently for each participant, i.e.
-that they have an inherence factor sufficient for authentication, even though they task do not involve an explicit secondary knowledge factor as in \textit{sport} or \textit{song}.
-We were able to achieve these results by generating feature vectors based on only 500ms (300 voltage readings across the three electrodes).
-This short timespan is somewhat surprising, given that tasks like \textit{song} presumably change over longer time periods.
-
-Contrary to our expectations, relatively low impedances are still achievable by an imposter using other participants' custom-fit earpieces, despite the uniqueness of ear canal shapes between individuals \cite{Akkermans2005}.
-This could likely have been due to our use of conductive gel and warrants further exploration.
-This discovery is not detrimental, however, as the primary inherence factor of this system is drawn from the uniqueness of EEG and not ear canal shape.
-Classifiers appear to still resist spoofing attacks, indicating that task-related signals are unique to individuals.
-In terms of establishing a possession factor, the custom-fit earpieces could easily include a hardware keypair to sign authentication attempts in a three-factor, one-step scheme.
-
-The powerful interactions between inherence and knowledge emerged in our spoofing attack.
-Although our target participant documented their chosen passthought, the spoofers found ambiguity in how these passthoughts could be expressed.
-For the \textit{face} task, the spoofers did not know the precise face the original participant had chosen.
-For the \textit{song} and \textit{song - open} tasks, though the song was known, the spoofers did not know what part of the song the original participant had imagined, or how it was imagined (humming, imagining a full performance, melody, vocals, etc).
-This experience sheds light on the highly individual nature of passthoughts, and provides a positive indication that there may be some intrinsic difficulty in spoofing attempts of passthoughts.
-
-Finally, performance on Fp1 was not as high as performance in the ear, despite Fp1's popularity in past work on passthoughts \cite{Chuang2013b}.
-This could be explained by the greater number of electrodes in the ear in this analysis (compared to one on Fp1).
-Additionally, Fp1 is best poised to pick up on frontal lobe activity (e..g, concentration), but our tasks did not generally involve frontal lobe activity; in fact, a good number of them involved audio, which we would expect to be better observed from the auditory cortex near the ears.
-Future work should continue to investigate what sorts of mental tasks best lend themselves to in-ear recording.
 

### 2017-04-14 paper.tex
Adjusting table 4, and reworking task result discussion

@@
 Speech & 0.0002 & 0 & 0.0005 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
-Sport & 0.0002 & 0 & 0 & 0 & 0 & 0 & 0 & 0  & 0 & 0.0127\\
+Sport & 0.0002 & 0 & 0 & 0 & 0 & 0 & 0 & 0  & 0 & 0.0127\\ \hline
 \textbf{Best Task} & \textbf{0} & \textbf{0} & \textbf{0} & \textbf{0} & \textbf{0} & \textbf{0} & \textbf{0} & \textbf{0} & \textbf{0} & \textbf{0}\\ \hline
@@
 All best-performing tasks in our best-case set achieved perfect FAR and FRRs.
-Interestingly, \textit{breathe} appeared as the best task across all participants, except P1 whose best task was \textit{listen} and P5 who had several other best performing tasks.
-Given our training strategy, these results indicate that a given person's \textit{breathe} task is distinguishable not only among other tasks, but among \textit{breathe} tasks from other participants.
-This task performed about as well as its open-eyes counterpart (Figure \ref{fig:meanByTask}), as did \textit{song - open} and \textit{sport} (though, interestingly, \textit{song} with eyes closed performed less well).
+Each task achieved perfect scores across multiple participants, notably \textit{listen} achieved perfect FAR and FRR for 6 out of 7 participants.
+Two participants, P4 and P6 achieved 0 FAR and FRR across all tasks.
+Interestingly, tasks like \textit{listen} and \textit{breathe} performed very well despite lacking a personalized secret, indicating that even when the task may be the same across participants our classifier was still able to distinguish between them.
 
@@
 \begin{center}
-\begin{tabular}{llrrr}
- \textbf{+ve Ex.'s} & \textbf{-ve Ex.'s} & \textbf{Factors} & \textbf{FAR} & \textbf{FRR} \\
+\begin{tabular}{llrr}
+ \textbf{+ Examples} & \textbf{- Examples} & \textbf{FAR} & \textbf{FRR} \\
 \hline
-$P_c, T_c$ & $P_i, T_*$ & I & 0.000074 & 0.004424\\
-$P_c, T_c$ & $P_i, T_c$ & I & 0.000724 & 0.001522\\
-$P_c, T_c$ & $P_c, T_i$ & K & 0.002523 & 0.039702\\
-$P_c, T_c$ & $P_i, T_* + P_c, T_i$ & I \& K & 0.000186 & 0.052565\\
+$P_c, T_c$ & $P_i, T_*$ & 0.000074 & 0.004424\\
+$P_c, T_c$ & $P_i, T_c$ & 0.000724 & 0.001522\\
+$P_c, T_c$ & $P_c, T_i$ & 0.002523 & 0.039702\\
+$P_c, T_c$ & $P_i, T_* + P_c, T_i$ & 0.000186 & 0.052565\\
 \hline
@@
 \end{center}
-\caption{Four analyses training classifiers on different negative examples with resulting mean FAR and FRR across all participants and tasks.
-$P_c$ indicates correct participant, $P_i$ incorrect participant, $T_c$ correct task, $T_i$ incorrect task, and $T_*$ any task.
-I indicates inherence factor and K knowledge factor was interrogated.}
+\caption{Four analyses in which classifiers were trained on differing negative examples paired with resulting mean FAR and FRR across all participants and tasks.
+$P_c$ indicates correct participant, $P_i$ incorrect participant, $T_c$ correct task, $T_i$ incorrect task, and $T_*$ any task.}
 \label{tab:compare}
@@
 Participants' best-performing passthoughts typically see no errors in our training.
+Passthoughts also appear to be quite memorable given our two week recall follow-up and some were rated highly repeatable and engaging.
 Furthermore, no spoofed attacks were successful in our cursory analysis.
 
-The \textit{breathe}, \textit{breathe-open}, and \textit{listen} tasks performed exceedingly well among participants, despite not having an explicit secondary knowledge factor as in \textit{sport} or \textit{song}.
-We were able to achieve these results by generating feature vectors based on only 500 ms (300 voltage readings across the three electrodes), which is somewhat surprising given that tasks like \textit{song} presumably change over longer periods.
+Several tasks performed exceedingly well among participants, even tasks like \textit{listen} and \textit{breathe} which didn't have an explicit secondary knowledge factor like in \textit{sport} or \textit{song}.
+This suggests a passthoughts system could present users with an array of options for them to choose from, though it remains to be seen how these tasks scale with larger populations.
+Furthermore, we were able to achieve these results by generating feature vectors based on only 500 ms (300 voltage readings across the three electrodes), which is somewhat surprising given that tasks like \textit{song} presumably change over longer periods.
 
 Our multiple classifier training strategies establish the presence of both knowledge and inherence factors as schemes isolating each achieve low FARs.
-The inherence factor performs strongest, while the knowledge factor contributes to a sizable increase in FRR.
-Interestingly, by training classifiers to reject both wrong participants and wrong tasks from the correct participant, thus incorporating both the knowledge and inherence factors, the FRR is highest suggesting multi-factor authentication's added security may come at a small cost to convenience.
+Interestingly, by training classifiers to reject both wrong participants and wrong tasks from the correct participant, thus incorporating both the knowledge and inherence factors, we see an increase in FRR suggesting multi-factor authentication's added security may come at a small cost to convenience.
 As preliminary evidence of a possession factor in the current prototypes, we had P1 use their best task (listen) with P6's earpieces but tested on P1's classifier, with a resultant FAR of 0.
@@
 
-Finally, our work leaves room for some clear user experience (UX) improvements.
-Future work should try using dry electrodes, commonly found in consumer EEG devices, for comfort and usability.
-The electrodes could be grounded to the ear, instead of the forehead.
-Additionally, future work could easily place a speaker inside our current custom-fit earbuds to produce working "hearables" that can be used as ordinary headphones.
+Finally, our work leaves room for some clear user experience improvements.
+Future work should assess dry electrodes, commonly found in consumer EEG devices, for comfort and usability.
+The electrodes could be grounded to the earlobe, instead of the forehead.
+Speakers could also be placed inside our current custom-fit earbuds to produce working "hearables" that could be used as ordinary headphones.
 Future work should also attempt a closed-loop (or online) passthought system, in which users receive immediate feedback on the result of their authentication attempt.
-A closed-loop BCI system could help us understand how learning effects on the human side might impact authentication performance, as the human and machine co-adapt through authentication attempts.
+A closed-loop BCI system would assist in understanding how human learning effects side might impact authentication performance, as the human and machine co-adapt.
 
